---
title: "Concentration and production of synthetic promoters in 96 well plates experiments"
author: "Dany Chauvin"
date: "4/1/2021"
output: html_document
---

# PREPARING MOTHER MACHINE DATA

Importing data.

```{r message=FALSE,warning=FALSE}
source("./constitexprImportdata/loadFunctionsAndPackages.R")
path_to_MM_data_summary <- "./dataLists/constitexprData.csv"
source("./constitexprImportdata/readMMData.R")
source("./constitexprImportdata/transformMMData.R")
path_to_bulk_data_summary <- "./dataLists/dataList.csv"
source("./constitexprImportdata/readBulkData.R")
path_to_manual_curation <- "./dataLists/manualCuration.csv"
source("./constitexprImportdata/transformBulkData.R")
```

# COMPUTING d(log(p))/dg BETWEEN ACETATE AND GLUCOSE, BETWEEN GLUCOSE AND GLUCOSEAA

```{r}
# The phenotype of each promoter is described in:

hi_or_med_p2 <- tibble(plate=rep(c("pl1","pl3","pl5","pl7"),each=6),strength=rep(rep(c("med","hi"),each=3),times=4),column=rep(c(7,8,9,10,11,12),times=4))
hi_or_med_p3 <- tibble(plate=rep(c("pl2","pl4","pl6","pl8"),each=12),strength=rep(rep(c("med","hi"),each=3),times=8),column=rep(c(1,2,3,4,5,6,7,8,9,10,11,12),times=4))
hi_or_med <- rbind(hi_or_med_p2,hi_or_med_p3)
type_rib_df <- tibble(strain=c("pl-rplN","pl-rpmB","pl-rrnB","pl-rpsB","ch-rrnB","ch-rplN","ch-rpmB","ch-rpsB"),type=rep(c("rib"),times=8))

mydata_results_all <- mydata_results %>% 
  ungroup() %>% 
  separate(well,c("well_1","well_2"),sep="-") %>% 
  tidyr::extract(well_1,"column","^pl[1-8]{1}_[A-H]{1}_([0-9]{1,})_[0-9a-z]{1,}$",remove=FALSE,convert=TRUE) %>% 
  left_join(hi_or_med,by=c("plate","column")) %>% 
  left_join(type_rib_df,by=c("strain")) %>%
  mutate(strength=ifelse(grepl("med",strain)==TRUE,"med",strength)) %>% 
  mutate(strength=ifelse(grepl("hi",strain)==TRUE,"hi",strength)) %>% 
  mutate(type=ifelse(is.na(type)==TRUE,strength,type)) %>% 
  mutate(sd_l_concentration=1/2*((max_l_pred_concentration-l_pred_concentration)+(l_pred_concentration-min_l_pred_concentration))) %>% 
  mutate(sd_concentration=sd_l_concentration*l_pred_concentration) %>% 
  mutate(sd_production=sd_concentration*well_gr*log(2)+sd_well_gr*log(2)*exp(l_pred_concentration)) %>% 
  mutate(production=exp(l_pred_concentration)*well_gr*log(2)) %>% 
  filter(!((log(production)<4)&(strength=="med"))) %>% 
  filter(!((log(production)<8)&(strength=="hi")))

log_average_data <- mydata_results_all %>% 
  #mutate(l_production=log(production)) %>% 
  #mutate(sd_l_production=sd_production/production) %>% 
  filter(condition %in% c("acetate","glycerol","glucose")) %>% 
  group_by(strain) %>% 
  mutate(m_production_all=mean(production)) %>% 
  mutate(sd_production_all=sqrt(1/3*sum(sd_production**2))) %>% 
  ungroup() %>% 
  distinct(strain,type,m_production_all,sd_production_all) %>% 
  mutate(sd_production_all=1/2*(log(m_production_all+sd_production_all)-log(m_production_all-sd_production_all)), 
         m_production_all=log(m_production_all))

log_average_data_gluaa <- mydata_results_all %>% 
  #mutate(l_production=log(production)) %>% 
  #mutate(sd_l_production=sd_production/production) %>% 
  filter(condition %in% c("glucoseaa")) %>% 
  group_by(strain) %>% 
  mutate(m_production_all=mean(production)) %>% 
  mutate(sd_production_all=sqrt(1/3*sum(sd_production**2,na.rm = TRUE))) %>% 
  ungroup() %>% 
  distinct(strain,type,m_production_all,sd_production_all) %>% 
  mutate(sd_production_gluaa=1/2*(log(m_production_all+sd_production_all)-log(m_production_all-sd_production_all)), 
         m_production_gluaa=log(m_production_all)) %>% 
  distinct(strain,type,m_production_gluaa,sd_production_gluaa)

#From acetate to glucose only
modeled_data_ace_glu <- mydata_results_all %>%
  filter(condition != "glucoseaa") %>% 
  mutate(l_production=log(production)) %>% 
  mutate(sd_l_production=sd_production/production) %>% 
  group_by(strain) %>% 
  do((function(.df){
     .new_df <- .df %>% 
       mutate(p=n()) %>% 
       mutate(s=compute_slope_errxy_robust(well_gr,l_production),
              e=compute_sdslope_errxy_robust(well_gr,l_production),
              i=mean(l_production)-s*mean(well_gr),
              i_min=mean(l_production)-(s+e)*mean(well_gr),
              i_max=mean(l_production)-(s-e)*mean(well_gr),
              l_production_pred=s*well_gr+i,
              l_production_pred_min=(s+e)*well_gr+i_min,
              l_production_pred_max=(s-e)*well_gr+i_max)
    return(.new_df)})(.)) %>% 
    ungroup()

modeled_data_glu_gluaa <- mydata_results_all %>%
  filter(condition %in% c("glucose","glucoseaa")) %>% 
  mutate(l_production=log(production)) %>% 
  mutate(sd_l_production=sd_production/production) %>% 
  group_by(strain) %>%
  do((function(.df){
     .new_df <- .df %>% 
       mutate(s=compute_slope_errxy_robust(well_gr,l_production),
              e=compute_sdslope_errxy_robust(well_gr,l_production),
              i=mean(l_production)-s*mean(well_gr),
              i_min=mean(l_production)-(s+e)*mean(well_gr),
              i_max=mean(l_production)-(s-e)*mean(well_gr),
              l_production_pred=s*well_gr+i,
              l_production_pred_min=(s+e)*well_gr+i_min,
              l_production_pred_max=(s-e)*well_gr+i_max)
    return(.new_df)})(.)) %>% 
    ungroup()


ace_glu <- modeled_data_ace_glu %>% 
  distinct(strain,s,e,type) %>% 
  rename(s_ace_glu=s,
         sd_s_ace_glu=e)

glu_gluaa <- modeled_data_glu_gluaa %>% 
  distinct(strain,s,e,type) %>% 
  rename(s_glu_gluaa=s,
         sd_s_glu_gluaa=e)

phenotypes <- left_join(ace_glu,glu_gluaa,by=c("strain","type")) %>% 
  left_join(log_average_data,by=c("strain","type")) %>% 
  left_join(log_average_data_gluaa,by=c("strain","type")) %>% 
  filter(s_ace_glu>0) #discard obvious outliers
```

These results can be used to infer the different distributions, using a Bayesian approach.
Writing a function to do that well.

```{r}
perform_inference_ace_glu <- function(.input_df,.type){
  
  #.input_df <- phenotypes
  #.type <- "hi"
  
    .df <- .input_df %>% 
      filter(!grepl("ch",strain)) %>% 
      filter(type==.type) %>% 
      dplyr::select(strain,type,s_ace_glu,sd_s_ace_glu) %>% 
      rename(s=s_ace_glu,
           sd=sd_s_ace_glu)
  
    compute_ll <- function(.sigma){
      .new_df <- .df %>% 
      mutate(wp=1/(sd**2+.sigma**2),
             sum_wp=sum(wp),
             weighed_s=wp*s/sum_wp)
      .u <- sum(.new_df$weighed_s)
      ll <- -(-1/2*sum(.new_df$wp*(.new_df$s**2-.u**2))-log(.sigma)+1/2*sum(log(.new_df$wp))-1/2*log(sum(.new_df$wp)))
      return(ll)
      }

      .sigmas <- seq(0.1,2,by=0.01)
      lls <- lapply(.sigmas,compute_ll)
      sigma <- nloptr::cobyla(x0=0.1,compute_ll)$par

      plot(.sigmas,lls)
      abline(v=c(sigma))
      title(paste(.type," acetate to glucose"))

      
      compute_mu <- function(.sigma){
        .new_df <- .df %>% 
        mutate(wp=1/(sd**2+.sigma**2),
               sum_wp=sum(wp),
               weighed_s=wp*s/sum_wp)
        .u <- sum(.new_df$weighed_s)
        return(.u)}

      mu <- compute_mu(sigma)
      
      return(tibble(type=c(.type),mean=c(mu),sd=c(sigma)))}

perform_inference_glu_gluaa <- function(.input_df,.type){
  
  #.input_df <- phenotypes
  #.type <- "hi"
  
    .df <- .input_df %>% 
      filter(!grepl("ch",strain)) %>% 
      filter(type==.type) %>% 
      dplyr::select(strain,type,s_glu_gluaa,sd_s_glu_gluaa) %>% 
      rename(s=s_glu_gluaa,
           sd=sd_s_glu_gluaa)
  
    compute_ll <- function(.sigma){
      .new_df <- .df %>% 
      mutate(wp=1/(sd**2+.sigma**2),
             sum_wp=sum(wp),
             weighed_s=wp*s/sum_wp)
      .u <- sum(.new_df$weighed_s)
      ll <- -(-1/2*sum(.new_df$wp*(.new_df$s**2-.u**2))-log(.sigma)+1/2*sum(log(.new_df$wp))-1/2*log(sum(.new_df$wp)))
      return(ll)
      }

      .sigmas <- seq(0.1,2,by=0.01)
      lls <- lapply(.sigmas,compute_ll)
      sigma <- nloptr::cobyla(x0=0.1,compute_ll)$par

      plot(.sigmas,lls)
      abline(v=c(sigma))
      title(paste(.type," glucose to glucoseaa"))


      
      compute_mu <- function(.sigma){
        .new_df <- .df %>% 
        mutate(wp=1/(sd**2+.sigma**2),
               sum_wp=sum(wp),
               weighed_s=wp*s/sum_wp)
        .u <- sum(.new_df$weighed_s)
        return(.u)}

      mu <- compute_mu(sigma)
      
      return(tibble(type=c(.type),mean=c(mu),sd=c(sigma)))}

perform_inference_log_mean <- function(.input_df,.type){
  
  #.input_df <- phenotypes
  #.type <- "hi"
  
    .df <- .input_df %>% 
      filter(!grepl("ch",strain)) %>% 
      filter(type==.type) %>% 
      dplyr::select(strain,type,m_production_all,sd_production_all) %>% 
      rename(s=m_production_all,
           sd=sd_production_all)
  
    compute_ll <- function(.sigma){
      .new_df <- .df %>% 
      mutate(wp=1/(sd**2+.sigma**2),
             sum_wp=sum(wp),
             weighed_s=wp*s/sum_wp)
      .u <- sum(.new_df$weighed_s)
      ll <- -(-1/2*sum(.new_df$wp*(.new_df$s**2-.u**2))-log(.sigma)+1/2*sum(log(.new_df$wp))-1/2*log(sum(.new_df$wp)))
      return(ll)
      }

      .sigmas <- seq(0.1,2,by=0.01)
      lls <- lapply(.sigmas,compute_ll)
      sigma <- nloptr::cobyla(x0=0.1,compute_ll)$par

      plot(.sigmas,lls)
      abline(v=c(sigma))
      title(paste(.type," glucose to glucoseaa"))


      
      compute_mu <- function(.sigma){
        .new_df <- .df %>% 
        mutate(wp=1/(sd**2+.sigma**2),
               sum_wp=sum(wp),
               weighed_s=wp*s/sum_wp)
        .u <- sum(.new_df$weighed_s)
        return(.u)}

      mu <- compute_mu(sigma)
      
      return(tibble(type=c(.type),mean=c(mu),sd=c(sigma)))}
```

```{r}
inference_results_ace_glu <- rbind(
  perform_inference_ace_glu(phenotypes,"hi"),
  perform_inference_ace_glu(phenotypes,"med"),
  perform_inference_ace_glu(phenotypes,"rib")) %>% 
  rename(mean_s_ace_glu=mean,
         sd_s_ace_glu=sd)       

inference_results_glu_gluaa <- rbind(
  perform_inference_glu_gluaa(phenotypes,"hi"),
  perform_inference_glu_gluaa(phenotypes,"med"),
  perform_inference_glu_gluaa(phenotypes,"rib")) %>% 
  rename(mean_s_glu_gluaa=mean,
         sd_s_glu_gluaa=sd)       

inference_results_log_mean <- rbind(
  perform_inference_log_mean(phenotypes,"hi"),
  perform_inference_log_mean(phenotypes,"med"),
  perform_inference_log_mean(phenotypes,"rib")) %>% 
  rename(log_mean_p=mean,
         log_sd_p=sd)

inference_results <- left_join(inference_results_ace_glu,inference_results_glu_gluaa,by=c("type")) %>% 
  left_join(inference_results_log_mean,by=c("type"))
```

```{r}
inference_results
```

# MOTEVO

```{r}
# Distribution des tailles
length_df %>% 
  ggplot()+
  geom_histogram(aes(length))+
  #theme_cowplot()+
  coord_cartesian(xlim=c(0,600))+
  xlab("Promoter length")

length_df %>% 
  filter(length>200) %>% 
  arrange(length)
```

I checked A04, and this is correct.
Now let's look at what WT_kinney gives to us.

```{r}
phenotypes
```
```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_kinney"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
# Overall distribution of scores and post_prob
motevo_results %>% 
  ggplot()+
  geom_point(aes(post_prob,WM_score))

motevo_results %>% 
  ggplot()+
  geom_freqpoly(aes(WM_score))

motevo_results %>% 
  ggplot()+
  geom_freqpoly(aes(post_prob))

# Overall distribution: apply a filter for post_prob > 0.1
motevo_results %>% 
  filter(post_prob>0.1) %>% 
  ggplot()+
  geom_point(aes(post_prob,WM_score))

motevo_results %>% 
  filter(post_prob>0.1) %>% 
  ggplot()+
  geom_freqpoly(aes(WM_score))

motevo_results %>% 
  filter(post_prob>0.1) %>% 
  ggplot()+
  geom_freqpoly(aes(post_prob))

# How many promoters are represented with such a filter?
```
```{r}
# Set a automatic filter to keep at least the 5 best sites per promoter, according to WM_score and/or post_prob
min_sites <- 1 # Which also sets a limit on WM_score
step <- 0.0001

motevo_results_filtered <- motevo_results %>% 
  do((function(.df){
    min_p <- 0
    
    new_df <- .df %>% 
      filter(post_prob>min_p) %>% 
      group_by(promoter) %>% 
      summarise(n=n())
    min_count <- min(new_df$n)
    i=0
    
    while(min_count>min_sites){
      
      i <- i+1
  
    new_df <- .df %>% 
      filter(post_prob>min_p+i*step) %>% 
      group_by(promoter) %>% 
      summarise(n=n())
    min_count <- min(new_df$n)
    }
    
    new_df <- .df %>% 
      filter(post_prob>min_p+(i-1)*step) %>% 
      mutate(p_thres=(i-1)*step)
    
    return(new_df)
    
  })(.)) %>% 
  ungroup()
  
  min_count <- min(motevo_results_filtered %>% 
    group_by(promoter) %>% 
    count() %>% 
    .$n)
  
  min_count
  unique(motevo_results_filtered$p_thres)
  
  motevo_results_filtered %>% 
    group_by(promoter) %>% 
    count() %>% 
    ggplot()+
    geom_histogram(aes(n))+
    coord_cartesian(xlim=c(0,100))
  
  motevo_results_filtered %>% 
    group_by(promoter) %>% 
    mutate(n_sites=n()) %>%
    mutate(max_WM_score=max(WM_score)) %>% 
    ungroup() %>% 
    distinct(promoter,.keep_all = TRUE) %>% 
    ggplot()+
    geom_point(aes(length,n_sites,col=max_WM_score))
```

So the fact that there is a correlation between length and number of sites is a sign for me... that we do not filter enough. Because this should not depend. So this is certainly not the best way to look at it. Another way is simply to take the 5 best ones for instance.

```{r}
motevo_results_5 <- motevo_results %>% 
  #filter(strand=="+") %>% 
  group_by(promoter,strand) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()<6) %>% 
  ungroup()

 motevo_results_5 %>% 
    ggplot()+
    geom_point(aes(length,WM_score,col=strand),alpha=0.5)
 
  motevo_results_5 %>% 
    ggplot()+
    geom_point(aes(post_prob,WM_score,col=strand))
```


```{r}
selected_strain <- phenotypes %>%
  distinct(strain)

toplot_results <- motevo_results_5 %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  #filter(strand=="+") %>% 
  #filter(WM_score>0) %>% 
  mutate(total_length=length+2*100) %>% 
  group_by(strain) %>% 
  mutate(ref=as.character(row_number())) %>% 
  ungroup() %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),
         end=as.double(end)) %>% 
  #filter((beg<=100+length) & (end>100)) %>% 
  pivot_longer(cols=c("beg","end"),values_to="x") %>% 
  mutate(x=as.double(x))

type_df <- phenotypes %>% 
  distinct(strain,type)

length_df_plot <- length_df %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  semi_join(toplot_results,by=c("strain")) %>% 
  left_join(type_df,by=c("strain")) %>% 
  mutate(y=0) %>% 
  group_by(strain) %>%
  mutate(endseq=length+2*100) %>% 
  mutate(begseq=1) %>% 
  mutate(begprom=101) %>% 
  mutate(begthreecon=length+100+1) %>% 
  ungroup() %>% 
  pivot_longer(cols=c("begseq","begprom","begthreecon","endseq"),values_to="x")
  
plot <- toplot_results %>% 
  filter(type=="med") %>% 
  ggplot()+
  geom_line(data=length_df_plot %>%
              filter(type=="med") %>% 
              filter(name %in% c("begseq","begprom")),aes(x,y),col="green",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(type=="med") %>% 
              filter(name %in% c("begprom","begthreecon")),aes(x,y),col="blue",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(type=="med") %>% 
              filter(name %in% c("begthreecon","endseq")),aes(x,y),col="green",alpha=1)+
  geom_line(data=toplot_results %>% filter(type=="med"),aes(x,WM_score,group=ref,col=strand),alpha=0.5)+
  facet_wrap(~strain,scale="free")+
  theme(legend.position = NULL)+
  xlab("Promoter position")+
  ylab("WM_score")
  #coord_cartesian(ylim=c(-1,1))
  
  
ggsave("all_med_WM_score_kinney.pdf",plot,width=15,height=10)
    
plot <- toplot_results %>% 
  filter(type=="hi") %>% 
  ggplot()+
  geom_line(data=length_df_plot %>% 
              filter(type=="hi") %>% 
              filter(name %in% c("begseq","begprom")),aes(x,y),col="green",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(type=="hi") %>% 
              filter(name %in% c("begprom","begthreecon")),aes(x,y),col="blue",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(type=="hi") %>%
              filter(name %in% c("begthreecon","endseq")),aes(x,y),col="green",alpha=1)+
  geom_line(data=toplot_results %>% filter(type=="hi"),aes(x,WM_score,group=ref,col=strand),alpha=0.5)+
  facet_wrap(~strain,scale="free")+
  theme(legend.position = NULL)+
  xlab("Promoter position")+
  ylab("WM_score")
  #coord_cartesian(ylim=c(-1,1))
  
ggsave("all_hi_WM_score_kinney.pdf",plot,width=15,height=10)
```

It is hard to see anything like that: I should simply look at the distributions.


```{r}
motevo_results_5 %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  #filter(strand=="+") %>% 
  ggplot()+
  stat_ecdf(aes(WM_score,col=interaction(strand,type)))+
  ylab("CDF")

motevo_results_5 %>% 
  filter(strand=="+") %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  #filter(strand=="+") %>% 
  ggplot()+
  stat_ecdf(aes(WM_score,col=interaction(strand,type)))+
  ylab("CDF")

motevo_results_5 %>% 
  filter(strand=="-") %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  #filter(strand=="+") %>% 
  ggplot()+
  stat_ecdf(aes(WM_score,col=interaction(strand,type)))+
  ylab("CDF")
```
```{r}
#post prob
motevo_results_5 %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  #filter(strand=="+") %>% 
  ggplot()+
  stat_ecdf(aes(post_prob,col=interaction(strand,type)))+
  ylab("CDF")

motevo_results_5 %>% 
  filter(strand=="+") %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  #filter(strand=="+") %>% 
  ggplot()+
  stat_ecdf(aes(post_prob,col=interaction(strand,type)))+
  ylab("CDF")

motevo_results_5 %>% 
  filter(strand=="-") %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  #filter(strand=="+") %>% 
  ggplot()+
  stat_ecdf(aes(post_prob,col=interaction(strand,type)))+
  ylab("CDF")
```

So we notice several things. There is a site that comes up in almost all data. At 2.5 or so. Always at the same position. This site is:

```{r}
# We can compute... for each promoter


  
  
```
# Correlation between these and phenotype data?

```{r}
motevo_results_5 %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  facet_wrap(~type,scale="free")+
  geom_point(aes(total_score,m_production_all))+
  ggpubr::stat_cor(aes(total_score,m_production_all))+
  xlab("WM_score")+
  theme_cowplot()

motevo_results_5 %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  facet_wrap(~type,scale="free")+
  geom_point(aes(total_score,s_glu_gluaa))+
  ggpubr::stat_cor(aes(total_score,s_glu_gluaa))+
  xlab("WM_score")+
  theme_cowplot()

motevo_results_5 %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  facet_wrap(~type,scale="free")+
  geom_point(aes(total_score,s_glu_gluaa))+
  ggpubr::stat_cor(aes(total_score,s_ace_glu))+
  xlab("WM_score")+
  coord_cartesian(ylim=c(-2,2))+
  theme_cowplot()
```

```{r}
motevo_results_5 %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score,pos) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  group_by(total_score,type) %>% 
  filter(n()>=2) %>% 
  ungroup() %>% 
  ggplot()+
  facet_wrap(~type,scale="free")+
  geom_point(aes(total_score,m_production_all,col=pos))+
  ggpubr::stat_cor(aes(total_score,m_production_all))+
  xlab("WM_score")+
  theme_cowplot()

motevo_results_5 %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  facet_wrap(~type,scale="free")+
  geom_point(aes(total_score,s_glu_gluaa))+
  ggpubr::stat_cor(aes(total_score,s_glu_gluaa))+
  xlab("WM_score")+
  theme_cowplot()

motevo_results_5 %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  facet_wrap(~type,scale="free")+
  geom_point(aes(total_score,s_glu_gluaa))+
  ggpubr::stat_cor(aes(total_score,s_ace_glu))+
  xlab("WM_score")+
  coord_cartesian(ylim=c(-2,2))+
  theme_cowplot()


```
```{r}
motevo_results_5 %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  filter(strand=="+") %>% 
  filter(type=="hi") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  filter(dplyr::between(total_score,4,5)) %>% 
  group_by(pos,total_score,sequence) %>% 
  mutate(p=n()) %>% 
  ungroup() %>% 
  distinct(p,sequence,pos,total_score) %>% 
  arrange(desc(p)) %>% 
  select(p,sequence,pos,total_score)

motevo_results_5 %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  filter(strand=="+") %>% 
  filter(type=="hi") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  filter(dplyr::between(total_score,5,6)) %>% 
  group_by(pos,total_score,sequence) %>% 
  mutate(p=n()) %>% 
  ungroup() %>% 
  distinct(p,sequence,pos,total_score) %>% 
  arrange(desc(p)) %>% 
  select(p,sequence,pos,total_score)
```


```{r}
motevo_results_5 %>% 
  filter(strand=="+") %>% 
  #group_by(strain) %>% 
  #mutate(total_score=) %>% 
  #ungroup() %>% 
  #distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  facet_wrap(~type,scale="free")+
  geom_point(aes(WM_score,m_production_all))+
  ggpubr::stat_cor(aes(WM_score,m_production_all))+
  xlab("WM_score")+
  theme_cowplot()
```
# 

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(max(WM_score))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(max(WM_score))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(max(WM_score))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```


```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(post_prob))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(post_prob))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(post_prob))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```
# Trying out with other matrices. -35 foot.

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_sigma70_35"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```
```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```

# -10 foot

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_sigma70_10"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```

```{r}
# Looking more closely at these data
minus10foot <- motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  ungroup()

# Surprise: Pribnow box right there: TATAAT
# Other box: TTGACA
# All promoters have a TATTAT or TATAAT
```

# -35 foot

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_sigma70_35"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```

```{r}
# Looking more closely at these data
minus35foot <- motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  ungroup()

# Surprise: Pribnow box right there: TATAAT
# Other box: TTGACA
# All promoters have a TATTAT or TATAAT
```

So the strategy is to use the best minus10 and the best minus35 foot that there is to find the best sites...
But maybe the best is simply to run motevo with these pwm...

# Sigma70 with different spacers

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_sigma_spacer"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(max(WM_score))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(max(WM_score))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(max(WM_score))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```

```{r}
all_spacer <- motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  ungroup()
```

I would have expected compatible results... but it does not seem to be the case:

```{r}
all_spacer %>% filter(promoter=="p2F9")
minus10foot %>% filter(promoter=="p2F9")
minus35foot %>% filter(promoter=="p2F9")
```
So looking at these sequences from the point of view of -10 foot or -35 foot, or different sigma 70 with spacers, does not really give a good prediction of the results. Now, I am curious to see: what are the predictions for single promoters, when considering these different feet/spacers?

# Looking at the length

First I would like to add promoter length to the df.
Are there many -10 feet?

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_sigma70_10"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
motevo_results %>% 
  distinct(strain,.keep_all = TRUE) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(length,s_glu_gluaa))

motevo_results %>% 
  distinct(strain,.keep_all = TRUE) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(length,m_production_all))

motevo_results %>% 
  distinct(strain,.keep_all = TRUE) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(length,s_ace_glu))
```
# Distribution of the TATA boxes (aka -10 foot).

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_sigma70_10"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

How to represent that correctly?
It is not exactly clear to me. First I would like to look at the distribution of score for each one of them. Scores and post_prob.
In a big faceted plot. Then obviously I would like to know if there are medium or hi. This information is already contained in phenotypes$type.

We know that all these are active.

```{r}
plot_med <- motevo_results %>% 
  filter(strand=="+") %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  separate(pos,into = c("beg","end")) %>% 
  filter(type=="med") %>% 
  filter(WM_score>4.5) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  mutate(rank=row_number()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(rank,WM_score))+
  facet_wrap(~promoter)

plot_hi <- motevo_results %>% 
  filter(strand=="+") %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  separate(pos,into = c("beg","end")) %>% 
  filter(type=="hi") %>% 
  filter(WM_score>4.5) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  mutate(rank=row_number()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(rank,WM_score))+
  facet_wrap(~promoter)

plot_med <- motevo_results %>% 
  filter(strand=="+") %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  separate(pos,into = c("beg","end")) %>% 
  filter(type=="med") %>% 
  filter(WM_score>2.5) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  mutate(rank=row_number()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(beg,WM_score))+
  facet_wrap(~promoter)
  
ggsave("./plot_med.pdf",plot_med,width=10,height=8)
ggsave("./plot_hi.pdf",plot_hi,width=10,height=8)

plot_hi <- motevo_results %>% 
  filter(strand=="+") %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  separate(pos,into = c("beg","end")) %>% 
  filter(type=="med") %>% 
  filter(WM_score>2.5) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  mutate(rank=row_number()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(rank,WM_score))+
  facet_wrap(~promoter)

ggsave("./plot_hi.pdf",plot_med,width=10,height=8)
  
# it looks like it is at the beginning of the sequence
# A given post_prob defines a minimum for the WM_score.
# 

plot_hi <- motevo_results %>% 
  filter(strand=="+") %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  separate(pos,into = c("beg","end")) %>% 
  filter(type=="med") %>% 
  filter(WM_score>2.5) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  mutate(rank=row_number()) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(post_prob,WM_score))
  #facet_wrap(~promoter)
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  separate(pos,into = c("beg","end")) %>% 
  #filter(type=="med") %>% 
  filter(WM_score>2) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  mutate(rank=row_number()) %>% 
  ungroup() %>% 
  ggplot()+
  stat_ecdf(aes(WM_score,col=type))

motevo_results %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1)
  
```

Ok, these sequences are found within the constant part for most of them.
Hence the analysis but must done a bit more rigorously. I need to get an idea of the position, length of the promoter, length of the 5' and 3' part as well.
And 50 bp before and after are enough. Then I should discard sites that are found at positions that are characterized by constant parts.

# Start over again

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_kinney_dany"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

Now let's represent where the sites are found. I ave an old code for that.

```{r}
selected_strain <- phenotypes %>%
  distinct(strain)

toplot_results <- motevo_results %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  filter(strand=="+") %>% 
  #filter(WM_score>0) %>% 
  mutate(total_length=length+2*100) %>% 
  group_by(strain) %>% 
  mutate(ref=as.character(row_number())) %>% 
  ungroup() %>% 
  separate(pos,into=c("beg","end")) %>% 
  pivot_longer(cols=c("beg","end"),values_to="x") %>% 
  mutate(x=as.double(x))

length_df_plot <- length_df %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  mutate(y=0) %>% 
  group_by(promoter) %>%
  mutate(endseq=length+2*100) %>% 
  mutate(begseq=1) %>% 
  mutate(begprom=101) %>% 
  mutate(begthreecon=length+100+1) %>% 
  ungroup() %>% 
  pivot_longer(cols=c("begseq","begprom","begthreecon","endseq"),values_to="x")
  
plot <- toplot_results %>% 
  ggplot()+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begseq","begprom")),aes(x,y),col="green")+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begprom","begthreecon")),aes(x,y),col="blue")+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begthreecon","endseq")),aes(x,y),col="green")+
  geom_line(data=toplot_results,aes(x,WM_score,group=ref))+
  facet_wrap(~strain,scale="free")+
  theme(legend.position = NULL)
  #coord_cartesian(ylim=c(-1,1))
  
ggsave("all_WM_score.pdf",plot,width=15,height=10)
```

```{r}
selected_strain <- phenotypes %>%
  distinct(strain)

toplot_results <- motevo_results %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  mutate(total_length=length+2*100) %>% 
  group_by(strain) %>% 
  mutate(ref=as.character(row_number())) %>% 
  ungroup() %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),
         end=as.double(end)) %>% 
  #filter((beg<=100+length) & (end>100)) %>% 
  pivot_longer(cols=c("beg","end"),values_to="x") %>% 
  mutate(x=as.double(x))

length_df_plot <- length_df %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  semi_join(toplot_results,by=c("strain")) %>% 
  mutate(y=0) %>% 
  group_by(strain) %>%
  mutate(endseq=length+2*100) %>% 
  mutate(begseq=1) %>% 
  mutate(begprom=101) %>% 
  mutate(begthreecon=length+100+1) %>% 
  ungroup() %>% 
  pivot_longer(cols=c("begseq","begprom","begthreecon","endseq"),values_to="x")
  
plot <- toplot_results %>% 
  ggplot()+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begseq","begprom")),aes(x,y),col="green",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begprom","begthreecon")),aes(x,y),col="blue",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begthreecon","endseq")),aes(x,y),col="green",alpha=1)+
  geom_line(data=toplot_results,aes(x,post_prob,group=ref,col=type),alpha=0.2)+
  facet_wrap(~strain,scale="free")+
  theme(legend.position = NULL)
  #coord_cartesian(ylim=c(-1,1))
  
ggsave("all_post_prob_constant_parts.pdf",plot,width=15,height=10)
```

I should get rid of the sequences that are completely on the sides, done.
Unfortunately, the proability look pretty bad in almost all cases.
Do they look better on the sides?
Nope.

Maybe my WM is shit?

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_kinney"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
selected_strain <- phenotypes %>%
  distinct(strain)

toplot_results <- motevo_results %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  mutate(total_length=length+2*100) %>% 
  group_by(strain) %>% 
  mutate(ref=as.character(row_number())) %>% 
  ungroup() %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),
         end=as.double(end)) %>% 
  #filter((beg<=100+length) & (end>100)) %>% 
  pivot_longer(cols=c("beg","end"),values_to="x") %>% 
  mutate(x=as.double(x))

length_df_plot <- length_df %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  semi_join(toplot_results,by=c("strain")) %>% 
  mutate(y=0) %>% 
  group_by(strain) %>%
  mutate(endseq=length+2*100) %>% 
  mutate(begseq=1) %>% 
  mutate(begprom=101) %>% 
  mutate(begthreecon=length+100+1) %>% 
  ungroup() %>% 
  pivot_longer(cols=c("begseq","begprom","begthreecon","endseq"),values_to="x")
  
plot <- toplot_results %>% 
  ggplot()+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begseq","begprom")),aes(x,y),col="green",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begprom","begthreecon")),aes(x,y),col="blue",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begthreecon","endseq")),aes(x,y),col="green",alpha=1)+
  geom_line(data=toplot_results,aes(x,post_prob,group=ref,col=type),alpha=0.5)+
  facet_wrap(~strain,scale="free")+
  theme(legend.position = NULL)
  #coord_cartesian(ylim=c(-1,1))
  
ggsave("all_post_prob_constant_parts.pdf",plot,width=15,height=10)
```


The scores look muuuch better.

```{r}
selected_strain <- phenotypes %>%
  distinct(strain)

toplot_results <- motevo_results %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  mutate(total_length=length+2*100) %>% 
  group_by(strain) %>% 
  mutate(ref=as.character(row_number())) %>% 
  ungroup() %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),
         end=as.double(end)) %>% 
  #filter((beg<=100+length) & (end>100)) %>% 
  pivot_longer(cols=c("beg","end"),values_to="x") %>% 
  mutate(x=as.double(x))

length_df_plot <- length_df %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  semi_join(toplot_results,by=c("strain")) %>% 
  mutate(y=0) %>% 
  group_by(strain) %>%
  mutate(endseq=length+2*100) %>% 
  mutate(begseq=1) %>% 
  mutate(begprom=101) %>% 
  mutate(begthreecon=length+100+1) %>% 
  ungroup() %>% 
  pivot_longer(cols=c("begseq","begprom","begthreecon","endseq"),values_to="x")
  
plot <- toplot_results %>% 
  ggplot()+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begseq","begprom")),aes(x,y),col="green",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begprom","begthreecon")),aes(x,y),col="blue",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begthreecon","endseq")),aes(x,y),col="green",alpha=1)+
  geom_line(data=toplot_results,aes(x,WM_score,group=ref,col=type),alpha=0.5)+
  facet_wrap(~strain,scale="free")+
  theme(legend.position = NULL)
  #coord_cartesian(ylim=c(-1,1))
  
ggsave("all_WM_score_constant_parts.pdf",plot,width=15,height=10)
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=beg/length) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(post_prob)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=beg/length) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(post_prob)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=post_prob) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=beg/length) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=beg/length) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```

They have something else. Something else enables them to be hi or medium. But what? Lets take a look at single foot again.

# Single foot from WM Kinney

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_kinney_minus35"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
selected_strain <- phenotypes %>%
  distinct(strain)

toplot_results <- motevo_results %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  mutate(total_length=length+2*100) %>% 
  group_by(strain) %>% 
  mutate(ref=as.character(row_number())) %>% 
  ungroup() %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),
         end=as.double(end)) %>% 
  filter((beg<=100+length) & (end>100)) %>% 
  pivot_longer(cols=c("beg","end"),values_to="x") %>% 
  mutate(x=as.double(x))

length_df_plot <- length_df %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  semi_join(toplot_results,by=c("strain")) %>% 
  mutate(y=0) %>% 
  group_by(strain) %>%
  mutate(endseq=length+2*100) %>% 
  mutate(begseq=1) %>% 
  mutate(begprom=101) %>% 
  mutate(begthreecon=length+100+1) %>% 
  ungroup() %>% 
  pivot_longer(cols=c("begseq","begprom","begthreecon","endseq"),values_to="x")
  
plot <- toplot_results %>% 
  ggplot()+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begseq","begprom")),aes(x,y),col="green",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begprom","begthreecon")),aes(x,y),col="blue",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begthreecon","endseq")),aes(x,y),col="green",alpha=1)+
  geom_line(data=toplot_results,aes(x,post_prob,group=ref,col=type),alpha=0.5)+
  facet_wrap(~strain,scale="free")+
  theme(legend.position = NULL)
  #coord_cartesian(ylim=c(-1,1))
  
ggsave("all_post_prob_constant_parts.pdf",plot,width=15,height=10)
```


The scores look muuuch better.

```{r}
selected_strain <- phenotypes %>%
  distinct(strain)

toplot_results <- motevo_results %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  mutate(total_length=length+2*100) %>% 
  group_by(strain) %>% 
  mutate(ref=as.character(row_number())) %>% 
  ungroup() %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),
         end=as.double(end)) %>% 
  filter((beg<=100+length) & (end>100)) %>% 
  pivot_longer(cols=c("beg","end"),values_to="x") %>% 
  mutate(x=as.double(x))

length_df_plot <- length_df %>% 
  semi_join(selected_strain,by=c("strain")) %>% 
  semi_join(toplot_results,by=c("strain")) %>% 
  mutate(y=0) %>% 
  group_by(strain) %>%
  mutate(endseq=length+2*100) %>% 
  mutate(begseq=1) %>% 
  mutate(begprom=101) %>% 
  mutate(begthreecon=length+100+1) %>% 
  ungroup() %>% 
  pivot_longer(cols=c("begseq","begprom","begthreecon","endseq"),values_to="x")
  
plot <- toplot_results %>% 
  ggplot()+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begseq","begprom")),aes(x,y),col="green",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begprom","begthreecon")),aes(x,y),col="blue",alpha=1)+
  geom_line(data=length_df_plot %>% 
              filter(name %in% c("begthreecon","endseq")),aes(x,y),col="green",alpha=1)+
  geom_line(data=toplot_results,aes(x,WM_score,group=ref,col=type),alpha=0.5)+
  facet_wrap(~strain,scale="free")+
  theme(legend.position = NULL)
  #coord_cartesian(ylim=c(-1,1))
  
ggsave("all_WM_score_constant_parts.pdf",plot,width=15,height=10)
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=beg/length) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(post_prob)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=beg/length) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(post_prob)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=post_prob) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=beg/length) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  filter(WM_score>0) %>% 
  separate(pos,into=c("beg","end")) %>% 
  mutate(beg=as.double(beg),end=as.double(end)) %>% 
  group_by(strain) %>% 
  arrange(desc(WM_score)) %>% 
  filter(row_number()==1) %>% 
  mutate(total_score=beg/length) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```


# Deeper investigation

Discussing with Erik, I realized a few things: first, the Sigma70 WM from McKinney, takes into account 41 bp.
But maybe I should only consider one foot?
I have other WM, such as sigma70_spacer11. 6 bp, then the linker, then 6 bp again.
The simplest, I think, would be to only take these 6 bp's: -35 first, and then -10.

# Checking the WM from Kinney and comparing with the one I got from Dorde

```{r}
correct_wm <- read_delim("./pwm/wm_kinney.txt",delim=" ")
correct_wm <- correct_wm +(-min(correct_wm))
correct_wm <- as_tibble(correct_wm) %>% 
  mutate(PO=row_number()) %>% 
  select(PO,A,C,G,T)
dorde_wm <- read_delim("./pwm/sigma70_kinney_backup.txt",delim="   ")
# Write new wm_kinney_dany
write_delim(correct_wm,"./pwm/wm_kinney_dany.txt",delim=" ")
```

Running motevo again.
```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_kinney_dany"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa,col=type))+
  theme_cowplot()
```
```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa,col=type))+
  theme_cowplot()
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(post_prob)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(post_prob)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(post_prob)) %>%  
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa,col=type))+
  theme_cowplot()
```
No good results either.
Could look at only one foot? -10?

# Looking at only one foot

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_kinney_dany_minus10"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```


```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(post_prob)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(post_prob)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(post_prob)) %>%  
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa,col=type))+
  theme_cowplot()
```

```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu,col=type))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa,col=type))+
  theme_cowplot()
```
Why is it that I am seeing the same score for ... most ! Of the sequences.

```{r}
motevo_results %>% 
  group_by(strain) %>% 
  summarise(max_prob=max(post_prob)) %>% View()
```

# Looking at -35 foot and -10 foot.

```{r}
# First I tried, only sigma70, with different spacers
set_id <- "wm_sigma70_35"
sequence_file <- "extended_proms.fasta"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/ouInference_bjoern/run_and_collect_motevo_results.R")
```






```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes,by=c("strain")) %>% 
  ggplot()+
  geom_point(aes(total_score,m_production_all))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()

motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=max(WM_score)) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_glu_gluaa))+
  theme_cowplot()
```



```{r}
motevo_results %>% 
  filter(strand=="+") %>% 
  group_by(strain) %>% 
  mutate(total_score=log(sum(exp(WM_score)))) %>% 
  ungroup() %>% 
  distinct(strain,total_score) %>% 
  left_join(phenotypes) %>% 
  ggplot()+
  geom_point(aes(total_score,s_ace_glu))+
  theme_cowplot()
```
```{r}

```


