# Manual curation of 96 well plates data
# David Schar, Dany Chauvin
# 20210302

# Loading packages and functions

```{r message=FALSE, warning=FALSE}
source("./load_packages_functions.R")
source("./modeling_functions.R")
source("./inference_functions.R")
```

# Importing all data
Here data of your choice can be imported, by providing correct paths. Here importing data which are stored in `path_to_data_list`.

```{r message=FALSE, warning=FALSE}
path_to_data_list <- "/scicore/home/nimwegen/schdav16/Projects/constitexpr/constitexpr_experiment_1/20210312_constitexpr3.0/dataList.csv"
source("./import_data.R")
mydata1 <- mydata
path_to_data_list <- "/scicore/home/nimwegen/schdav16/Projects/constitexpr/constitexpr_experiment_1/20210317_constitexpr3.1/dataList.csv"
source("./import_data.R")
mydata2 <- mydata
path_to_data_list <- "/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/constitexpr/20210208_constitexpr_testrun2/dataList.csv"
source("./import_data.R")
mydata3 <- mydata
```
# Now biding all data

```{r}
mydata <- rbind(
  mydata1,
  mydata2,
  mydata3)
```

Adding well information

```{r}
mydata <- mydata %>% 
  mutate(valid=NA) %>% 
  mutate(well=paste(plate,row,column,strain,sep="_"))

mean_blank_od <- 0.03840125
mydata <- mydata %>% 
  mutate(corrected_od=od-mean_blank_od)

mean_blank_fluo <- 35.3075
mydata <- mydata %>% 
  mutate(corrected_fluo=fluo-mean_blank_fluo) %>% 
  filter(!grepl("H_7",well))
```

# Import curated data

```{r message=FALSE, warning=FALSE}
#path_to_curated_data <- "../curated_data_dany"
#mydata_curated <- do.call(rbind, #lapply(list.files(path_to_curated_data,pattern=".csv",full.names=TRUE), readr::read_csv))
mydata_bad <- readr::read_csv("../manualCuration.csv")
mydata <- mydata %>% 
  mutate(rowcol=paste(row,column,sep=""))
replica_df <- tibble(description=unique(mydata$description),replica=c(2,3,1))
mydata_curated <- mydata %>% 
  anti_join(mydata_bad,by=c("description","plate","rowcol")) %>% 
  left_join(replica_df,by=c("description")) %>% 
  mutate(well_rep=paste(well,replica,sep="-"))
```

# Checking variability of estimated Beta from one day to the next

# ACETATE, replicate 1,2,3

```{r}
min_corrected_od <- 0.05
max_corrected_od <- 0.15
cond1 <- "acetate"
reps1 <- c(1)
reps2 <- c(2)
reps3 <- c(3)


inference_results <- rbind(
  run_inference_clean(cond1,reps1,mydata_curated),
  run_inference_clean(cond1,reps2,mydata_curated),
  run_inference_clean(cond1,reps3,mydata_curated)
  )

mydata_inferred_ace <- mydata_curated %>% 
  filter(!grepl("empty",strain)) %>% #filter out empty wells
  filter(condition==cond1) %>% 
  #filter(replica %in% reps) %>% 
  #filter(valid=="y") %>% 
  #filter(between(corrected_od,min_corrected_od,max_corrected_od)) %>% 
  filter(max(od)>min_corrected_od) %>% #to get rid of wells in which there are no growth at all
  ungroup() %>% 
  group_by(description,plate,well) %>%
  arrange(time_min) %>% 
  mutate(above_max_time=ifelse(corrected_od>=max_corrected_od,time_min,NA)) %>% 
  mutate(time_limit=min(c(above_max_time,Inf),na.rm=TRUE)) %>% 
  filter(time_min<time_limit) %>% 
  mutate(below_min_time=ifelse(corrected_od<=min_corrected_od,time_min,NA)) %>% 
  mutate(time_limit=max(c(below_min_time,-Inf),na.rm=TRUE)) %>% 
  filter(time_min>time_limit) %>% 
  ungroup() %>% 
  select(-c(above_max_time,time_limit,below_min_time)) %>% 
  left_join(inference_results,by=c("description","well","replica","condition"))
  
```

```{r}
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 24
mycolors <- colorRampPalette(brewer.pal(8, "Dark2"))(nb.cols)

mydata_inferred_ace$replica <- factor(mydata_inferred_ace$replica,levels = c(1,2,3))
for(s in unique(mydata_inferred_ace$strain)[1:10]){
print(mydata_inferred_ace %>%
    filter(strain==s) %>%
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=replica),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~replica)+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()
)}
```
```{r}
control_df <- mydata_inferred_ace %>% 
  filter(strain=="MG1655") %>% 
  mutate(mean_alpha_strain_control=mean(alpha_tot_predict)) %>% 
  group_by(replica) %>% 
  mutate(p=n()) %>% 
  mutate(mean_alpha_control_offset=mean(alpha_tot_predict-mean_alpha_strain_control)) %>% 
  mutate(mean_alpha_control=mean(alpha_tot_predict)) %>% 
  mutate(sd_alpha_control=sqrt(var(alpha_tot_predict)+sum(sd_alpha_tot**2)/p)) %>% 
  ungroup() %>% 
  distinct(replica,mean_alpha_control,sd_alpha_control,mean_alpha_strain_control,mean_alpha_control_offset)

mydata_inferred_ace %>% 
  filter(strain!="MG1655") %>% 
  filter(strain=="pl-hi1") %>% 
  left_join(control_df,by=c("replica")) %>% 
  group_by(strain) %>% 
  mutate(sd_alpha=sd(alpha_tot_predict)) %>% 
  mutate(mean_alpha=mean(alpha_tot_predict)) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(mean_alpha_control,mean_alpha),alpha=0.2)+
  geom_errorbar(aes(x=mean_alpha_control,ymax=mean_alpha+sd_alpha,ymin=mean_alpha+sd_alpha))

mydata_inferred_ace %>% 
  filter(strain!="MG1655") %>% 
  left_join(control_df,by=c("replica")) %>% 
  #group_by(strain) %>% 
  #mutate(sd_alpha=sd(alpha_tot_predict))+
  ggplot()+
  geom_boxplot(aes(x=mean_alpha_control,y=alpha_tot_predict,col=replica))+
  coord_cartesian(xlim=c(1250,2500))+
  theme_cowplot()

mydata_inferred_ace %>% 
  filter(strain!="MG1655") %>% 
  left_join(control_df,by=c("replica")) %>% 
  group_by(strain,replica) %>% 
  mutate(mean_alpha=mean(alpha_tot_predict)) %>% 
  mutate(sd_alpha=sd(alpha_tot_predict)) %>% 
  ggplot()+
  geom_point(aes(x=mean_alpha_control,y=alpha_tot_predict,col=replica))+
  coord_cartesian(xlim=c(1250,2500))+
  theme_cowplot()+
  facet_wrap(~strain,scales="free")+
  theme(strip.text = element_text(size = 20))+
    ggsave("./covariation_control_prom.pdf",width=12*5,height=7*5,limitsize = FALSE)

mydata_inferred_ace %>% 
  filter(strain!="MG1655") %>% 
  left_join(control_df,by=c("replica")) %>% 
  group_by(strain,replica) %>% 
  #mutate(mean_alpha=mean(alpha_tot_predict)) %>% 
  #mutate(sd_alpha=sd(alpha_tot_predict)) %>% 
  #distinct(strain,replica,.keep_all=TRUE) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(x=mean_alpha_control,y=alpha_tot_predict),col="black",size=3,alpha=0.5)+
  geom_errorbar(aes(x=mean_alpha_control,ymax=alpha_tot_predict+sd_alpha_tot,ymin=alpha_tot_predict-sd_alpha_tot,col=replica),width=0)+
  geom_errorbarh(aes(y=alpha_tot_predict,xmin=mean_alpha_control-sd_alpha_control,xmax=mean_alpha_control+sd_alpha_control,col=replica))+
  coord_cartesian(xlim=c(1250,2500))+
  theme_cowplot()+
  facet_wrap(~strain,scales="free")+
  theme(strip.text = element_text(size = 20))+
    ggsave("./covariation_control_prom.pdf",width=12*5,height=7*5,limitsize = FALSE)

mydata_inferred_ace %>% 
  filter(strain!="MG1655") %>% 
  left_join(control_df,by=c("replica")) %>% 
  group_by(strain,replica) %>% 
  mutate(mean_alpha=mean(alpha_tot_predict)-mean_alpha_control) %>% 
  mutate(sd_alpha=sqrt(sd(alpha_tot_predict)**2+sd(sd_alpha_control))) %>%
  #distinct(strain,replica,.keep_all=TRUE) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(x=replica,y=mean_alpha),col="black",size=3,alpha=0.5)+
  geom_errorbar(aes(x=replica,ymax=mean_alpha+sd_alpha,ymin=mean_alpha-sd_alpha,col=replica),width=0)+
  #geom_errorbarh(aes(y=mean_alpha,xmin=mean_alpha_control-sd_alpha_control,xmax=mean_alpha_control+sd_alpha_control,col=replica))+
  #coord_cartesian(xlim=c(1250,2500))+
  theme_cowplot()+
  facet_wrap(~strain,scales="free")+
  theme(strip.text = element_text(size = 20))+
    ggsave("./covariation_control_prom_minus_mean_alpha_control.pdf",width=12*5,height=7*5,limitsize = FALSE)

mydata_inferred_ace %>% 
  filter(strain!="MG1655") %>% 
  left_join(control_df,by=c("replica")) %>% 
  group_by(strain) %>% 
  mutate(mean_alpha_strain=mean(alpha_tot_predict)) %>% 
  ungroup() %>% 
  group_by(strain,replica) %>% 
  mutate(alpha_offset=alpha_tot_predict-mean_alpha_strain) %>% 
  mutate(mean_alpha_offset=mean(alpha_offset)) %>% 
  mutate(sd_alpha=sd(alpha_tot_predict)) %>%
  #distinct(strain,replica,.keep_all=TRUE) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(x=mean_alpha_control_offset,y=mean_alpha_offset),col="black",size=3,alpha=0.5)+
  geom_errorbar(aes(x=mean_alpha_control_offset,ymax=mean_alpha_offset+sd_alpha,ymin=mean_alpha_offset-sd_alpha,col=replica),width=0)+
  geom_errorbarh(aes(y=mean_alpha_offset,xmin=mean_alpha_control_offset-sd_alpha_control,xmax=mean_alpha_control_offset+sd_alpha_control,col=replica))+
  #coord_cartesian(xlim=c(1250,2500))+
  theme_cowplot()+
  facet_wrap(~strain,scales="free")+
  theme(strip.text = element_text(size = 20))+
    ggsave("./covariation_control_prom_offset.pdf",width=12*5,height=7*5,limitsize = FALSE)

mydata_inferred_ace %>% 
  filter(strain!="MG1655") %>% 
  left_join(control_df,by=c("replica")) %>% 
  group_by(strain) %>% 
  mutate(mean_alpha_strain=mean(alpha_tot_predict)) %>% 
  ungroup() %>% 
  group_by(strain,replica) %>% 
  mutate(alpha_offset=alpha_tot_predict-mean_alpha_strain) %>% 
  mutate(mean_alpha_offset=mean(alpha_offset)) %>% 
  mutate(sd_alpha=sd(alpha_tot_predict)) %>%
  #distinct(strain,replica,.keep_all=TRUE) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(x=mean_alpha_control_offset,y=mean_alpha_offset),col="black",size=3,alpha=0.5)+
  geom_errorbar(aes(x=mean_alpha_control_offset,ymax=mean_alpha_offset+sd_alpha,ymin=mean_alpha_offset-sd_alpha,col=replica),width=0)+
  geom_errorbarh(aes(y=mean_alpha_offset,xmin=mean_alpha_control_offset-sd_alpha_control,xmax=mean_alpha_control_offset+sd_alpha_control,col=replica))+
  #coord_cartesian(xlim=c(1250,2500))+
  theme_cowplot()+
  #facet_wrap(~strain,scales="free")+
  theme(strip.text = element_text(size = 20))
    #ggsave("./covariation_control_prom_offset_all.pdf",width=12*5,height=7*5,limitsize = FALSE)
```

# Implementation of Erik's method for free Beta

Given the previous results, we decided to go for a free model that assumes a alpha/beta specific to each well. Which is a much easier problem to solve.

I will therefore create a new file for that.





So there are wells that are obviously not good for controls. Ones that are too high.
Ones that are too low. And for the bulk there seem to be variations that I do not get well.

Now, How do I do to look at the co-variation?
Also, is it safe to say that the Beta is the same everyday (beta=fluorescence when there is no autofluorescence, should be close to 35).
p3-F8 has to out.

Cleaning controls
Clearly, the controls are pausing some problems there.
Some are completely off. Isolate adn check them.
They have very small slope, or very big slope.

```{r}
mydata_inferred_ace %>% 
  filter(strain=="MG1655") %>% 
  #filter(replica==2) %>% 
  distinct(replica,well,.keep_all = TRUE) %>% 
  select(replica,well,alpha_tot_predict,sd_alpha_tot,beta_predict_ite,beta_sd_ite) %>% 
  group_by(replica) %>% 
  mutate(p=n()) %>% 
  mutate(mean_alpha_tot=mean(alpha_tot_predict)) %>%
  mutate(var_alpha_day_to_day=sqrt(var(alpha_tot_predict))) %>% 
  mutate(var_alpha_inf=sqrt(sum(sd_alpha_tot**2))/p) %>%
  distinct(replica,mean_alpha_tot,var_alpha_inf,var_alpha_day_to_day,beta_predict_ite) %>% 
  arrange(replica)
  

# So clearly, this is coming from pl2_H_7_MG1655 mislabelling by David.
# I will erase that. Done.
# Then there is pl1_H_2 and pl1_G_2 that are very low. Why?

s <- "MG1655"
mydata_inferred_ace %>%
    filter(strain==s) %>%
    #filter(replica==1) %>% 
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=well),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~interaction(replica,well))+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()

s <- "MG1655"
mydata_inferred_ace %>%
    filter(strain==s) %>%
    #filter(replica==1) %>% 
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=well),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_point(aes(0,0*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),shape="+",col="red",alpha=0.2,size=5)+
    #geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~replica)+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()+
    coord_cartesian(xlim=c(0,0.15),ylim=c(0,350))
```

# GLYCEROL

```{r}
min_corrected_od <- 0.05
max_corrected_od <- 0.2
cond1 <- "glycerol"
reps1 <- c(1)
reps2 <- c(2)
reps3 <- c(3)


inference_results <- rbind(
  run_inference_clean(cond1,reps1,mydata_curated),
  run_inference_clean(cond1,reps2,mydata_curated),
  run_inference_clean(cond1,reps3,mydata_curated)
  )

mydata_inferred_gly <- mydata_curated %>% 
  filter(!grepl("empty",strain)) %>% #filter out empty wells
  filter(condition==cond1) %>% 
  #filter(replica %in% reps) %>% 
  #filter(valid=="y") %>% 
  #filter(between(corrected_od,min_corrected_od,max_corrected_od)) %>% 
  filter(max(od)>min_corrected_od) %>% #to get rid of wells in which there are no growth at all
  ungroup() %>% 
  group_by(description,plate,well) %>%
  arrange(time_min) %>% 
  mutate(above_max_time=ifelse(corrected_od>=max_corrected_od,time_min,NA)) %>% 
  mutate(time_limit=min(c(above_max_time,Inf),na.rm=TRUE)) %>% 
  filter(time_min<time_limit) %>% 
  mutate(below_min_time=ifelse(corrected_od<=min_corrected_od,time_min,NA)) %>% 
  mutate(time_limit=max(c(below_min_time,-Inf),na.rm=TRUE)) %>% 
  filter(time_min>time_limit) %>% 
  ungroup() %>% 
  select(-c(above_max_time,time_limit,below_min_time)) %>% 
  left_join(inference_results,by=c("description","well","replica","condition"))
  
```


```{r}
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 24
mycolors <- colorRampPalette(brewer.pal(8, "Dark2"))(nb.cols)

mydata_inferred_gly$replica <- factor(mydata_inferred_gly$replica,levels = c(1,2,3))
for(s in unique(mydata_inferred_gly$strain)[1:10]){
print(mydata_inferred_gly %>%
    filter(strain==s) %>%
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=replica),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~replica)+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()
    )}
```

```{r}
mydata_inferred_gly %>% 
  filter(strain=="MG1655") %>% 
  #filter(replica==2) %>% 
  distinct(replica,well,.keep_all = TRUE) %>% 
  select(replica,well,alpha_tot_predict,sd_alpha_tot,beta_predict_ite,beta_sd_ite) %>% 
  group_by(replica) %>% 
  mutate(p=n()) %>% 
  mutate(mean_alpha_tot=mean(alpha_tot_predict)) %>%
  mutate(var_alpha_day_to_day=sqrt(var(alpha_tot_predict))) %>% 
  mutate(var_alpha_inf=sqrt(sum(sd_alpha_tot**2))/p) %>%
  distinct(replica,mean_alpha_tot,var_alpha_inf,var_alpha_day_to_day,beta_predict_ite) %>% 
  arrange(replica)
  

# So clearly, this is coming from pl2_H_7_MG1655 mislabelling by David.
# I will erase that. Done.
# Then there is pl1_H_2 and pl1_G_2 that are very low. Why?

s <- "MG1655"
mydata_inferred_gly %>%
    filter(strain==s) %>%
    #filter(replica==1) %>% 
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=well),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~interaction(replica,well))+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()

s <- "MG1655"
mydata_inferred_gly %>%
    filter(strain==s) %>%
    #filter(replica==1) %>% 
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=well),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_point(aes(0,0*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),shape="+",col="red",alpha=0.2,size=5)+
    #geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~replica)+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()+
    coord_cartesian(xlim=c(0,0.2),ylim=c(0,250))
```
# GLUCOSE

```{r}
min_corrected_od <- 0.05
max_corrected_od <- 0.4
cond1 <- "glucose"
reps1 <- c(1)
reps2 <- c(2)
reps3 <- c(3)


inference_results <- rbind(
  run_inference_clean(cond1,reps1,mydata_curated),
  run_inference_clean(cond1,reps2,mydata_curated),
  run_inference_clean(cond1,reps3,mydata_curated)
  )

mydata_inferred_glu <- mydata_curated %>% 
  filter(!grepl("empty",strain)) %>% #filter out empty wells
  filter(condition==cond1) %>% 
  #filter(replica %in% reps) %>% 
  #filter(valid=="y") %>% 
  #filter(between(corrected_od,min_corrected_od,max_corrected_od)) %>% 
  filter(max(od)>min_corrected_od) %>% #to get rid of wells in which there are no growth at all
  ungroup() %>% 
  group_by(description,plate,well) %>%
  arrange(time_min) %>% 
  mutate(above_max_time=ifelse(corrected_od>=max_corrected_od,time_min,NA)) %>% 
  mutate(time_limit=min(c(above_max_time,Inf),na.rm=TRUE)) %>% 
  filter(time_min<time_limit) %>% 
  mutate(below_min_time=ifelse(corrected_od<=min_corrected_od,time_min,NA)) %>% 
  mutate(time_limit=max(c(below_min_time,-Inf),na.rm=TRUE)) %>% 
  filter(time_min>time_limit) %>% 
  ungroup() %>% 
  select(-c(above_max_time,time_limit,below_min_time)) %>% 
  left_join(inference_results,by=c("description","well","replica","condition"))
  
```
```{r}
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 24
mycolors <- colorRampPalette(brewer.pal(8, "Dark2"))(nb.cols)

mydata_inferred_glu$replica <- factor(mydata_inferred_glu$replica,levels = c(1,2,3))
for(s in unique(mydata_inferred_glu$strain)[1:10]){
print(mydata_inferred_glu %>%
    filter(strain==s) %>%
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=replica),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~replica)+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()
    )}
```

```{r}
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 8
mycolors <- colorRampPalette(brewer.pal(8, "Set1"))(nb.cols)


mydata_inferred_glu %>% 
  filter(strain=="MG1655") %>% 
  #filter(replica==2) %>% 
  distinct(replica,well,.keep_all = TRUE) %>% 
  select(replica,well,alpha_tot_predict,sd_alpha_tot,beta_predict_ite,beta_sd_ite) %>% 
  group_by(replica) %>% 
  mutate(p=n()) %>% 
  mutate(mean_alpha_tot=mean(alpha_tot_predict)) %>%
  mutate(var_alpha_day_to_day=sqrt(var(alpha_tot_predict))) %>% 
  mutate(var_alpha_inf=sqrt(sum(sd_alpha_tot**2))/p) %>%
  distinct(replica,mean_alpha_tot,var_alpha_inf,var_alpha_day_to_day,beta_predict_ite) %>% 
  arrange(replica)
  

# So clearly, this is coming from pl2_H_7_MG1655 mislabelling by David.
# I will erase that. Done.
# Then there is pl1_H_2 and pl1_G_2 that are very low. Why?



s <- "MG1655"
mydata_inferred_glu %>%
    filter(strain==s) %>%
    #filter(replica==1) %>% 
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=replica),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~interaction(replica,well))+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()



s <- "MG1655"
mydata_inferred_glu %>%
    filter(strain==s) %>%
    #filter(replica==1) %>% 
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=well),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_point(aes(0,0*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),shape="+",col="red",alpha=0.2,size=5)+
    #geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~replica)+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()+
    coord_cartesian(xlim=c(0,0.4),ylim=c(0,350))
```

# GLUCOSE

```{r}
min_corrected_od <- 0.05
max_corrected_od <- 0.6
cond1 <- "glucoseaa"
reps1 <- c(1)
reps2 <- c(2)
reps3 <- c(3)


inference_results <- rbind(
  run_inference_clean(cond1,reps1,mydata_curated),
  #run_inference_clean(cond1,reps2,mydata_curated),
  run_inference_clean(cond1,reps3,mydata_curated)
  )

mydata_inferred_gluaa <- mydata_curated %>% 
  filter(!grepl("empty",strain)) %>% #filter out empty wells
  filter(condition==cond1) %>% 
  #filter(replica %in% reps) %>% 
  #filter(valid=="y") %>% 
  #filter(between(corrected_od,min_corrected_od,max_corrected_od)) %>% 
  filter(max(od)>min_corrected_od) %>% #to get rid of wells in which there are no growth at all
  ungroup() %>% 
  group_by(description,plate,well) %>%
  arrange(time_min) %>% 
  mutate(above_max_time=ifelse(corrected_od>=max_corrected_od,time_min,NA)) %>% 
  mutate(time_limit=min(c(above_max_time,Inf),na.rm=TRUE)) %>% 
  filter(time_min<time_limit) %>% 
  mutate(below_min_time=ifelse(corrected_od<=min_corrected_od,time_min,NA)) %>% 
  mutate(time_limit=max(c(below_min_time,-Inf),na.rm=TRUE)) %>% 
  filter(time_min>time_limit) %>% 
  ungroup() %>% 
  select(-c(above_max_time,time_limit,below_min_time)) %>% 
  left_join(inference_results,by=c("description","well","replica","condition"))
  
```

```{r}
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 24
mycolors <- colorRampPalette(brewer.pal(8, "Set1"))(nb.cols)

mydata_inferred_gluaa$replica <- factor(mydata_inferred_gluaa$replica,levels = c(1,2,3))
for(s in unique(mydata_inferred_gluaa$strain)[1:10]){
print(mydata_inferred_gluaa %>%
    filter(strain==s) %>%
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=replica),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~replica)+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()
    )}
```

```{r}
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 8
mycolors <- colorRampPalette(brewer.pal(8, "Set1"))(nb.cols)


mydata_inferred_gluaa %>% 
  filter(strain=="MG1655") %>% 
  #filter(replica==2) %>% 
  distinct(replica,well,.keep_all = TRUE) %>% 
  select(replica,well,alpha_tot_predict,sd_alpha_tot,beta_predict_ite,beta_sd_ite) %>% 
  group_by(replica) %>% 
  mutate(p=n()) %>% 
  mutate(mean_alpha_tot=mean(alpha_tot_predict)) %>%
  mutate(var_alpha_day_to_day=var(alpha_tot_predict)) %>% 
  mutate(var_alpha_inf=sqrt(sum(sd_alpha_tot**2))/p) %>%
  distinct(replica,mean_alpha_tot,var_alpha_inf,var_alpha_day_to_day,beta_predict_ite) %>% 
  arrange(replica)
  

# So clearly, this is coming from pl2_H_7_MG1655 mislabelling by David.
# I will erase that. Done.
# Then there is pl1_H_2 and pl1_G_2 that are very low. Why?



s <- "MG1655"
mydata_inferred_gluaa %>%
    filter(strain==s) %>%
    #filter(replica==1) %>% 
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=replica),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~interaction(replica,well))+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()



s <- "MG1655"
mydata_inferred_gluaa %>%
    filter(strain==s) %>%
    #filter(replica==1) %>% 
    ggplot() +
    geom_point(aes(corrected_od,fluo,col=well),alpha=1)+
    geom_line(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),col="red",alpha=0.2)+
    geom_point(aes(0,0*alpha_tot_predict+beta_predict_ite,group=interaction(replica,well)),shape="+",col="red",alpha=0.2,size=5)+
    #geom_text(aes(x = -Inf, y = -Inf, label = s),size=5,vjust=-0.2,hjust=-0.2)+
    facet_wrap(~replica)+
    xlab("corrected_od")+
    ylab("fluo")+
    scale_color_manual(values = mycolors)+
    theme_cowplot()+
    coord_cartesian(xlim=c(0,0.6),ylim=c(0,350))
```






# GLYCEROL

```{r}
min_corrected_od <- 0.05
max_corrected_od <- 0.2
cond <- "glycerol"
```

```{r}
source("./run_inference.R")
```

```{r}
mydata_inferred_gly <- mydata_curated_cond %>% 
  left_join(mydata_inference,by=c("well","description"))
  #distinct(well,.keep_all = TRUE)

mydata_inferred_gly %>% 
  distinct(strain,.keep_all=TRUE) %>% 
  ggplot()+
  stat_ecdf(aes(alpha_tot_predict))+
  theme_cowplot()
```

```{r}
for(w in unique(mydata_inferred_gly$well)[1:10]){
print(mydata_inferred_gly %>%
    filter(well==w) %>%
    ggplot() +
    geom_point(aes(corrected_od,fluo),alpha=0.2,col="black")+
    geom_point(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite),col="red")+
    xlab("log(c_od)")+
    ylab("fluo")+theme_cowplot()
    )}
```

# GLUCOSE

```{r}
min_corrected_od <- 0.05
max_corrected_od <- 0.4
cond <- "glucose"
```

```{r}
source("./run_inference.R")
```

```{r}
mydata_inferred_gluaa <- mydata_curated_cond %>% 
  left_join(mydata_inference,by=c("well","description"))
  #distinct(well,.keep_all = TRUE)

mydata_inferred_gluaa %>% 
  distinct(strain,.keep_all=TRUE) %>% 
  ggplot()+
  stat_ecdf(aes(alpha_tot_predict))+
  theme_cowplot()
```

```{r}
for(w in unique(mydata_inferred_glu$well)[1:10]){
print(mydata_inferred_glu %>%
    filter(well==w) %>%
    ggplot() +
    geom_point(aes(corrected_od,fluo),alpha=0.2,col="black")+
    geom_point(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite),col="red")+
    xlab("log(c_od)")+
    ylab("fluo")+theme_cowplot()
    )}
```

# GLUCOSEAA

```{r}
min_corrected_od <- 0.05
max_corrected_od <- 0.6
cond <- "glucoseaa"
```

```{r}
source("./run_inference.R")
```

```{r}
mydata_inferred_gluaa <- mydata_curated_cond %>% 
  left_join(mydata_inference,by=c("well","description"))
  #distinct(well,.keep_all = TRUE)

mydata_inferred_gluaa %>% 
  distinct(strain,.keep_all=TRUE) %>% 
  ggplot()+
  stat_ecdf(aes(alpha_tot_predict))+
  theme_cowplot()
```

```{r}
for(w in unique(mydata_inferred_gluaa$well)[1:10]){
print(mydata_inferred_gluaa %>%
    filter(well==w) %>%
    ggplot() +
    geom_point(aes(corrected_od,fluo),alpha=0.2,col="black")+
    geom_point(aes(corrected_od,corrected_od*alpha_tot_predict+beta_predict_ite),col="red")+
    xlab("log(c_od)")+
    ylab("fluo")+theme_cowplot()
    )}
```

# All data together

```{r}
mydata_inferred_all <- rbind(
  mydata_inferred_ace %>% 
    distinct(description,well,.keep_all = TRUE),
  
  mydata_inferred_gly %>% 
    distinct(description,well,.keep_all = TRUE),

  mydata_inferred_glu%>% 
    distinct(description,well,.keep_all = TRUE),
  
  mydata_inferred_gluaa%>% 
    distinct(description,well,.keep_all = TRUE))
```

```{r}
readr::write_csv(mydata_inferred_all,"./mydata_inferred_all.csv")
```

```{r message=FALSE, warning=FALSE}
gr_df <- tibble(gr=c(0.2,0.5,1),condition=c("acetate","glycerol","glucose"))

mydata_inferred_all %>% 
  left_join(gr_df,by=c("condition")) %>% 
  filter(grepl("p2-",strain)) %>% 
  ggplot()+
  geom_point(aes(gr,alpha_tot_predict,col=condition))+
  geom_errorbar(aes(x=gr,ymin=alpha_tot_predict-sd_alpha_tot,ymax=alpha_tot_predict+sd_alpha_tot))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("alpha (GFP + autofluorescence)")
  #facet_wrap(~well,scales="free")
```


```{r,message=FALSE,warning=FALSE}
mystrain <- unique(mydata_inferred_all$strain)

mydata_inferred_control <- mydata_inferred_all %>% 
  filter(strain=="MG1655") %>% 
  distinct(well,.keep_all = TRUE) %>% 
  group_by(condition) %>% 
  mutate(p=n()) %>% 
  mutate(alpha_0_mean=mean(alpha_tot_predict)) %>% 
  mutate(alpha_0_sd=sqrt(sum(sd_alpha_tot**2)/(p**2)+var(alpha_tot_predict))) %>% 
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  select(condition,alpha_0_mean,alpha_0_sd)
```

```{r}
mydata_inferred_all_control <- mydata_inferred_all %>%
  left_join(mydata_inferred_control,by=c("condition")) %>% 
  group_by(strain,condition) %>% 
  filter(n()>=2) %>% 
  mutate(p=n()) %>% 
  mutate(alpha_gfp=mean(alpha_tot_predict-mean(alpha_0_mean))) %>% 
  mutate(sd_alpha_gfp=sqrt(sum(sd_alpha_tot**2)/(p**2)+alpha_0_sd**2+var(alpha_tot_predict))) %>% 
  ungroup()
```

# Save the data for future analysis

```{r}
mydata_inferred_all_control %>% 
  readr::write_csv("./20210329_inference_results_constitexpr_all.csv")
```

# Comparison with mother machine data

Fetch mother machine data first.

Loading mother machine data, using the correct script in ouInferenceBjorn, dataAnalysis.Rmd.
Using the length and width (small and big axis to reconstruct the total cell volume).

The total volume is given by:

((length_um-width_um)*(width_um/2)**2*3.14)+4/3*3.14*(width_um/2)***3

```{r}
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 18
mycolors <- colorRampPalette(brewer.pal(8, "Set2"))(nb.cols)


#myframes_to_mycells
#mycells
myframes_to_mycells <- myframes_to_mycells %>% 
  mutate(volume_um=((length_um-width_um)*(width_um/2)**2*3.14)+4/3*3.14*(width_um/2)**3) %>%
  mutate(concentration_length=gfp_nb/length_um) %>% 
  mutate(concentration_volume=gfp_nb/volume_um) %>% 
  group_by(promoter,condition) %>% 
  mutate(mean_concentration_length=mean(concentration_length,na.rm=TRUE)) %>% 
  mutate(mean_concentration_volume=mean(concentration_volume,na.rm=TRUE)) %>% 
  mutate(sd_concentration_length=sd(concentration_length,na.rm=TRUE)) %>% 
  mutate(sd_concentration_volume=sd(concentration_volume,na.rm=TRUE))

gr_df <- mycells %>% 
  group_by(condition,promoter) %>% 
  mutate(mean_alpha=mean(alpha,na.rm=TRUE)) %>% 
  mutate(mean_doubling_time=mean_alpha*3600/log(2)) %>% 
  distinct(condition,promoter,.keep_all = TRUE ) %>% 
  select(condition, promoter, mean_doubling_time,mean_alpha) %>% 
  ungroup()

```

```{r}
myframes_to_mycells %>% 
  left_join(gr_df,by=c("condition","promoter")) %>% 
  distinct(promoter,condition,.keep_all=TRUE) %>%
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_length),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_length),col=promoter))+
  scale_color_manual(values = mycolors)+
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(<Concentration>) (length based)")
  #facet_wrap(~promoter)
  
myframes_to_mycells %>% 
  left_join(gr_df,by=c("condition","promoter")) %>% 
  distinct(promoter,condition,.keep_all=TRUE) %>%
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  scale_fill_manual(values = mycolors) +
  #facet_wrap(~promoter)+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(<Concentration>) (volume based)")
```
Correction for proper volume does not change anything. Mother machine data stays the same.
Now let's compare the plate's data and mother machine data.

```{r}
myconcentrations <- myframes_to_mycells %>%
  distinct(condition,promoter,.keep_all = TRUE) %>% 
  left_join(gr_df,by=c("condition","promoter")) %>% 
  select(condition,promoter,mean_concentration_length,mean_concentration_volume,sd_concentration_length,sd_concentration_volume)

promoters_of_interest <- list("hi1","hi3","med2","med3","rpsB","rpmB","rplN","rrnB")
```

There is some uncertainty on the alpha's that I need to sum up.

```{r}
#No need to go for a reference, I can simply check all ratios
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 18
mycolors <- colorRampPalette(brewer.pal(8, "Set2"))(nb.cols)

myconcentrations$condition <- factor(myconcentrations$condition, levels = c("acetate","glycerol","glucose","glucoseaa"))

mydata_wells <- mydata_inferred_all_control %>%
  separate(strain,into=c("vector","promoter")) %>%
  filter(promoter %in% promoters_of_interest) %>% 
  filter(vector=="pl") %>% 
  distinct(promoter,condition,well,.keep_all = TRUE) %>% 
  select(promoter,condition,well,alpha_gfp,sd_alpha_gfp)
    
myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>%
  mutate(ratio=mean_concentration_volume/alpha_gfp) %>%
  ggplot()+
  geom_point(aes(log(mean_concentration_volume),log(alpha_gfp),col=promoter),size=4)+
  geom_errorbar(aes(x=log(mean_concentration_volume),ymax=log(alpha_gfp+sd_alpha_gfp),ymin=log(alpha_gfp-sd_alpha_gfp)))+
  geom_errorbarh(aes(y=log(alpha_gfp),xmax=log(mean_concentration_volume+sd_concentration_volume),xmin=log(mean_concentration_volume-sd_concentration_volume)))+
  stat_smooth(aes(log(mean_concentration_volume),log(alpha_gfp)),method="lm", fullrange=TRUE,col='blue',alpha=0.2)+
    ggpubr::stat_cor(aes(log(mean_concentration_volume),log(alpha_gfp)),method = "pearson",size=4, label.y.npc = 0.8,label.x.npc = 0)+
    ggpubr::stat_regline_equation(aes(log(mean_concentration_volume),log(alpha_gfp)),size=4,label.y.npc = 1,label.x.npc = 0)+
  facet_wrap(~condition,scale="free")+
  scale_color_manual(values = mycolors)+
  theme_cowplot()+
  xlab("log(<Concentration>), mother Machine")+
  ylab("log(<alpha GFP>), bulk")+
  labs(subtitle=("Bulk (plasmid) vs Mother Machine (chromosome) "))
```



```{r}
mydata_wells <- mydata_inferred_all_control %>%
  separate(strain,into=c("vector","promoter")) %>%
  filter(promoter %in% promoters_of_interest) %>% 
  filter(vector=="ch") %>% 
  filter(promoter!="med2") %>% 
  distinct(promoter,condition,well,.keep_all = TRUE) %>% 
  select(promoter,condition,well,alpha_gfp,sd_alpha_gfp)

myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>%
  mutate(ratio=mean_concentration_volume/alpha_gfp) %>%
  ggplot()+
  geom_point(aes(log(mean_concentration_volume),log(alpha_gfp),col=promoter),size=4)+
  geom_errorbar(aes(x=log(mean_concentration_volume),ymax=log(alpha_gfp+sd_alpha_gfp),ymin=log(alpha_gfp-sd_alpha_gfp)))+
  geom_errorbarh(aes(y=log(alpha_gfp),xmax=log(mean_concentration_volume+sd_concentration_volume),xmin=log(mean_concentration_volume-sd_concentration_volume)))+
  stat_smooth(aes(log(mean_concentration_volume),log(alpha_gfp)),method="lm", fullrange=TRUE,col='blue',alpha=0.2)+
    ggpubr::stat_cor(aes(log(mean_concentration_volume),log(alpha_gfp)),method = "pearson",size=4, label.y.npc = 0.8,label.x.npc = 0)+
    ggpubr::stat_regline_equation(aes(log(mean_concentration_volume),log(alpha_gfp)),size=4,label.y.npc = 1,label.x.npc = 0)+
  facet_wrap(~condition,scale="free")+
  scale_color_manual(values = mycolors)+
  theme_cowplot()+
  xlab("log(<Concentration>), mother Machine")+
  ylab("log(<alpha GFP>), bulk")+
  labs(subtitle=("Bulk (chromosome) vs Mother Machine (chromosome) "))
```

It is hard to compare here, because the strains are slightly different. I am actually tempted to do the same, without any proper change.
These slopes can be used to say something about how the concentration really changes together with the growth rate for plasmid species... except that my ground truth is NOT, in plasmid, it is within the chromosome. How am I going to get out of that?

Which also mean that we do not need to these experiments to establish the concentration. We can simply use this "calibration curve", to determine the "real concentration", for other promoters as well. This concentration, should give us together with the growth rate, the actual production, by simply measuring the growth rate.

But now, what I should do is redo these experiments, 8 promoters at a time, in the plasmid.

But what I am showing here is that, the response to growth rate, in plasmid and chromosome is the same.
The difference of power is certainly due to chromosome versus plasmid there.


```{r}
#No need to go for a reference, I can simply check all ratios
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 18
mycolors <- colorRampPalette(brewer.pal(8, "Set2"))(nb.cols)

myconcentrations$condition <- factor(myconcentrations$condition, levels = c("acetate","glycerol","glucose","glucoseaa"))

mydata_wells <- mydata_inferred_all_control %>%
  separate(strain,into=c("vector","promoter")) %>%
  filter(promoter %in% promoters_of_interest) %>% 
  filter(vector=="pl") %>% 
  distinct(promoter,condition,well,.keep_all = TRUE) %>% 
  select(promoter,condition,well,alpha_gfp,sd_alpha_gfp)
    
myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>%
  mutate(ratio=mean_concentration_volume/alpha_gfp) %>%
  ggplot()+
  geom_point(aes(mean_concentration_volume,alpha_gfp,col=promoter),size=4)+
  geom_errorbar(aes(x=mean_concentration_volume,ymax=alpha_gfp+sd_alpha_gfp,ymin=alpha_gfp-sd_alpha_gfp))+
  geom_errorbarh(aes(y=alpha_gfp,xmax=mean_concentration_volume+sd_concentration_volume,xmin=mean_concentration_volume-sd_concentration_volume))+
  stat_smooth(aes(mean_concentration_volume,alpha_gfp),formula=y~x+0,method="lm", fullrange=TRUE,col='blue',alpha=0.2)+
    ggpubr::stat_cor(aes(mean_concentration_volume,alpha_gfp),method = "pearson",size=4, label.y.npc = 0.8,label.x.npc = 0)+
    ggpubr::stat_regline_equation(aes(mean_concentration_volume,alpha_gfp),formula=y~x+0,size=4,label.y.npc = 1,label.x.npc = 0)+
  facet_wrap(~condition,scale="free")+
  scale_color_manual(values = mycolors)+
  theme_cowplot()+
  xlab("<Concentration>, mother Machine")+
  ylab("<alpha GFP>, bulk")+
  labs(subtitle=("Bulk (plasmid) vs Mother Machine (chromosome) "))
```

```{r}
#No need to go for a reference, I can simply check all ratios
library(RColorBrewer)
# Définissez le nombre de couleurs que vous voulez
nb.cols <- 18
mycolors <- colorRampPalette(brewer.pal(8, "Set2"))(nb.cols)

myconcentrations$condition <- factor(myconcentrations$condition, levels = c("acetate","glycerol","glucose","glucoseaa"))

mydata_wells <- mydata_inferred_all_control %>%
  separate(strain,into=c("vector","promoter")) %>%
  filter(promoter %in% promoters_of_interest) %>% 
  filter(vector=="ch") %>% 
  filter(promoter!="med2") %>% 
  distinct(promoter,condition,well,.keep_all = TRUE) %>% 
  select(promoter,condition,well,alpha_gfp,sd_alpha_gfp)
    
myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>%
  mutate(ratio=mean_concentration_volume/alpha_gfp) %>%
  ggplot()+
  geom_point(aes(mean_concentration_volume,alpha_gfp,col=promoter),size=4)+
  geom_errorbar(aes(x=mean_concentration_volume,ymax=alpha_gfp+sd_alpha_gfp,ymin=alpha_gfp-sd_alpha_gfp))+
  geom_errorbarh(aes(y=alpha_gfp,xmax=mean_concentration_volume+sd_concentration_volume,xmin=mean_concentration_volume-sd_concentration_volume))+
  stat_smooth(aes(mean_concentration_volume,alpha_gfp),formula=y~x+0,method="lm", fullrange=TRUE,col='blue',alpha=0.2)+
    ggpubr::stat_cor(aes(mean_concentration_volume,alpha_gfp),method = "pearson",size=4, label.y.npc = 0.8,label.x.npc = 0)+
    ggpubr::stat_regline_equation(aes(mean_concentration_volume,alpha_gfp),formula=y~x+0,size=4,label.y.npc = 1,label.x.npc = 0)+
  facet_wrap(~condition,scale="free")+
  scale_color_manual(values = mycolors)+
  theme_cowplot()+
  xlab("<Concentration>, mother Machine")+
  ylab("<alpha GFP>, bulk")+
  labs(subtitle=("Bulk (chromosome) vs Mother Machine (chromosome) "))
```

Now redo the previous plot by transforming all data with the corresponding factor.

```{r message=FALSE,warning=FALSE}

scaling_factor <- tibble(condition=c("acetate","glycerol","glucose","glucoseaa"),scaling_factor_chromosomal=c(0.29,0.22,0.18,0.23),scaling_factor_plasmid=c(1.5,0.99,0.67,0.91))

mydata_wells <- mydata_inferred_all_control %>%
  separate(strain,into=c("vector","promoter")) %>%
  filter(promoter %in% promoters_of_interest) %>% 
  filter(vector=="ch") %>% 
  filter(promoter!="med2") %>% 
  #group_by(promoter,condition) %>% 
  #mutate(mean_alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  ungroup() %>% 
  distinct(promoter,condition,well,.keep_all = TRUE) %>% 
  select(promoter,condition,well,alpha_gfp,sd_alpha_gfp)

myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>%
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_chromosomal) %>%
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_chromosomal) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(corrected_alpha_gfp),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(corrected_alpha_gfp),col=promoter))+
  geom_errorbar(aes(x=log(mean_doubling_time),ymax=log(corrected_alpha_gfp+corrected_sd_alpha_gfp),ymin=log(corrected_alpha_gfp-corrected_sd_alpha_gfp)))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  #facet_wrap(~promoter)+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Corrected alpha (GFP)), bulk")+
  coord_cartesian(ylim=c(2,12))+
  labs(subtitle="Chromosomal strains")

myconcentrations %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  geom_errorbar(aes(log(mean_doubling_time),ymax=log(mean_concentration_volume+sd_concentration_volume),ymin=log(mean_concentration_volume-sd_concentration_volume)))+
  #geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  #facet_wrap(~promoter)+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Concentration (#GFP/um3), mother machine")+
  coord_cartesian(ylim=c(2,12))

```


```{r message=FALSE,warning=FALSE}

scaling_factor <- tibble(condition=c("acetate","glycerol","glucose","glucoseaa"),scaling_factor_chromosomal=c(0.29,0.22,0.18,0.23),scaling_factor_plasmid=c(1.5,0.99,0.67,0.91))

#gr_df_cond <- gr_df %>% 
#  group_by(condition) %>% 
#  mutate(mean_mean_alpha=mean(mean_alpha,na.rm=TRUE)) %>% 
#  mutate(mean_mean_doubling_time=mean(mean_doubling_time,na.rm=TRUE)) %>% 
#  ungroup() %>% 
#  distinct(condition,.keep_all = TRUE) %>% 
#  select(condition,mean_mean_alpha,mean_mean_doubling_time)

mydata_wells <- mydata_inferred_all_control %>%
  separate(strain,into=c("vector","promoter")) %>%
  filter(promoter %in% promoters_of_interest) %>% 
  filter(vector=="pl") %>% 
  #group_by(promoter,condition) %>% 
  #mutate(mean_alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(promoter,condition,well,.keep_all = TRUE) %>%
  select(promoter,condition,well,alpha_gfp,sd_alpha_gfp)

myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>%
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>%
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(corrected_alpha_gfp),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(corrected_alpha_gfp),col=promoter))+
  geom_errorbar(aes(x=log(mean_doubling_time),ymax=log(corrected_alpha_gfp+corrected_sd_alpha_gfp),ymin=log(corrected_alpha_gfp-corrected_sd_alpha_gfp)))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  #facet_wrap(~promoter)+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Corrected alpha (GFP)), bulk")+
  coord_cartesian(ylim=c(2,12))+
  labs(subtitle="Plasmid strains")

myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>%
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>%
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(corrected_alpha_gfp),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(corrected_alpha_gfp),col=promoter))+
  geom_errorbar(aes(x=log(mean_doubling_time),ymax=log(corrected_alpha_gfp+corrected_sd_alpha_gfp),ymin=log(corrected_alpha_gfp-corrected_sd_alpha_gfp)))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  facet_wrap(~promoter,scale="free")+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Corrected alpha (GFP)), bulk")+
  #coord_cartesian(ylim=c(2,12))+
  labs(subtitle="Plasmid strains")

myconcentrations %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  geom_errorbar(aes(log(mean_doubling_time),ymax=log(mean_concentration_volume+sd_concentration_volume),ymin=log(mean_concentration_volume-sd_concentration_volume)))+
  #geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  #facet_wrap(~promoter)+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Concentration (#GFP/um3), mother machine")+
  coord_cartesian(ylim=c(2,12))

myconcentrations %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  geom_errorbar(aes(log(mean_doubling_time),ymax=log(mean_concentration_volume+sd_concentration_volume),ymin=log(mean_concentration_volume-sd_concentration_volume)))+
  #geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  facet_wrap(~promoter,scale="free")+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Concentration (#GFP/um3), mother machine")
  #coord_cartesian(ylim=c(2,12))

# Production

myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>%
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>%
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_errorbar(aes(x=log(mean_doubling_time),ymax=log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600+corrected_sd_alpha_gfp*mean_doubling_time*log(2)/3600),ymin=log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600-corrected_sd_alpha_gfp*mean_doubling_time*log(2)/3600)))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  #facet_wrap(~promoter)+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Production), bulk")+
  #oord_cartesian(ylim=c(2,12))+
  labs(subtitle="Plasmid strains")

myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>%
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>%
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_errorbar(aes(x=log(mean_doubling_time),ymax=log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600+corrected_sd_alpha_gfp*mean_doubling_time*log(2)/3600),ymin=log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600-corrected_sd_alpha_gfp*mean_doubling_time*log(2)/3600)))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  facet_wrap(~promoter,scale="free")+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Production), bulk")+
  #coord_cartesian(ylim=c(2,12))+
  labs(subtitle="Plasmid strains")

myconcentrations %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_errorbar(aes(log(mean_doubling_time),ymax=log(mean_concentration_volume*mean_doubling_time*log(2)/3600+sd_concentration_volume*mean_doubling_time*log(2)/3600),ymin=log(mean_concentration_volume*mean_doubling_time*log(2)/3600-sd_concentration_volume*mean_doubling_time*log(2)/3600)))+
  #geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  #facet_wrap(~promoter)+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Production), mother machine")
  #coord_cartesian(ylim=c(2,12))

myconcentrations %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_errorbar(aes(log(mean_doubling_time),ymax=log(mean_concentration_volume*mean_doubling_time*log(2)/3600+sd_concentration_volume*mean_doubling_time*log(2)/3600),ymin=log(mean_concentration_volume*mean_doubling_time*log(2)/3600-sd_concentration_volume*mean_doubling_time*log(2)/3600)))+
  #geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  facet_wrap(~promoter,scale="free")+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Production), mother machine")
  #coord_cartesian(ylim=c(2,12))



myconcentrations %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  mutate(q=mean_concentration_volume*mean_doubling_time*log(2)/3600) %>% 
  filter(promoter=="rrnB") %>% 
  distinct(condition,q)
```

```{r}
myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>%
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>%
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600),col="blue"))+
  geom_line(aes(log(mean_doubling_time),log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600),col="blue"))+
  geom_errorbar(aes(x=log(mean_doubling_time),ymax=log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600+corrected_sd_alpha_gfp*mean_doubling_time*log(2)/3600),ymin=log(corrected_alpha_gfp*mean_doubling_time*log(2)/3600-corrected_sd_alpha_gfp*mean_doubling_time*log(2)/3600)))+
  #################################################
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume*mean_doubling_time*log(2)/3600),col="red"))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume*mean_doubling_time*log(2)/3600),col="red"))+
  geom_errorbar(aes(log(mean_doubling_time),ymax=log(mean_concentration_volume*mean_doubling_time*log(2)/3600+sd_concentration_volume*mean_doubling_time*log(2)/3600),ymin=log(mean_concentration_volume*mean_doubling_time*log(2)/3600-sd_concentration_volume*mean_doubling_time*log(2)/3600)))+
  facet_wrap(~promoter,scale="free")+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Production), bulk")+
  #coord_cartesian(ylim=c(2,12))+
  labs(subtitle="Plasmid strains")

myconcentrations %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume*mean_doubling_time*log(2)/3600),col=promoter))+
  geom_errorbar(aes(log(mean_doubling_time),ymax=log(mean_concentration_volume*mean_doubling_time*log(2)/3600+sd_concentration_volume*mean_doubling_time*log(2)/3600),ymin=log(mean_concentration_volume*mean_doubling_time*log(2)/3600-sd_concentration_volume*mean_doubling_time*log(2)/3600)))+
  #geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col=promoter))+
  #scale_fill_manual(values = mycolors) +
  facet_wrap(~promoter,scale="free")+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Production), mother machine")
  #coord_cartesian(ylim=c(2,12))
```

```{r}
myconcentrations %>% 
  arrange(condition) %>% 
  ungroup() %>% 
  left_join(gr_df,by=c("promoter","condition")) %>% 
  left_join(mydata_wells,by=c("promoter","condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>%
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>%
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_doubling_time),log(corrected_alpha_gfp),col="blue"))+
  geom_line(aes(log(mean_doubling_time),log(corrected_alpha_gfp),col="blue"))+
  geom_errorbar(aes(x=log(mean_doubling_time),ymax=log(corrected_alpha_gfp+corrected_sd_alpha_gfp),ymin=log(corrected_alpha_gfp-corrected_sd_alpha_gfp)))+
  ################################
  geom_point(aes(log(mean_doubling_time),log(mean_concentration_volume),col="red"))+
  geom_line(aes(log(mean_doubling_time),log(mean_concentration_volume),col="red"))+
  geom_errorbar(aes(log(mean_doubling_time),ymax=log(mean_concentration_volume+sd_concentration_volume),ymin=log(mean_concentration_volume-sd_concentration_volume)))+
  facet_wrap(~promoter,scale="free")+
  scale_color_manual(values = mycolors) +
  theme_cowplot()+
  xlab("log(Doublings per hour)")+
  ylab("log(Corrected alpha (GFP)), bulk")+
  #coord_cartesian(ylim=c(2,12))+
  labs(subtitle="Plasmid strains")
```
Ok, so that's pretty clear that it works...

```{r}
scaling_factor <- scaling_factor %>% 
  mutate(ratio=scaling_factor_plasmid/scaling_factor_chromosomal)
scaling_factor
```

So to me, all of this looks extremely casher.
And somehow, the plasmid copy number is pretty stable accross conditions. It seems that the ratio chromosomal/plasmid is kept relatively constant. I am actually amazed that it works so well.

Now can I also correct the others? And get back to production this way?

```{r}
gr_df_cond <- gr_df %>% 
  group_by(condition) %>% 
  mutate(mean_mean_alpha=mean(mean_alpha,na.rm=TRUE)) %>% 
  mutate(mean_mean_doubling_time=mean(mean_doubling_time,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,.keep_all = TRUE) %>% 
  select(condition,mean_mean_alpha,mean_mean_doubling_time)

mydata_inferred_all_control %>%
  filter(grepl("p2-|p3-|pl-",strain)) %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp),col=condition),size=3)+
  geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp-corrected_sd_alpha_gfp),ymax=log(corrected_alpha_gfp+corrected_sd_alpha_gfp)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Concentration (#GFP/um3)")+
  facet_wrap(~strain,scale="free")+
  theme(strip.text = element_text(size = 20))+
    ggsave("./all_concentration_free.pdf",width=12*5,height=7*5,limitsize = FALSE)
```

```{r message=FALSE, warning=FALSE}
gr_df_cond <- gr_df %>% 
  group_by(condition) %>% 
  mutate(mean_mean_alpha=mean(mean_alpha,na.rm=TRUE)) %>% 
  mutate(mean_mean_doubling_time=mean(mean_doubling_time,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,.keep_all = TRUE) %>% 
  select(condition,mean_mean_alpha,mean_mean_doubling_time)

mydata_inferred_all_control %>%
  filter(grepl("p2-|p3-|pl-",strain)) %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp*mean_mean_alpha),col=condition),size=3)+
  geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production (#GFP/um3/s)")+
  facet_wrap(~strain,scale="free")+
  theme(strip.text = element_text(size = 20))+
    ggsave("./all_production_free.pdf",width=12*5,height=7*5,limitsize = FALSE)
```

- I could define some kind of robustness?
- All promoters test here are characterized by the same trend:
- From acetate to glucose, keeps going up! But from glucose to glucoseaa, things become different...
- Is there some kind of invariance that I can characterize?


```{r message=FALSE, warning=FALSE}
gr_df_cond <- gr_df %>% 
  group_by(condition) %>% 
  mutate(mean_mean_alpha=mean(mean_alpha,na.rm=TRUE)) %>% 
  mutate(mean_mean_doubling_time=mean(mean_doubling_time,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,.keep_all = TRUE) %>% 
  select(condition,mean_mean_alpha,mean_mean_doubling_time)

hi_or_med_p2 <- tibble(pattern_pl="p2-",strength=rep(c("med","hi"),each=3),column=c(7,8,9,10,11,12))
hi_or_med_p3 <- tibble(pattern_pl="p3-",strength=rep(rep(c("med","hi"),each=3),times=2),column=c(1,2,3,4,5,6,7,8,9,10,11,12))
hi_or_med <- rbind(hi_or_med_p2,hi_or_med_p3)

mydata_inferred_all_control %>%
  filter(grepl("p2-|p3-",strain)) %>% 
  mutate(pattern_pl=ifelse(grepl("p2-",strain),"p2-","p3-")) %>% 
  left_join(hi_or_med_p2,by=c("column","pattern_pl")) %>%
  filter(strength=="hi") %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp*mean_mean_alpha),col=condition),size=3)+
  geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production (#GFP/um3/s)")

mydata_inferred_all_control %>%
  filter(grepl("p2-|p3-",strain)) %>% 
  mutate(pattern_pl=ifelse(grepl("p2-",strain),"p2-","p3-")) %>% 
  left_join(hi_or_med_p2,by=c("column","pattern_pl")) %>%
  filter(is.na(strength)==FALSE) %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_boxplot(aes(x=log(mean_mean_doubling_time),y=log(corrected_alpha_gfp*mean_mean_alpha),group=interaction(strength,condition),col=condition),width=10)+
  #geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp*mean_mean_alpha),col=condition),size=3)+
  #geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production (#GFP/um3/s)")
```
I could for instance, normalize everything by rrnB... or normalize everything by level in acetate.

```{r message=FALSE, warning=FALSE}
gr_df_cond <- gr_df %>% 
  group_by(condition) %>% 
  mutate(mean_mean_alpha=mean(mean_alpha,na.rm=TRUE)) %>% 
  mutate(mean_mean_doubling_time=mean(mean_doubling_time,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,.keep_all = TRUE) %>% 
  select(condition,mean_mean_alpha,mean_mean_doubling_time)

conditionX <- "glucoseaa"

mydata_inferred_all_control %>%
  filter(grepl("p2-|p3-|pl-",strain)) %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  group_by(strain,condition) %>% 
  mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  ungroup() %>% 
  group_by(strain) %>% 
  mutate(x=ifelse(condition==conditionX,alpha_gfp,NA)) %>% 
  fill(x,.direction = "downup") %>% 
  ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_sd_alpha_gfp_tot/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp*mean_mean_alpha/x),col=condition),size=3)+
  #geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production (#GFP/um3/s)")
```
I can define robustness, which is in essence, how production increases, together with the growth rate between two conditions.
I define it as: delta Q / delta alpha.
And I can plot again the three different robustness scores.

```{r message=FALSE, warning=FALSE}
gr_df_cond <- gr_df %>% 
  group_by(condition) %>% 
  mutate(mean_mean_alpha=mean(mean_alpha,na.rm=TRUE)) %>% 
  mutate(mean_mean_doubling_time=mean(mean_doubling_time,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,.keep_all = TRUE) %>% 
  select(condition,mean_mean_alpha,mean_mean_doubling_time)


mydata_inferred_all_control %>%
  filter(grepl("p2-|p3-|pl-",strain)) %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(strain,condition,.keep_all = TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  group_by(strain) %>% 
  arrange(mean_mean_alpha) %>% 
  mutate(d_mean_mean_alpha=mean_mean_alpha-lag(mean_mean_alpha)) %>%
  mutate(q=corrected_alpha_gfp*mean_mean_alpha) %>% 
  mutate(d_q=q-lag(q)) %>% 
  mutate(d_q_d_gr=d_q/d_mean_mean_alpha) %>% 
  ungroup() %>% 
  ggplot()+
  geom_point(aes(log(mean_mean_doubling_time),d_q_d_gr,col=condition),size=3)+
  #geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production robustness")

mydata_inferred_all_control %>%
  filter(grepl("p2-|p3-|pl-",strain)) %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  group_by(strain,condition) %>% 
  mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  ungroup() %>% 
  distinct(strain,condition,.keep_all = TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_sd_alpha_gfp_tot/scaling_factor_plasmid) %>% 
  group_by(strain) %>% 
  arrange(mean_mean_alpha) %>% 
  mutate(d_mean_mean_alpha=mean_mean_alpha-lag(mean_mean_alpha)) %>%
  mutate(d_mean_mean_alpha_x=lag(mean_mean_alpha)+d_mean_mean_alpha/2) %>% 
  mutate(q=corrected_alpha_gfp*mean_mean_alpha) %>% 
  mutate(d_q=q-lag(q)) %>% 
  mutate(d_q_d_gr=d_q/d_mean_mean_alpha) %>% 
  mutate(condition=sprintf("%s to %s",lag(condition),condition)) %>% 
  ungroup() %>% 
  filter(condition %in% list("acetate to glycerol","glycerol to glucose", "glucose to glucoseaa")) %>% 
  ggplot()+
  geom_boxplot(aes(d_mean_mean_alpha_x*3600/log(2),d_q_d_gr,col=condition),size=1)+
  geom_hline(aes(yintercept=0))+
  #geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production robustness")
```

In other words, MOST of the promoters are characterized by decreasing production, from glucose to glucose aa.
Who are the winners that are very robust?
What is making them different from the others?

# How to proceed further?

- Normalize by a given condition: no invariance

```{r message=FALSE, warning=FALSE}
gr_df_cond <- gr_df %>% 
  group_by(condition) %>% 
  mutate(mean_mean_alpha=mean(mean_alpha,na.rm=TRUE)) %>% 
  mutate(mean_mean_doubling_time=mean(mean_doubling_time,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,.keep_all = TRUE) %>% 
  select(condition,mean_mean_alpha,mean_mean_doubling_time)

hi_or_med_p2 <- tibble(pattern_pl="p2-",strength=rep(c("med","hi"),each=3),column=c(7,8,9,10,11,12))
hi_or_med_p3 <- tibble(pattern_pl="p3-",strength=rep(rep(c("med","hi"),each=3),times=2),column=c(1,2,3,4,5,6,7,8,9,10,11,12))
hi_or_med <- rbind(hi_or_med_p2,hi_or_med_p3)

mydata_inferred_all_control %>%
  filter(grepl("p2-|p3-",strain)) %>% 
  mutate(pattern_pl=ifelse(grepl("p2-",strain),"p2-","p3-")) %>% 
  left_join(hi_or_med_p2,by=c("column","pattern_pl")) %>%
  filter(strength=="hi") %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp*mean_mean_alpha),col=condition),size=3)+
  geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production (#GFP/um3/s)")

mydata_inferred_all_control %>%
  filter(rowcol!="C11") %>% 
  filter(grepl("p2-|p3-",strain)) %>% 
  mutate(pattern_pl=ifelse(grepl("p2-",strain),"p2-","p3-")) %>% 
  left_join(hi_or_med_p2,by=c("column","pattern_pl")) %>%
  filter(is.na(strength)==FALSE) %>% 
  filter(strength=="hi") %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  filter(corrected_alpha_gfp) %>% 
  ggplot()+
  geom_boxplot(aes(x=log(mean_mean_doubling_time),y=log(corrected_alpha_gfp*mean_mean_alpha),group=interaction(strength,condition),col=condition),width=10)+
  #geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp*mean_mean_alpha),col=condition),size=3)+
  #geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production (#GFP/um3/s)")
```

```{r}
mydata_inferred_all_control %>%
  filter(rowcol!="C11") %>% 
  filter(grepl("p2-|p3-",strain)) %>% 
  mutate(pattern_pl=ifelse(grepl("p2-",strain),"p2-","p3-")) %>% 
  left_join(hi_or_med_p2,by=c("column","pattern_pl")) %>%
  filter(is.na(strength)==FALSE) %>% 
  filter(strength=="hi") %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_boxplot(aes(x=log(mean_mean_doubling_time),y=log(corrected_alpha_gfp*mean_mean_alpha),group=interaction(strength,condition),col=condition),width=10)+
  #geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp*mean_mean_alpha),col=condition),size=3)+
  #geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production (#GFP/um3/s)")

mydata_inferred_all_control %>%
  filter(rowcol!="C11") %>% 
  filter(grepl("p2-|p3-",strain)) %>% 
  mutate(pattern_pl=ifelse(grepl("p2-",strain),"p2-","p3-")) %>% 
  left_join(hi_or_med_p2,by=c("column","pattern_pl")) %>%
  filter(is.na(strength)==FALSE) %>% 
  filter(strength=="med") %>% 
  left_join(gr_df_cond,by=c("condition")) %>% 
  left_join(scaling_factor,by=c("condition")) %>% 
  #group_by(strain,condition) %>% 
  #mutate(alpha_gfp=mean(alpha_gfp,na.rm=TRUE)) %>% 
  #mutate(sd_sd_alpha_gfp_tot=sqrt(sum(sd_alpha_gfp**2))) %>%
  #ungroup() %>% 
  distinct(condition,strain,.keep_all=TRUE) %>% 
  mutate(corrected_alpha_gfp=alpha_gfp/scaling_factor_plasmid) %>% 
  mutate(corrected_sd_alpha_gfp=sd_alpha_gfp/scaling_factor_plasmid) %>% 
  ggplot()+
  geom_boxplot(aes(x=log(mean_mean_doubling_time),y=log(corrected_alpha_gfp*mean_mean_alpha),group=interaction(strength,condition),col=condition),width=10)+
  #geom_point(aes(log(mean_mean_doubling_time),log(corrected_alpha_gfp*mean_mean_alpha),col=condition),size=3)+
  #geom_errorbar(aes(x=log(mean_mean_doubling_time),ymin=log(corrected_alpha_gfp*mean_mean_alpha-corrected_sd_alpha_gfp*mean_mean_alpha),ymax=log(corrected_alpha_gfp*mean_mean_alpha+corrected_sd_alpha_gfp*mean_mean_alpha)))+
  theme_cowplot()+
  xlab("Doublings per hour")+
  ylab("Production (#GFP/um3/s)")
```

