---
title: "Comparing_models.Rmd"
author: "Dany Chauvin"
date: "6/4/2021"
output: html_document
---

# IMPORTING DATA

```{r message=FALSE,warning=FALSE}
#Load the first data set
source("./loadFunctionsAndPackages.R")
path_to_MM_data_summary <- "./dataLists/hi1_only.csv"

source("./readMMData_20220113.R")
source("./transformMMData.R")

myframes_to_mycells <- myframes_to_mycells %>% 
   mutate(strain='MG1655')
```

# COMPARISON OF TRACES FOR GLUCOSE FOR A FEW TRACES

Test in glucose, where the tilting can be ignored.

```{r}
selected_cells <- myframes_to_mycells %>%
  filter(condition=="glucose") %>% 
  ungroup() %>% 
  distinct(cell) %>% 
  sample_n(10)

dl <- 0.065

myframes_to_mycells %>% 
  semi_join(selected_cells,by=c("cell")) %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(true_frame=frame+1) %>% 
  ggplot()+
  geom_point(aes(true_frame,oriented_bbox_length_um),col="red",alpha=0.5)+
  geom_point(aes(true_frame,bbox_length_um),col="blue",alpha=0.5)+
  geom_point(aes(true_frame,length_um),col="orange",alpha=0.5)+
  facet_wrap(~cell,scale="free")

myframes_to_mycells %>% 
  semi_join(selected_cells,by=c("cell")) %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(bbox_rad=(90/360*2*pi)-oriented_bbox_orientation_angle_rad) %>% 
  mutate(true_frame=frame+1) %>% 
  ggplot()+
  geom_point(aes(true_frame,bbox_rad),col="red",alpha=0.5)+
  #geom_point(aes(true_frame,bbox_length_um),col="blue",alpha=0.5)+
  geom_point(aes(true_frame,tilt_radian),col="orange",alpha=0.5)+
  facet_wrap(~cell,scale="free")
```

# COMPARISON FOR GLYCEROL DATA FOR A FEW TRACES

```{r}
selected_cells <- myframes_to_mycells %>%
  filter(condition=="glycerol") %>% 
  ungroup() %>% 
  distinct(cell) %>% 
  sample_n(10)

dl <- 0.065

myframes_to_mycells %>% 
  semi_join(selected_cells,by=c("cell")) %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(true_frame=frame+1) %>% 
  ggplot()+
  geom_point(aes(true_frame,oriented_bbox_length_um),col="red",alpha=0.5)+
  geom_point(aes(true_frame,bbox_length_um),col="blue",alpha=0.5)+
  geom_point(aes(true_frame,length_um),col="orange",alpha=0.5)+
  facet_wrap(~cell,scale="free")

myframes_to_mycells %>% 
  semi_join(selected_cells,by=c("cell")) %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(bbox_rad=(90/360*2*pi)-oriented_bbox_orientation_angle_rad) %>% 
  mutate(true_frame=frame+1) %>% 
  ggplot()+
  geom_point(aes(true_frame,bbox_rad),col="red",alpha=0.5)+
  #geom_point(aes(true_frame,bbox_length_um),col="blue",alpha=0.5)+
  geom_point(aes(true_frame,tilt_radian),col="orange",alpha=0.5)+
  facet_wrap(~cell,scale="free")
```

# COMPARISON FOR GLYCEROL DATA FOR A FEW TRACES

```{r}
selected_cells <- myframes_to_mycells %>%
  filter(condition=="acetate") %>% 
  ungroup() %>% 
  distinct(cell) %>% 
  sample_n(10)

dl <- 0.065

myframes_to_mycells %>% 
  semi_join(selected_cells,by=c("cell")) %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(true_frame=frame+1) %>% 
  ggplot()+
  geom_point(aes(true_frame,oriented_bbox_length_um),col="red",alpha=0.5)+
  geom_point(aes(true_frame,bbox_length_um),col="blue",alpha=0.5)+
  geom_point(aes(true_frame,length_um),col="orange",alpha=0.5)+
  facet_wrap(~cell,scale="free")

myframes_to_mycells %>% 
  semi_join(selected_cells,by=c("cell")) %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(bbox_rad=(90/360*2*pi)-oriented_bbox_orientation_angle_rad) %>% 
  mutate(true_frame=frame+1) %>% 
  ggplot()+
  geom_point(aes(true_frame,bbox_rad),col="red",alpha=0.5)+
  #geom_point(aes(true_frame,bbox_length_um),col="blue",alpha=0.5)+
  geom_point(aes(true_frame,tilt_radian),col="orange",alpha=0.5)+
  facet_wrap(~cell,scale="free")
```

# COMPARISON FOR ALL TRACES IN THIS DATA SET

```{r}
selected_cells <- myframes_to_mycells %>%
  #filter(condition=="glucose") %>% 
  ungroup() %>% 
  distinct(cell)
  #sample_n(10)

dl <- 0.065

myframes_to_mycells %>% 
  semi_join(selected_cells,by=c("cell")) %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(true_frame=frame+1) %>% 
  ggplot()+
  #geom_point(aes(length_um,oriented_bbox_length_um),col="black",alpha=0.5)+
  geom_point(aes(bbox_length_um,oriented_bbox_length_um),col="red",alpha=0.1)+
  geom_abline(aes(slope=1,intercept=0))+
  #geom_point(aes(true_frame,length_um),col="orange",alpha=0.5)+
  facet_wrap(~condition,scale="free")

myframes_to_mycells %>% 
  semi_join(selected_cells,by=c("cell")) %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(bbox_rad=(90/360*2*pi)-oriented_bbox_orientation_angle_rad) %>% 
  mutate(true_frame=frame+1) %>% 
  ggplot()+
  geom_point(aes(tilt_radian,bbox_rad),col="black",alpha=0.5)+
  #geom_point(aes(true_frame,bbox_length_um),col="blue",alpha=0.5)+
  #geom_point(aes(true_frame,tilt_radian),col="orange",alpha=0.5)+
  facet_wrap(~condition,scale="free")
```

# LOOKING MORE CLOSELY AT TILT DISTRIBUTION

```{r}
myframes_to_mycells <- myframes_to_mycells %>% 
  mutate(oriented_bbox_width_um=oriented_bbox_width_px*dl,
         oriented_bbox_length_um=oriented_bbox_length_px*dl) %>% 
  mutate(bbox_length_px=(vertical_bottom-vertical_top),
         bbox_length_um=bbox_length_px*dl) %>% 
  mutate(bbox_rad=(90/360*2*pi)-oriented_bbox_orientation_angle_rad) %>% 
  mutate(true_frame=frame+1)
```

```{r}
# getting the vector of interest.
df <- myframes_to_mycells %>% 
  filter(condition=="glucose") %>% .$bbox_rad

summary(df)

breakVec <-  seq(-3e-1,3e-1,by=1e-2)
dev.new(width=4, height=4)
h <- hist(df, breaks = breakVec, density = 10,freq=TRUE,prob=FALSE,ylab="Counts",main="",xaxp=c(-3e-1,3e-1,10))
h$counts = log10(h$counts)
plot(h,ylim=c(0,4),ylab='log10(Counts)',main="",xlab="bbox_tilt_rad")
title("Glucose")
```

```{r}
# getting the vector of interest.
df <- myframes_to_mycells %>% 
  filter(condition=="glucose") %>% .$tilt_radian

summary(df)

breakVec <-  seq(-3e-1,3e-1,by=1e-2)
dev.new(width=4, height=4)
h <- hist(df, breaks = breakVec, density = 10,freq=TRUE,prob=FALSE,ylab="Counts",main="",xaxp=c(-3e-1,3e-1,10))
h$counts = log10(h$counts)
plot(h,ylim=c(0,4),ylab='log10(Counts)',main="",xlab="ellipse_tilt_rad")
title("Glucose")
```

```{r}
# getting the vector of interest.
df <- myframes_to_mycells %>% 
  filter(condition=="glycerol") %>% .$bbox_rad

summary(df)

breakVec <-  seq(-3e-1,3e-1,by=1e-2)
dev.new(width=4, height=4)
h <- hist(df, breaks = breakVec, density = 10,freq=TRUE,prob=FALSE,ylab="Counts",main="",xaxp=c(-3e-1,3e-1,10))
h$counts = log10(h$counts)
plot(h,ylim=c(0,4),ylab='log10(Counts)',main="",xlab="bbox_tilt_rad")
title("Glycerol")
```

```{r}
# getting the vector of interest.
df <- myframes_to_mycells %>% 
  filter(condition=="glycerol") %>% .$tilt_radian

summary(df)

breakVec <-  seq(-3e-1,3e-1,by=1e-2)
dev.new(width=4, height=4)
h <- hist(df, breaks = breakVec, density = 10,freq=TRUE,prob=FALSE,ylab="Counts",main="",xaxp=c(-3e-1,3e-1,10))
h$counts = log10(h$counts)
plot(h,ylim=c(0,4),ylab='log10(Counts)',main="",xlab="ellipse_tilt_rad")
title("Glycerol")
```

So for a reason that I do not understand... assymetrical.
I would need to do it in acetate now.

```{r}
# getting the vector of interest.
df <- myframes_to_mycells %>% 
  filter(condition=="acetate") %>% .$bbox_rad

summary(df)

breakVec <-  seq(-4e-1,4e-1,by=1e-2)
dev.new(width=4, height=4)
h <- hist(df, breaks = breakVec, density = 10,freq=TRUE,prob=FALSE,ylab="Counts",main="",xaxp=c(-4e-1,4e-1,10))
h$counts = log10(h$counts)
plot(h,ylim=c(0,4),ylab='log10(Counts)',main="",xlab="bbox_tilt_rad")
title("Acetate")
```

```{r}
# getting the vector of interest.
df <- myframes_to_mycells %>% 
  filter(condition=="acetate") %>% .$tilt_radian

summary(df)

breakVec <-  seq(-4e-1,4e-1,by=1e-2)
dev.new(width=4, height=4)
h <- hist(df, breaks = breakVec, density = 10,freq=TRUE,prob=FALSE,ylab="Counts",main="",xaxp=c(-4e-1,4e-1,10))
h$counts = log10(h$counts)
plot(h,ylim=c(0,4),ylab='log10(Counts)',main="",xlab="ellipse_tilt_rad")
title("Acetate")
```

Now, I need to look at the overlays.

# COMPARISON CELL BY CELL

First, I have to find a way to establish the correspondence between the cells in the three data sets. Which is something I had done in the past.

```{r}
#First cells that are the closest to each other between old and augmented

augmented_cells <- myframes_to_mycells_model2 %>% 
  group_by(cell) %>% 
  mutate(first_frame=first(frame)) %>% 
  ungroup() %>% 
  distinct(cell,gl,first_frame,mean_position_um)

old_cells <- myframes_to_mycells_model1 %>% 
  group_by(cell) %>% 
  mutate(first_frame=first(frame)) %>% 
  ungroup() %>% 
  distinct(cell,gl,first_frame,mean_position_um)


find_closest <- function(df1,df2){
  
    closest <- df1 %>%
      group_by(cell) %>% 
      do((function(.df){
        mean_pos_1 <- .df$mean_position_um[[1]]
        first_frame_1 <- .df$first_frame[[1]]
        cell_1 <- .df$cell[[1]]
        gl_1 <- .df$gl[[1]]
        lc <- df2  %>% 
          filter(gl==gl_1) %>% 
          mutate(cell_1=cell_1) %>% 
          mutate(delta_pos=abs(mean_pos_1-mean_position_um),
                 delta_frame=abs(first_frame_1-first_frame),
                 total_dif=(delta_pos+1)*(delta_frame+1)) %>% 
          arrange(total_dif) %>%
          filter(row_number()==1) %>% 
          select(cell_1,cell,delta_pos,delta_frame,total_dif)
        return(lc)
      })(.)) %>% 
      ungroup()
    return(closest)
    }
  
closest_old_augmented <- find_closest(old_cells,augmented_cells)

```

```{r}
# Getting rid of ambiguities
closest_old_augmented <- closest_old_augmented %>% 
  group_by(cell) %>% 
  filter(n()<2) %>% 
  ungroup()
```

# NOW COMPARING RESULTS

```{r}
for(c1 in closest_old_augmented$cell_1[1:10]){
  c2 <- unique(closest_old_augmented %>% 
                 filter(cell_1==c1) %>% 
                 .$cell)
  
    print(myframes_to_mycells_model1 %>% 
    filter(cell==c1) %>% 
      ggplot()+
      geom_point(aes(time_sec,volume_um),col="black")+
      geom_point(data=myframes_to_mycells_model2 %>% 
                   filter(cell==c2),aes(time_sec,volume_um),col="green"))
}

```
