---
title: "Concentration and production of synthetic promoters in 96 well plates experiments"
author: "Dany Chauvin"
date: "4/1/2021"
output: html_document
---

# Importing bulk data

Importing data into bulk_data tibble.

```{r message=FALSE,warning=FALSE}
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/bulk_experiments_toolbox/loadFunctionsAndPackages.R")
path_to_bulk_data_summary <- "/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/bulk_experiments_toolbox/dataList.csv"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/bulk_experiments_toolbox/readBulkData.R")
path_to_manual_curation <- "/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/bulk_experiments_toolbox/manualCuration.csv"
source("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/bulk_experiments_toolbox/transformBulkData.R")
```

The following routines will import:
- mydata_curated: raw data, curated to keep only well behaving wells (not showing obvious growth defects, or fluorescence measurement obvious errors).
- bulk_data: data where the apparent concentration (alpha_gfp) and growth-rate (well_gr in doublings/hours) were computed.

# Saving data summary for further analysis

```{r}
readr::write_csv(bulk_data,"/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/fitted_bulk_data/bulk_data.csv")
```
