---
title: "sanity_checks"
author: "Dany Chauvin"
date: '2022-10-05'
output: html_document
---

Some code to "post deep moma" check agreement between deep moma curation and imported data.

## Number of full cell cycles per growth lane, per cell rank

```{r}
myframes_complete %>% 
  #filter(condition=="glucoseaa") %>%
  distinct(promoter,condition,date,pos,gl_number,cell,mean_cell_rank) %>% 
  group_by(condition,promoter,date,pos,gl_number,mean_cell_rank) %>% 
  arrange(pos) %>% 
  #filter(mean_cell_rank>=2) %>% 
  count()
```

## Number of cell cycles per growth lanes

```{r}
myframes_complete %>% 
  #filter(condition=="glucoseaa") %>%
  distinct(promoter,condition,date,pos,gl_number,cell,mean_cell_rank) %>% 
  group_by(condition,promoter,date,pos,gl_number) %>% 
  arrange(pos) %>% 
  #filter(mean_cell_rank>=2) %>% 
  count()
```


# Number of cells per condition, per mean cell rank

```{r}
myframes_complete %>% 
  #filter(condition=="glucoseaa") %>%
  distinct(promoter,condition,date,pos,gl_number,cell,mean_cell_rank) %>% 
  group_by(condition,promoter,mean_cell_rank) %>% 
  arrange(pos) %>% 
  #filter(mean_cell_rank>=2) %>% 
  count()
```

Example: Glucoseaa, Pos0, GL8, 2 cells with mean_cell_rank 2, ok, 1 cell with mean_cell_rank 4, problematic
```{r}
myframes_complete %>% 
  filter(condition=="glucoseaa") %>%
  group_by(cell) %>% 
  mutate(mean_cell_rank=round(mean(cell_rank,na.rm=TRUE),0)) %>% 
  ungroup() %>% 
  #distinct(promoter,condition,date,pos,gl_number,cell,mean_cell_rank,.keep_all=TRUE) %>% 
  filter(gl_number==8,pos==0,mean_cell_rank %in% c(2,4)) %>% 
  select(cell,cell_rank,frame,mean_cell_rank,vertical_top,length_um) %>% 
  group_by(cell) %>% 
  arrange(frame) %>% 
  mutate(dl=last(length_um)-first(length_um)) %>% 
  ungroup() %>% 
  mutate(true_frame=frame+1)
```

Example: Glucoseaa, Pos0, GL28: everything alright
```{r}
myframes_complete %>% 
  filter(condition=="glucoseaa") %>%
  group_by(cell) %>% 
  mutate(mean_cell_rank=round(mean(cell_rank,na.rm=TRUE),0)) %>% 
  ungroup() %>% 
  #distinct(promoter,condition,date,pos,gl_number,cell,mean_cell_rank,.keep_all=TRUE) %>% 
  filter(gl_number==28,pos==0,mean_cell_rank %in% c(2,3,4)) %>% 
  select(cell,cell_rank,frame,mean_cell_rank,vertical_top,length_um) %>% 
  group_by(cell) %>% 
  arrange(frame) %>% 
  mutate(dl=last(length_um)-first(length_um)) %>% 
  ungroup() %>% 
  mutate(true_frame=frame+1) %>% 
  arrange(cell,frame)
```

Example: Glucoseaa, Pos0, GL40: everything alright
```{r}
myframes_complete %>% 
  filter(condition=="glucoseaa") %>%
  group_by(cell) %>% 
  mutate(mean_cell_rank=round(mean(cell_rank,na.rm=TRUE),0)) %>% 
  ungroup() %>% 
  #distinct(promoter,condition,date,pos,gl_number,cell,mean_cell_rank,.keep_all=TRUE) %>% 
  filter(gl_number==40,pos==0,mean_cell_rank %in% c(2,3,4)) %>% 
  select(cell,cell_rank,frame,mean_cell_rank,vertical_top,length_um) %>% 
  group_by(cell) %>% 
  arrange(frame) %>% 
  mutate(dl=last(length_um)-first(length_um)) %>% 
  ungroup() %>% 
  mutate(true_frame=frame+1) %>% 
  arrange(cell,frame)
```
