---
title: "Import all data"
author: "Dany Chauvin"
date: '2022-12-14'
output: html_document
---

All raw data should be already loaded. For each data set, the following code produces new yaml files, that can be used to re-curate data if necessary.

```{r}
unique(myframes_all$file_path)
columns <- colnames(myframes_all)
columns[str_detect(columns,"path")]
```


Actually what I need to do first, is to look in each one of these files, if I can find "pruned" or not. Then I know which one I have to do again or not. Then if there are some I need to do again, I will go and try to find export log. To collect backups. Then finally redo curation if necessary. And clean data in the mean time.

# Step 1, finding CellStats csv files containing "pruned"

## Only a very few are found with "pruned"

/scicore/home/nimwegen/rocasu25/MM_Data/Dany/20220824/curated_data/20220824_ch_hi1_curated/20220824_ace_1_MMStack_Pos4_GL57_curated/ExportedCellStats__20220824_ace_1_MMStack_Pos4_GL57.tif.csv
/scicore/home/nimwegen/rocasu25/MM_Data/Dany/20220824/curated_data/20220824_ch_hi1_curated/20220824_ace_1_MMStack_Pos5_GL6_curated/ExportedCellStats__20220824_ace_1_MMStack_Pos5_GL6.tif.csv
/scicore/home/nimwegen/rocasu25/MM_Data/Dany/20220824/curated_data/20220824_ch_hi1_curated/20220824_ace_1_MMStack_Pos4_GL39_curated/ExportedCellStats__20220824_ace_1_MMStack_Pos4_GL39.tif.csv

# Step 2, search for export logs

20190515, 
First take a look at when exporting.
## 20221121
No exporting log.
## 20220824

# Step 3: recurating...
## 20190515 hi1
```{r}
myframes_all %>% filter(date=="20190515") %>% filter(promoter=="hi1") %>%  group_by(pos,gl) %>% count()
```
## Generate file list
```{r}
file_list <- unique(myframes_all$file_path)
#write_lines(file_list, "./file_list.txt")
```

## 20190515

For 20190515, some curation had been done BEFORE. File names contain therefore: ExportedCellStats in there filenames.
I should therefore only consider the following.

```{r}
all_20190515 <- file_list[str_detect(file_list,"20190515")]
all_20190515[str_detect(all_20190515,"ExportedCellStats")]
```
Done, right and left should be curated again

## 20221121

Curation was finished at 20221128 11:56:52
Export started at 20221128 12:37:58

```{r}
all_20221121 <- file_list[str_detect(file_list,"20221121")]
all_20221121[str_detect(all_20190515,"CellStats")]

myframes_all %>%
  filter(condition=="acetate005") %>% 
  filter(date=="20221121") %>% 
  group_by(pos,gl) %>% 
  count() %>% View()
  
```

## 20220921

```{r}
all_20220921 <- file_list[str_detect(file_list,"20220921")]
all_20220921[str_detect(all_20220921,"CellStats")]



myframes_all %>%
  #filter(condition=="glucoseaa020") %>% 
  filter(date=="20220921") %>% 
  group_by(pos,gl) %>% 
  count() %>% 
  mutate(pos=as.character(pos),gl=as.character(gl)) %>% 
  mutate(pos=as.integer(pos),gl=as.integer(gl)) %>% 
  arrange(pos,gl) %>% 
  View()
```

## 20220824

- No need to recurate these.

```{r}
all_20220824 <- file_list[str_detect(file_list,"20220824")]
all_20220824[str_detect(all_20220824,"CellStats")]

myframes_all %>%
  #filter(condition=="glucoseaa020") %>% 
  filter(date=="20220824") %>% 
  group_by(pos,gl) %>% 
  count() %>% 
  mutate(pos=as.character(pos),gl=as.character(gl)) %>% 
  mutate(pos=as.integer(pos),gl=as.integer(gl)) %>% 
  arrange(pos,gl) %>% 
  View()
```

# TODO

## For hi1

Rerun for the following:
- 20190515
- 20221121
- 20220921

Necessary recuration, prune, and export.






