---
title: "import_denoised_hi1_data_all_conditions.Rmd"
author: "Dany Chauvin"
date: '2022-12-01'
output: html_document
---

# Set folder where to perform the analysis

Note:
-denoising_20230119195253
Full cell cycles only. Promoter 'Hi1' in acetate 0.05% (20221121), acetate 0.20 % (20220824), glycerol 0.40% (20190515), glucose 0.20% (20190515), glucose 0.20% + amino acids (20220921).
-denoising_20230120151340
All cells (more than 10 data points, which doubles the number of cells I have in my dataset). Promoter 'Hi1' in acetate 0.05% (20221121), acetate 0.20 % (20220824), glycerol 0.40% (20190515), glucose 0.20% (20190515), glucose 0.20% + amino acids (20220921).

```{r message=FALSE,warning=FALSE}
#data_folder <- c("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/raw_curated_data")
data_folder <- c("/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/raw_curated_data_complete_cycles")
#Accompanying raw data (full cell cycle only)

# No bleaching 
#denoised_data_files_dir <- "/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/denoising_raw_data/denoising_20230215111724"

#With bleaching
denoised_data_files_dir <-"/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/denoising_raw_data/denoising_20230215074335"
```

# Import raw data

```{r}
source("../mother_machine_experiments_toolbox/load_functions_and_packages.R")
```

```{r}
list_of_data_files <- lapply(data_folder,function(.l){
  list.files(path=.l,pattern="rawdata.csv$",recursive = TRUE,full.names=TRUE)}) %>% 
  unlist()

df_of_data_files <- tibble(path=list_of_data_files) %>% 
    tidyr::extract(path,"condition","[0-9a-zA-Z]{1,}_([0-9a-zA-Z]{1,})_[0-9]{8}_rawdata.csv$",remove=FALSE,convert=FALSE) %>% 
    tidyr::extract(path,"promoter","([0-9a-z]{1,})_[0-9a-zA-Z]{1,}_[0-9]{8}_rawdata.csv$",remove=FALSE,convert=FALSE) %>% 
    tidyr::extract(path,"date","[0-9a-z]{1,}_[0-9a-zA-Z]{1,}_([0-9]{8})_rawdata.csv$",remove=FALSE,convert=FALSE) %>% 
  rename(raw_curated_data_path=path) %>% 
  tidyr::extract(condition,"carbon_source_concentration","^[a-z]{1,}0([0-9]{2})",remove=FALSE,convert=FALSE) %>% 
  mutate(carbon_source_concentration=as.double(carbon_source_concentration)/100) %>% 
  tidyr::extract(condition,"carbon_source","^([a-z]{1,})0[0-9]{2}",remove=FALSE,convert=FALSE)

myframes_raw <- df_of_data_files %>% 
  ungroup() %>% 
  distinct(raw_curated_data_path) %>% 
  .$raw_curated_data_path %>% 
  lapply(function(.l) readr::read_csv(.l) %>% 
  mutate(raw_curated_data_path=.l)) %>% 
  do.call(rbind, .) %>% 
  mutate(date=as.character(date)) %>% 
  #rename(carbon_source=condition) %>% 
  left_join(df_of_data_files,by=c("condition","promoter","date","raw_curated_data_path"))
```

# Importing denoised data (as well as parameters and errors)

```{r}
find_command <- sprintf("find %s -type f -name '*prediction.csv'",denoised_data_files_dir)
list_of_denoised_data_files <- system(find_command, intern=TRUE)

myframes_denoised <- list_of_denoised_data_files %>% 
  lapply(function(.l) readr::read_csv(.l,skip=13) %>% 
           mutate(denoised_data_path=.l)) %>% 
  do.call(rbind,.) %>% 
  extract(denoised_data_path,"promotercondition","/([a-z0-9A-Z]{1,}_[0-9a-zA-Z]{1,})_[0-9]{8}_rawdata_[a-z0-9]{1,}_b_prediction.csv$",remove=FALSE,convert=FALSE) %>% 
  extract(denoised_data_path,"date","/[a-z0-9A-Z]{1,}_[0-9a-zA-Z]{1,}_([0-9]{8})_rawdata_[a-z0-9]{1,}_b_prediction.csv$",remove=FALSE,convert=FALSE) %>% 
  separate(promotercondition,into=c("promoter","condition"),sep="_") %>% 
  separate(condition,into=c("carbon_source","carbon_source_concentration"),sep="(?<=[A-Za-z])(?=[0-9])",remove=FALSE) %>% 
  mutate(carbon_source_concentration=as.double(carbon_source_concentration)/100)
  
find_command <- sprintf("find %s -type f -name '*final.csv'",denoised_data_files_dir)

myparameters <- system(find_command, intern=TRUE) %>% 
  lapply(function(.l) readr::read_csv(.l,n_max=10) %>% 
           mutate(denoised_data_path=.l)) %>% 
  do.call(rbind,.) %>% 
  extract(denoised_data_path,"promotercondition","/([a-z0-9A-Z]{1,}_[0-9a-zA-Z]{1,})_[0-9]{8}_rawdata_[a-z0-9]{1,}_b_final.csv$",remove=FALSE,convert=FALSE) %>% 
  extract(denoised_data_path,"date","/[a-z0-9A-Z]{1,}_[0-9a-zA-Z]{1,}_([0-9]{8})_rawdata_[a-z0-9]{1,}_b_final.csv$",remove=FALSE,convert=FALSE) %>% 
  separate(promotercondition,into=c("promoter","condition"),sep="_") %>% 
  separate(condition,into=c("carbon_source","carbon_source_concentration"),sep="(?<=[A-Za-z])(?=[0-9])",remove=FALSE) %>% 
  mutate(carbon_source_concentration=as.double(carbon_source_concentration)/100)

myerrors <- system(find_command, intern=TRUE) %>% 
  lapply(function(.l) readr::read_csv(.l,n_max=3,skip=14) %>% 
           mutate(denoised_data_path=.l)) %>% 
  do.call(rbind,.) %>% 
 extract(denoised_data_path,"promotercondition","/([a-z0-9A-Z]{1,}_[0-9a-zA-Z]{1,})_[0-9]{8}_rawdata_[a-z0-9]{1,}_b_final.csv$",remove=FALSE,convert=FALSE) %>% 
  extract(denoised_data_path,"date","/[a-z0-9A-Z]{1,}_[0-9a-zA-Z]{1,}_([0-9]{8})_rawdata_[a-z0-9]{1,}_b_final.csv$",remove=FALSE,convert=FALSE) %>% 
  separate(promotercondition,into=c("promoter","condition"),sep="_") %>% 
  separate(condition,into=c("carbon_source","carbon_source_concentration"),sep="(?<=[A-Za-z])(?=[0-9])",remove=FALSE) %>% 
  mutate(carbon_source_concentration=as.double(carbon_source_concentration)/100)
```

# Analyze inferred parameters

```{r}
dt_df <- tibble(dt=c(12,6,3,1.5),condition=conditions)

myparameters %>% 
  filter(name=="beta") %>% 
  select(name,final,promoter,date,condition) %>% 
  pivot_wider(names_from = name, values_from = final) %>% 
  left_join(dt_df,by=c("condition")) %>% 
  ggplot()+
  geom_point(aes(dt,beta,col=promoter))+
  scale_y_continuous(trans="log10")

myparameters %>% 
  filter(name=="beta") %>% 
  select(name,final,promoter,date,condition) %>% 
  pivot_wider(names_from = name, values_from = final) %>% 
  left_join(dt_df,by=c("condition")) %>% 
  arrange(dt) %>% 
  View()
```


# Concatenate denoised data and raw data

```{r}
myframes_raw <- myframes_raw %>% 
  select(-c(length_um,gfp_nb,carbon_source_concentration,carbon_source,parent)) %>% 
  ungroup()

myframes_denoised <- myframes_denoised %>% 
  ungroup() %>% 
  rename(cell=cell_id,
         parent=parent_id,
         time_min=time,
         gfp_nb=mean_g,
         lambda=mean_l,
         q=mean_q) %>% 
  mutate(time_sec=time_min*60,
         length_um_raw=exp(log_length),
         gfp_nb_raw=fp,
         length_um=exp(mean_x)) %>% 
  select(-c(log_length,fp,mean_x))

myframes_final <- left_join(myframes_raw,myframes_denoised,by=c("condition","promoter","date","cell","time_sec"))
```

# Save the data on the disk for further analysis

```{r}
#Filtering out cells which have bad segmentation issue.

bad_cells <- myframes_final %>% 
  mutate(lambda_high_boundary=lambda+sqrt(cov_ll)) %>% 
  filter(lambda_high_boundary<0) %>% 
  distinct(cell)

myframes_final <- myframes_final %>% 
  anti_join(bad_cells,by=c("cell"))

myframes_final %>% 
  group_by(date,promoter,condition) %>% 
  do((function(.df) {
    #readr::write_csv(.df,sprintf("../denoised_data/%s_%s_denoised.csv",unique(.df$promoter),unique(.df$condition)))
    readr::write_csv(.df,sprintf("../denoised_data_complete_cycles/%s_%s_%s_date_denoised_complete.csv",unique(.df$promoter),unique(.df$condition),unique(.df$date)))
    return(tibble())
  })(.)) %>% 
  ungroup()
```