---
title: "simulations_hi1.Rmd"
author: "Dany Chauvin"
date: '2023-01-24'
output: html_document
---

```{r}
source("../mother_machine_experiments_toolbox/load_functions_and_packages.R")
#data_folder <- "/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/hybrid_simulations_output/hybrid_simulations_20221219_10h"
data_folder <- "/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/denoising_raw_data/denoising_20230131121905/integration"
experimental_data_folder <- "/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/denoised_data_complete_cycles"
#experimental_data_folder <- "/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/denoised_data"
```

# Import simulation data

```{r}
noise_contribution_data <- lapply(data_folder,function(.l){
  list.files(path=.l,pattern=".csv$",recursive = TRUE,full.names=TRUE)}) %>% 
  unlist() %>% 
  lapply(function(.l) readr::read_csv(.l) %>% 
           mutate(path=.l)) %>% 
  do.call(rbind, .) %>% 
  tidyr::extract(path,"promoter","/([0-9a-zA-Z]{1,})_[0-9a-zA-Z]{1,}_[a-z]{1,}.csv$",remove=FALSE,convert=FALSE) %>% 
  tidyr::extract(path,"condition","/[0-9a-zA-Z]{1,}_([0-9a-zA-Z]{1,})_[a-z]{1,}.csv$",remove=FALSE,convert=FALSE) %>%
  tidyr::extract(condition,"carbon_source_concentration","^[a-z]{1,}0([0-9]{2})",remove=FALSE,convert=FALSE) %>% 
  mutate(carbon_source_concentration=as.double(carbon_source_concentration)/100) %>% 
  tidyr::extract(condition,"carbon_source","^([a-z]{1,})0[0-9]{2}",remove=FALSE,convert=FALSE) %>% 
  tidyr::extract(path,"datatype","/[0-9a-z]{1,}_[0-9a-zA-Z]{1,}_([a-z]{1,}).csv$",remove=FALSE,convert=FALSE) %>% 
  rename(cell=cell_id,parent=parent_id,gfp_nb=gfp,lambda=lt,q=qt) %>% 
  mutate(time_sec=time_min*60,
  length_um=exp(log_length)) %>%
  select(-c("...1"))

experimental_data <- lapply(experimental_data_folder,function(.l){
  list.files(path=.l,pattern="denoised[_complete]*.csv$",recursive = TRUE,full.names=TRUE)}) %>% 
  unlist() %>% 
  lapply(function(.l) readr::read_csv(.l) %>% 
           mutate(path=.l)) %>% 
  do.call(rbind, .) %>% 
  mutate(datatype="experimentaldata") %>% 
  mutate(time_sec=time_min*60) %>% 
  mutate(log_length=log(length_um)) %>% 
  select(c("cell","time_min","parent","log_length","gfp_nb","lambda","q","promoter","condition","carbon_source","carbon_source_concentration","time_sec","length_um","datatype","path","mean_cell_rank","gl_id"))

mean_cell_rank_df <- experimental_data %>% 
  distinct(cell,mean_cell_rank,gl_id)

nrow(experimental_data %>% filter(condition=="glucose020"))
nrow(noise_contribution_data %>% filter(condition=="glucose020") %>% filter(datatype=="allnoisesources"))
```

```{r}
noise_contribution_data <- rbind(noise_contribution_data %>% 
                                   left_join(mean_cell_rank_df,by=c("cell")),
                                 experimental_data) %>% 
  mutate(concentration=gfp_nb/length_um)

nrow(noise_contribution_data %>% filter(condition=="glucose020") %>% filter(datatype=="experimentaldata"))
nrow(noise_contribution_data %>% filter(condition=="glucose020") %>% filter(datatype=="allnoisesources"))
a <- noise_contribution_data %>% filter(condition=="glucose020") %>% filter(datatype=="experimentaldata")
b <- noise_contribution_data %>% filter(condition=="glucose020") %>% filter(datatype=="allnoisesources")
a[!complete.cases(a),]
b[!complete.cases(b),]
```

# Plot concentration histogram

```{r}
plot_histogram <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  
  exp_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$concentration)
  sim_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$concentration)
  exp <- noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$concentration
  sim <- noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$concentration
  exp_density
  sim_density
  print(exp_density)
  print(sim_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  h_sim <- hist(sim, breaks = breakVec,plot=FALSE)
  if(plot){
  print(
  ggplot()+
    geom_col(aes(x=h_exp$mids,y=h_exp$counts),fill="blue",alpha=0.5)+
    geom_col(aes(x=h_sim$mids,y=h_sim$counts),fill="red",alpha=0.5))+
      scale_y_continuous(trans = "log10")+
      ylab("Counts")+
      xlab("Concentration")}
}

breakVec=seq(8000,80000,200)
plot_histogram("acetate005",breakVec,TRUE)

breakVec=seq(7000,60000,200)
plot_histogram("acetate020",breakVec,TRUE)

breakVec=seq(100,45000,200)
plot_histogram("glycerol040",breakVec,TRUE)

breakVec=seq(4000,43000,200)
plot_histogram("glucose020",breakVec,TRUE)

breakVec=seq(4000,35000,200)
plot_histogram("glucoseaa020",breakVec,TRUE)
```

# Plot length histogram

```{r}
plot_histogram <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  
  exp_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$length_um)
  sim_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$length_um)
  exp <- noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$length_um
  sim <- noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$length_um
  exp_density
  sim_density
  print(exp_density)
  print(sim_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  h_sim <- hist(sim, breaks = breakVec,plot=FALSE)
  if(plot){
  print(
  ggplot()+
    geom_col(aes(x=h_exp$mids,y=h_exp$counts),fill="blue",alpha=0.5)+
    geom_col(aes(x=h_sim$mids,y=h_sim$counts),fill="red",alpha=0.5))+
      scale_y_continuous(trans = "log10")+
      ylab("Counts")+
      xlab("Cell-size")}
}

breakVec=seq(0.8,5,0.05)
plot_histogram("acetate005",breakVec,TRUE)

breakVec=seq(0.8,7,0.05)
plot_histogram("acetate020",breakVec,TRUE)

breakVec=seq(0.8,10,0.05)
plot_histogram("glycerol040",breakVec,TRUE)

breakVec=seq(1,16,0.05)
plot_histogram("glucose020",breakVec,TRUE)

breakVec=seq(1,24,0.05)
plot_histogram("glucoseaa020",breakVec,TRUE)
```

# Plot log-length histogram

```{r}
plot_histogram <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  
  exp_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% mutate(ll=log(length_um)) %>%  .$ll)
  sim_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% mutate(ll=log(length_um)) %>%  .$ll)
  exp <- noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% mutate(ll=log(length_um)) %>% .$ll
  sim <- noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% mutate(ll=log(length_um)) %>% .$ll
  exp_density
  sim_density
  print(exp_density)
  print(sim_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  h_sim <- hist(sim, breaks = breakVec,plot=FALSE)
  if(plot){
  print(
  ggplot()+
    geom_col(aes(x=h_exp$mids,y=h_exp$counts),fill="blue",alpha=0.5)+
    geom_col(aes(x=h_sim$mids,y=h_sim$counts),fill="red",alpha=0.5))+
      scale_y_continuous(trans = "log10")+
      #scale_x_continuous(trans = "log10")+
      ylab("Counts")+
      xlab("log(Cell-size)")}
}

breakVec=seq(0.005,1.6,0.01)
plot_histogram("acetate005",breakVec,TRUE)

breakVec=seq(0.003,2,0.01)
plot_histogram("acetate020",breakVec,TRUE)

breakVec=seq(0.07,2.5,0.05)
plot_histogram("glycerol040",breakVec,TRUE)

breakVec=seq(0.1,3,0.05)
plot_histogram("glucose020",breakVec,TRUE)

breakVec=seq(0.4,3.2,0.05)
plot_histogram("glucoseaa020",breakVec,TRUE)
```

# Plot gfp histogram

```{r}
plot_histogram <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  
  exp_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$gfp_nb)
  sim_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$gfp_nb)
  exp <- noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$gfp_nb
  sim <- noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$gfp_nb
  exp_density
  sim_density
  print(exp_density)
  print(sim_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  h_sim <- hist(sim, breaks = breakVec,plot=FALSE)
  if(plot){
  print(
  ggplot()+
    geom_col(aes(x=h_exp$mids,y=h_exp$counts),fill="blue",alpha=0.5)+
    geom_col(aes(x=h_sim$mids,y=h_sim$counts),fill="red",alpha=0.5))+
      scale_y_continuous(trans = "log10")+
      ylab("Counts")+
      xlab("GFP per cell")}
}

breakVec=seq(10000,300000,2000)
plot_histogram("acetate005",breakVec,TRUE)

breakVec=seq(10000,300000,2000)
plot_histogram("acetate020",breakVec,TRUE)

breakVec=seq(-1300,260000,2000)
plot_histogram("glycerol040",breakVec,TRUE)

breakVec=seq(5000,250000,2000)
plot_histogram("glucose020",breakVec,TRUE)

breakVec=seq(14000,330000,2000)
plot_histogram("glucoseaa020",breakVec,TRUE)
```

# Plot log-gfp histogram

```{r}
plot_histogram <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  
  exp_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% mutate(ll=log(gfp_nb)) %>%  .$ll)
  sim_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% mutate(ll=log(gfp_nb)) %>%  .$ll)
  exp <- noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% mutate(ll=log(gfp_nb)) %>% .$ll
  sim <- noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% mutate(ll=log(gfp_nb)) %>% .$ll
  exp_density
  sim_density
  print(exp_density)
  print(sim_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  h_sim <- hist(sim, breaks = breakVec,plot=FALSE)
  if(plot){
  print(
  ggplot()+
    geom_col(aes(x=h_exp$mids,y=h_exp$counts),fill="blue",alpha=0.5)+
    geom_col(aes(x=h_sim$mids,y=h_sim$counts),fill="red",alpha=0.5))+
      scale_y_continuous(trans = "log10")+
      #scale_x_continuous(trans = "log10")+
      ylab("Counts")+
      xlab("log(#GFP)")}
}

breakVec=seq(9,13,0.05)
plot_histogram("acetate005",breakVec,TRUE)

breakVec=seq(9,13,0.05)
plot_histogram("acetate020",breakVec,TRUE)

breakVec=seq(7,13,0.05)
plot_histogram("glycerol040",breakVec,TRUE)

breakVec=seq(9,13,0.05)
plot_histogram("glucose020",breakVec,TRUE)

breakVec=seq(9,13,0.05)
plot_histogram("glucoseaa020",breakVec,TRUE)
```



```{r}
experimental_data <- lapply(experimental_data_folder,function(.l){
  list.files(path=.l,pattern="denoised[_complete]*.csv$",recursive = TRUE,full.names=TRUE)}) %>% 
  unlist() %>% 
  lapply(function(.l) readr::read_csv(.l) %>% 
           mutate(path=.l)) %>% 
  do.call(rbind, .) %>% 
  mutate(datatype="experimentaldata") %>% 
  mutate(time_sec=time_min*60) %>% 
  mutate(log_length=log(length_um)) %>% 
  select(c("cell","time_min","parent","log_length","gfp_nb","lambda","q","promoter","condition","carbon_source","carbon_source_concentration","time_sec","length_um","datatype","path","mean_cell_rank","length_um_raw"))


selected_cell <- experimental_data %>% 
  #filter(datatype=="experimentaldata") %>% 
  sample_n(1) %>% 
  select(cell)
  
experimental_data %>% 
  #filter(datatype=="experimentaldata") %>% 
  semi_join(selected_cell,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec,length_um_raw))+
  geom_line(aes(time_sec,length_um),col="red")
```
You can also see it, on the stat_ecdf plots.

```{r}
noise_contribution_data %>% 
  filter(datatype %in% c("experimentaldata","allnoisesources")) %>% 
  #filter(condition=="glucose020") %>% 
  mutate(concentration=gfp_nb/length_um) %>% 
  ggplot(aes(concentration))+
  stat_ecdf(aes(col=datatype))+
  facet_wrap(~condition)
```

# Plot single cell traces, glucose only

```{r}
glucose_data <- noise_contribution_data %>% 
  filter(datatype %in% c("experimentaldata","allnoisesources")) %>% 
  filter(condition=="glucose020")

glucose_data %>% 
  select(datatype,cell,time_sec,concentration) %>% 
  pivot_wider(names_from = datatype,values_from = concentration) %>% 
  mutate(delta_c=allnoisesources-experimentaldata) %>% 
  mutate(delta_c=(allnoisesources-experimentaldata)/experimentaldata) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,delta_c),alpha=0.01)+
  ylab("allnoisesources - experimentaldata")+
  xlab("time (h)")
```

This plot should be symmetrical, around 0. But his is not. it does not seem to get worse over the course of the experiment either.
I can plot this distribution using a bar plot.

```{r}
delta_c_data <- glucose_data %>% 
  select(datatype,cell,time_sec,concentration) %>% 
  pivot_wider(names_from = datatype,values_from = concentration) %>% 
  mutate(delta_c=allnoisesources-experimentaldata) %>% 
  #group_by(cell) %>% 
  #sample_n(1) %>% 
  #ungroup() %>% 
  #mutate(delta_c_norm=delta_c/experimentaldata) %>% 
  .$delta_c

density(delta_c_data)

h <- hist(delta_c_data,breaks=seq(-12000,1000,100),plot=FALSE)

ggplot()+
  geom_col(aes(x=h$mids,y=h$counts),fill="blue",alpha=0.5)+
  scale_y_continuous(trans="log10")
```

```{r}
delta_c_data <- glucose_data %>% 
  select(datatype,cell,time_sec,concentration) %>% 
  pivot_wider(names_from = datatype,values_from = concentration) %>% 
  mutate(delta_c=allnoisesources-experimentaldata) %>% 
  #group_by(cell) %>% 
  #sample_n(1) %>% 
  #ungroup() %>% 
  mutate(delta_c=delta_c/experimentaldata) %>% 
  .$delta_c

density(delta_c_data)

h <- hist(delta_c_data,breaks=seq(-0.3,0.13,0.01),plot=FALSE)

ggplot()+
  geom_col(aes(x=h$mids,y=h$counts),fill="blue",alpha=0.5)+
  scale_y_continuous(trans="log10")
```

Can it be that this long tail, is somewhat responsible for the discrepancy we see? It is not just a few outliers...
Because it means that, somehow, the concentration in silico data, can be reduced by up to 25%, where as we never go as high as a 10% increase.

```{r}
glucose_data %>% 
  select(datatype,cell,time_sec,concentration) %>% 
  pivot_wider(names_from = datatype,values_from = concentration) %>% 
  mutate(delta_c=allnoisesources-experimentaldata) %>% 
  #group_by(cell) %>% 
  #sample_n(1) %>% 
  #ungroup() %>% 
  mutate(delta_c=delta_c/experimentaldata) %>% 
  ggplot()+
  geom_point(aes(experimentaldata,delta_c),alpha=0.01)+
  ylab("(c_sim-c_exp)/c_exp")+
  xlab("c_exp")
```

```{r}
glucose_data %>% 
  select(datatype,cell,time_sec,length_um) %>% 
  pivot_wider(names_from = datatype,values_from = length_um) %>% 
  mutate(delta_c=allnoisesources-experimentaldata) %>% 
  #group_by(cell) %>% 
  #sample_n(1) %>% 
  #ungroup() %>% 
  mutate(delta_c=delta_c/experimentaldata) %>% 
  ggplot()+
  geom_point(aes(experimentaldata,allnoisesources),alpha=0.01)+
  geom_abline(slope=1,intercept=0,alpha=1,linetype="dashed")+
  ylab("length um (forward integration)")+
  xlab("length um (inferred data)")+
  xlim(0,10)+
  ylim(0,10)+
  coord_fixed(ratio=1)
```


# Study one lineage

```{r}
#select a relevant lineage
selected_cells_gls <- glucose_data %>% 
  select(datatype,cell,time_sec,concentration,gl_id) %>% 
  pivot_wider(names_from = datatype,values_from = concentration) %>% 
  mutate(delta_c=allnoisesources-experimentaldata) %>% 
  mutate(delta_c=delta_c/experimentaldata) %>% 
  filter(delta_c<(-0.2)) %>% 
  distinct(cell,gl_id)

#Let's investigate, gl 3.6
gl0 <- "20190515.3.6"

glucose_data %>% 
  filter(gl_id==gl0) %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,concentration,col=datatype,group=interaction(cell,datatype)))
```

```{r}
interesting_cells <- selected_cells_gls %>% 
  filter(gl_id==gl0) %>% 
  distinct(cell)

interesting_parents <- glucose_data %>% 
  filter(gl_id==gl0) %>% 
  semi_join(interesting_cells,by=c("cell")) %>%
  distinct(parent) %>% 
  rename(cell=parent)

glucose_data %>% 
  filter(cell=="20190515.3.6.74") %>% 
  #semi_join(interesting_parents,by=c("cell")) %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,concentration,col=datatype,group=interaction(cell,datatype)))+
  ylim(0,30000)

glucose_data %>% 
  filter(cell=="20190515.3.6.74") %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,length_um,col=datatype,group=interaction(cell,datatype)))#+
  #ylim(0,3)

glucose_data %>% 
  filter(cell=="20190515.3.6.74") %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,gfp_nb,col=datatype,group=interaction(cell,datatype)))+
  ylim(0,250000)

glucose_data %>% 
  filter(cell=="20190515.3.6.74") %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,lambda,col=datatype,group=interaction(cell,datatype)))

glucose_data %>% 
  filter(cell=="20190515.3.6.74") %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,q,col=datatype,group=interaction(cell,datatype)))
```

Generally, allnoisesources is always below: length seems to be the culprit. Relative length is not conserved, if alpha were to be the same.


```{r}
#select a relevant lineage
selected_cells_gls <- glucose_data %>% 
  select(datatype,cell,time_sec,concentration,gl_id) %>% 
  pivot_wider(names_from = datatype,values_from = concentration) %>% 
  mutate(delta_c=allnoisesources-experimentaldata) %>% 
  mutate(delta_c=delta_c/experimentaldata) %>% 
  filter(delta_c<(-0.2)) %>% 
  distinct(cell,gl_id)

#Let's investigate, gl 3.6
gl0 <- "20190515.3.6"

glucose_data %>% 
  filter(gl_id==gl0) %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,log(length_um),col=datatype,group=interaction(cell,datatype)))+
  xlab("Time (h)")+
  ylab("Length (um)")+
  scale_y_continuous(trans="log10")+
  scale_color_manual(labels = c("Forward integration","Inferred data"),values=c("dodgerblue2","#FDBF6F"))

ggsave("./log_lentgh_time_hi1_glucose.pdf",height=10,width=40,limitsize = FALSE)


glucose_data %>% 
  filter(gl_id==gl0) %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,gfp_nb,col=datatype,group=interaction(cell,datatype)))

glucose_data %>% 
  filter(gl_id==gl0) %>% 
  ggplot()+
  geom_line(aes(time_sec/(60*3),log(length_um),col=datatype,group=interaction(cell,datatype)))
  #geom_line(data=glucose_data %>% 
  #            filter(gl_id==gl0) %>% 
  #            semi_join(selected_cells_gls %>% distinct(cell),by=c("cell"))
  #          ,aes(time_sec/3600,log(length_um),group=interaction(cell,datatype),alpha=0.1))

glucose_data %>% 
  filter(gl_id==gl0) %>% 
  ggplot()+
  geom_line(aes(time_sec/(60*3),gfp_nb,col=datatype,group=interaction(cell,datatype)))
```

# Report for rocket chat

Dear all, I investigated why the CV in inferred length and gfp data is systematically bigger than the CV from forward integration of inferred time derivatives (all noise sources included). It seems clear to me that it stems in the small difference between inferred measurement and inferred derivatives (\lambda and \q), which adds up and can lead to dramatic differences between inferred data and forward integration.

To illustrate the problem, I selected a symptomatic growth lane, in glucose. I plot here $log(l)$ versus time, for forward integration (blue) and inferred data (orange). Before 10h, inferred data and forward integration are pretty close. From 10h on, the root cell starts growing obviously slow (from 10h, it grows ~ twice as slow as the mean value for this data-set), and it takes it 5 hours to complete its cell cycle. By integrating the inferred growth rate (blue), we overestimates its growth compared to inferred data (orange). And this error is propagated to the offsprings from 15h on, which do look much bigger than what they were actually measured.

```{r}
glucose_data <- noise_contribution_data %>% 
  filter(datatype %in% c("experimentaldata","allnoisesources")) %>% 
  filter(condition=="glucose020")

#Let's investigate, gl 3.6
gl0 <- "20190515.3.6"

glucose_data %>% 
  filter(gl_id==gl0) %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,log(length_um),col=datatype,group=interaction(cell,datatype)))+
  xlab("Time (h)")+
  ylab("Length (um)")+
  scale_y_continuous(trans="log10")+
  scale_color_manual(labels = c("Forward integration","Inferred data"),values=c("dodgerblue2","#FDBF6F"))+
  theme_cowplot()

ggsave("./log_lentgh_time_hi1_glucose.pdf",height=8,width=60,limitsize = FALSE)
```

So what happens to gfp? For this cell that behaves wonky, it goes up as well, higher than in the inferred data (Q for this particular cell is close to the mean of the data set). Here is what happens for the concentration. 

```{r}
#Let's investigate, gl 3.6
gl0 <- "20190515.3.6"

glucose_data %>% 
  filter(gl_id==gl0) %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,gfp_nb,col=datatype,group=interaction(cell,datatype)))+
  xlab("Time (h)")+
  ylab("#GFP")+
  #scale_y_continuous(trans="log10")+
  scale_color_manual(labels = c("Forward integration","Inferred data"),values=c("dodgerblue2","#FDBF6F"))+
  theme_cowplot()

ggsave("./gfp_time_hi1_glucose.pdf",height=10,width=40,limitsize = FALSE)
```

For that cell, forward integration has smaller concentration than inferred data. Looking at other cells, we can see that this is quite general. Cells that tend to have high inferred data concentration, have lower forward integration, and vice versa. It is more dramatic with cells that display growth rate or production in the tail of the distributions. Altogether, the forward integration CV is smaller than our inferred data CV.

```{r}
#Let's investigate, gl 3.6
gl0 <- "20190515.3.6"

glucose_data %>% 
  filter(gl_id==gl0) %>% 
  ggplot()+
  geom_line(aes(time_sec/3600,concentration,col=datatype,group=interaction(cell,datatype)))+
  xlab("Time (h)")+
  ylab("Concentration")+
  #scale_y_continuous(trans="log10")+
  scale_color_manual(labels = c("Forward integration","Inferred data"),values=c("dodgerblue2","#FDBF6F"))+
  theme_cowplot()

ggsave("./concentration_time_hi1_glucose.pdf",height=10,width=40,limitsize = FALSE)
```
This is how the distributions of concentration look like, where we see that very high concentrations events present in inferred data (blue) disappear in the forward integration (red).

```{r}
plot_histogram <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  
  exp_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$concentration)
  sim_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$concentration)
  exp <- noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$concentration
  sim <- noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$concentration
  exp_density
  sim_density
  print(exp_density)
  print(sim_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  h_sim <- hist(sim, breaks = breakVec,plot=FALSE)
  if(plot){
  print(
  ggplot()+
    geom_col(aes(x=h_exp$mids,y=h_exp$counts,fill="#FDBF6F"),alpha=0.5)+
    geom_col(aes(x=h_sim$mids,y=h_sim$counts,fill="dodgerblue2"),alpha=0.5))+
      scale_y_continuous(trans = "log10")+
      ylab("Counts")+
      xlab("Concentration")+
      labs(fill = "Legend") +
      scale_fill_identity(name = "Data type",
                       breaks = c("dodgerblue2", "#FDBF6F"),
                       labels = c("Forward integration", "Inferred data"),
                       guide = "legend")+
      theme_cowplot()}
}

breakVec=seq(4000,45000,400)
plot_histogram("glucose020",breakVec,TRUE)
ggsave("./distribution.pdf",width=7,height=4)
```

The histograms look weird, but they are perfectly fine.
Here is a plot that shows the content of this last bin.

```{r}
.cond <- "glucose020"
breakVec=seq(4000,45000,400)
exp_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$concentration)
sim_density <- density(noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$concentration)
exp <- noise_contribution_data %>% filter(condition==.cond,datatype=="experimentaldata") %>% .$concentration
sim <- noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% .$concentration
exp_density
sim_density
print(exp_density)
print(sim_density)
h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
h_sim <- hist(sim, breaks = breakVec,plot=FALSE)


ptot <- ggplot()+
  geom_col(aes(x=h_exp$mids,y=h_exp$counts,fill="#FDBF6F"),alpha=0.5)+
  geom_col(aes(x=h_sim$mids,y=h_sim$counts,fill="dodgerblue2"),alpha=0.5)+
  scale_y_continuous(trans = "log10")+
  ylab("Counts")+
  xlab("Concentration")+
  labs(fill = "Legend") +
  scale_fill_identity(name = "Data type",
                   breaks = c("dodgerblue2", "#FDBF6F"),
                   labels = c("Forward integration", "Inferred data"),
                   guide = "legend")+
  theme_cowplot()

ptot

#Forward integration
# Determine last bin that's not empty
#n <- length(h_sim$breaks)
#l <- length(h_sim$counts)
n <- tail(which(h_sim$counts!=0),1)
last_breaks <- h_sim$breaks[c(n,n+1)]

last_bin <- noise_contribution_data %>% filter(condition==.cond,datatype=="allnoisesources") %>% 
  filter(dplyr::between(concentration,last_breaks[1],last_breaks[2]))

last_bin %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,concentration))

noise_contribution_data %>% 
  filter(condition==.cond,datatype=="allnoisesources") %>%
  ggplot()+
  geom_point(aes(time_sec/3600,concentration),alpha=0.2)+
  geom_hline(aes(yintercept=last_breaks[1]),col="red")+
  geom_hline(aes(yintercept=last_breaks[2]),col="red")+
  xlab("Time (h)")+
  ylab("Concentration")

ggsave("./last_bin_info.pdf",height=8,width=20)
  
```

```{r}
h_sim
```

# Compute naive estimate of the cells growth rate

Now that the data have been cleaned... I can produce a rough estimate of the growth rate.

```{r}
dt_df <- tibble(dt=c(12,12,6,3,1.5),condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

growth_data <- noise_contribution_data %>% 
  left_join(dt_df,by=c("condition")) %>% 
  group_by(promoter,condition,cell,datatype) %>% 
  arrange(time_sec) %>% 
  mutate(lambda_naive=(log_length-dplyr::lag(log_length))/dt) %>%
  #mutate(lambda_naive=2) %>%
  ungroup()

growth_data %>% 
  filter(condition=="glucose020",datatype %in% c("experimentaldata","allnoisesources")) %>% 
  ggplot()+
  geom_point(aes(lambda,lambda_naive,col=datatype),alpha=0.1)+
  geom_abline(aes(slope=1,intercept=0))+
  facet_wrap(~datatype)+
  ylab("Lambda (naive)")+
  xlab("Lambda (inferred)")
  #labs(color = "Legend") +
      #scale_color_identity(name = "Data type",
                          #breaks = c("dodgerblue2", "#FDBF6F"),
                          #labels = c("Forward integration", "Inferred data"))
```

# Bjoern rerun the whole inference. And got no trouble: keep that to show that inference ran twice, lead to the same results.

```{r}

experimental_data <- lapply(experimental_data_folder,function(.l){
  list.files(path=.l,pattern="denoised.csv$",recursive = TRUE,full.names=TRUE)}) %>% 
  unlist() %>% 
  lapply(function(.l) readr::read_csv(.l) %>% 
           mutate(path=.l)) %>% 
  do.call(rbind, .) %>% 
  mutate(datatype="experimentaldata") %>% 
  mutate(time_sec=time_min*60) %>% 
  mutate(log_length=log(length_um)) %>% 
  select(c("cell","time_min","parent","log_length","gfp_nb","lambda","q","promoter","condition","carbon_source","carbon_source_concentration","time_sec","length_um","datatype","path","mean_cell_rank","gl_id"))

mean_cell_rank_df <- experimental_data %>% 
  distinct(cell,mean_cell_rank,gl_id)

nrow(experimental_data %>% filter(condition=="glucose020"))
nrow(noise_contribution_data %>% filter(condition=="glucose020") %>% filter(datatype=="allnoisesources"))
```

```{r}
data_path <- c('/scicore/home/nimwegen/ksches0000/mother_machine/experimental_data/data_dany/data_dany_hi1_output_20230125/hi1_glucose020_f01234578910_b_prediction.csv','/scicore/home/nimwegen/rocasu25/Documents/Projects/biozentrum/gfp_fluctuations_project/denoising_raw_data/denoising_20230127152737/hi1_glucose020_rawdata_f01234578910_b_prediction.csv')
source_df <- tibble(denoised_data_path=data_path,source=c("bjoern","dany"))

our_data <- data_path %>% 
  lapply(function(.l) readr::read_csv(.l,skip=13) %>% 
           mutate(denoised_data_path=.l)) %>% 
  do.call(rbind,.) %>% 
  extract(denoised_data_path,"promotercondition","/([a-z0-9A-Z]{1,}_[0-9a-zA-Z]{1,})_[rawdata_]*[a-z0-9]{1,}_b_prediction.csv$",remove=FALSE,convert=FALSE) %>% 
  separate(promotercondition,into=c("promoter","condition"),sep="_") %>% 
  separate(condition,into=c("carbon_source","carbon_source_concentration"),sep="(?<=[A-Za-z])(?=[0-9])",remove=FALSE) %>% 
  mutate(carbon_source_concentration=as.double(carbon_source_concentration)/100) %>% 
  ungroup() %>% 
  rename(cell=cell_id,
         parent=parent_id,
         time_min=time,
         gfp_nb=mean_g,
         lambda=mean_l,
         q=mean_q) %>% 
  mutate(time_sec=time_min*60,
         length_um_raw=exp(log_length),
         gfp_nb_raw=fp,
         length_um=exp(mean_x)) %>% 
  select(-c(log_length,fp,mean_x)) %>% 
  left_join(source_df,by=c("denoised_data_path"))
```

```{r}
#Checking length estimation
our_data %>% 
  select(cell,time_sec,length_um,source) %>% 
  rename(variable=length_um) %>% 
  pivot_wider(names_from = source,values_from = variable) %>% 
  ggplot()+
  geom_point(aes(dany,bjoern))+
  ylab("Bjoern's length")+
  xlab("Dany's length")
  
#GFP
our_data %>% 
  select(cell,time_sec,gfp_nb,source) %>% 
  rename(variable=gfp_nb) %>% 
  pivot_wider(names_from = source,values_from = variable) %>% 
  ggplot()+
  geom_point(aes(dany,bjoern))+
  ylab("Bjoern's gfp")+
  xlab("Dany's gfp")

#lambda
our_data %>% 
  select(cell,time_sec,lambda,source) %>% 
  rename(variable=lambda) %>% 
  pivot_wider(names_from = source,values_from = variable) %>% 
  ggplot()+
  geom_abline(aes(slope=1,intercept=0),col="red")+
  geom_point(aes(dany,bjoern),alpha=0.1)+
  ylab("Bjoern's lambda")+
  xlab("Dany's lambda")

#production
our_data %>% 
  select(cell,time_sec,q,source) %>% 
  rename(variable=q) %>% 
  pivot_wider(names_from = source,values_from = variable) %>% 
  ggplot()+
  geom_point(aes(dany,bjoern),alpha=0.1)+
  geom_abline(aes(slope=1,intercept=0),col="red")+
  ylab("Bjoern's Q")+
  xlab("Dany's Q")
```



