---
title: "Fluorescence equivalence"
author: "Dany Chauvin"
date: '2022-10-10'
output: html_document
---

```{r message=FALSE,warning=FALSE}
source("./mother_machine_experiments_toolbox/loadFunctionsAndPackages.R")
path_to_MM_data_summary <- "./dataList.csv"
source("./mother_machine_experiments_toolbox/readMMData_20220131.R")
source("./mother_machine_experiments_toolbox/transformMMData.R")
source("./mother_machine_experiments_toolbox/inference_simulations_useful_functions.R")
path_to_MM_data_denoised <- "./20220919_predicted_data.csv"
path_to_inferred_parameters <- "./20220919_final_parameters.csv"
source("./mother_machine_experiments_toolbox/import_denoised_data.R")
```

```{r}
myframes %>% 
  group_by(date,condition,promoter) %>% 
  summarise(m_c=mean(gfp_nb/length_um_oriented_bbox,na.rm=TRUE))

myframes %>% group_by(date,condition,promoter) %>% 
  count()
```

# Establishing calibration curve between experimental setup 1 and 3 (respectively Stacy and Momo)

```{r}
data_to_plot <- myframes_complete %>% 
  ungroup() %>% 
  filter(condition %in% c("glucose")) %>% 
  filter(promoter %in% c("hi1","rrnB","rplN","med3")) %>% 
  group_by(cell) %>% 
  mutate(mean_concentration=mean(gfp_nb/length_um,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(cell,.keep_all=TRUE) %>% 
  group_by(condition,promoter,experimental_setup) %>% 
  mutate(mean_mean_concentration=mean(mean_concentration,na.rm=TRUE),
         sd_mean_concentration=sd(mean_concentration,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,promoter,mean_mean_concentration,sd_mean_concentration,experimental_setup)
```

```{r}
#Calibration in log space

data_to_plot %>% 
  pivot_wider(values_from = c("mean_mean_concentration","sd_mean_concentration"),names_from = c("experimental_setup")) %>% 
  mutate(s=compute_slope_errxy_robust(log(mean_mean_concentration_3),log(mean_mean_concentration_1)),
         i=compute_intercept_errxy_robust(log(mean_mean_concentration_3),log(mean_mean_concentration_1)),
         sd=compute_sdslope_errxy_robust(log(mean_mean_concentration_3),log(mean_mean_concentration_1))) %>% 
  ggplot()+
  geom_point(aes(log(mean_mean_concentration_3),log(mean_mean_concentration_1),col=promoter))+
  geom_errorbar(aes(x=log(mean_mean_concentration_3),ymin=log(mean_mean_concentration_1-sd_mean_concentration_1),ymax=log(mean_mean_concentration_1+sd_mean_concentration_1),col=promoter),width=0)+
  geom_errorbarh(aes(y=log(mean_mean_concentration_1),xmin=log(mean_mean_concentration_3-sd_mean_concentration_3),xmax=log(mean_mean_concentration_3+sd_mean_concentration_3),col=promoter),height=0)+
  geom_line(aes(log(mean_mean_concentration_3),log(mean_mean_concentration_3)*s+i),linetype="dashed")

data_to_plot %>% 
  pivot_wider(values_from = c("mean_mean_concentration","sd_mean_concentration"),names_from = c("experimental_setup")) %>% 
  mutate(s=compute_slope_errxy_robust(log(mean_mean_concentration_3),log(mean_mean_concentration_1)),
         i=compute_intercept_errxy_robust(log(mean_mean_concentration_3),log(mean_mean_concentration_1)),
         sd=compute_sdslope_errxy_robust(log(mean_mean_concentration_3),log(mean_mean_concentration_1)))
```

So according to this, the best conversion factor is exp(-0.389127)=0.678. Let's see how this is scaling. Because I also have to take into consideration, the fact that the cells did not grew at the exact same speed.

# Looking at growth rates

```{r}
data_to_plot <- myframes_complete %>% 
  ungroup() %>% 
  filter(condition %in% c("glucose")) %>% 
  filter(promoter %in% c("hi1","rrnB","rplN","med3")) %>% 
  distinct(cell,.keep_all=TRUE) %>% 
  group_by(condition,promoter,experimental_setup) %>% 
  mutate(mean_gr=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE),
         sd_gr=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,promoter,mean_gr,sd_gr,experimental_setup)
```

```{r}
#Calibration in log space
data_to_plot %>% 
  pivot_wider(values_from = c("mean_gr","sd_gr"),names_from = c("experimental_setup")) %>% 
  mutate(s=compute_slope_errxy_robust(mean_gr_3,mean_gr_1),
         i=compute_intercept_errxy_robust(mean_gr_3,mean_gr_1),
         sd=compute_sdslope_errxy_robust(mean_gr_3,mean_gr_1)) %>% 
  ggplot()+
  geom_point(aes(mean_gr_3,mean_gr_1,col=promoter))+
  geom_errorbar(aes(x=mean_gr_3,ymin=mean_gr_1-sd_gr_1,ymax=mean_gr_1+sd_gr_1,col=promoter),width=0)+
  geom_errorbarh(aes(y=mean_gr_1,xmin=mean_gr_3-sd_gr_3,xmax=mean_gr_3+sd_gr_3,col=promoter),height=0)+
  geom_abline(aes(slope=1,intercept=0))+
  coord_cartesian(xlim=c(0.5,1.5),ylim=c(0.5,1.5))
  #geom_line(aes(mean_gr_3,mean_gr_3*s+i),linetype="dashed")+

data_to_plot %>% 
  pivot_wider(values_from = c("mean_gr","sd_gr"),names_from = c("experimental_setup")) %>% 
  mutate(s=compute_slope_errxy_robust(mean_gr_3,mean_gr_1),
         i=compute_intercept_errxy_robust(mean_gr_3,mean_gr_1),
         sd=compute_sdslope_errxy_robust(mean_gr_3,mean_gr_1))
```

Growth-rate are similar in the two experiments: however, it seems that that cells a bit faster in the older experiments compared to the newest. This could explain the higher fluorescence that is witness.

```{r}
data_to_plot <- myframes_complete %>% 
  ungroup() %>% 
  filter(condition %in% c("glucose")) %>% 
  filter(promoter %in% c("hi1","rrnB","rplN","med3")) %>% 
  group_by(cell) %>% 
  mutate(mean_concentration=mean(gfp_nb/length_um,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(cell,.keep_all=TRUE) %>% 
  group_by(condition,promoter,experimental_setup) %>% 
  mutate(mean_gr=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE),
         sd_gr=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(mean_mean_concentration=mean(mean_concentration,na.rm=TRUE),
         sd_mean_concentration=sd(mean_concentration,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,promoter,mean_mean_concentration,sd_mean_concentration,experimental_setup) %>% 
  pivot_wider(values_from = c("mean_mean_concentration","sd_mean_concentration"),names_from = c("experimental_setup")) %>% 
  mutate(ratio=mean_mean_concentration_3/mean_mean_concentration_1)

data_to_plot
```

Hi1/med3/rplN/rrnB glucose experimental setup 3 are from one date: 20220707.
The same promoters in glucose for experimental setup 1 are from: 20190515 (hi1), 20190529 (med3 and rplN), 20190730 (rrnB).
The differences of ratio reflects that the variation of accuracy in our gfp measurements between experimental setup 1 and 3, are of the same order of the actual variations we see between between experiments on the same setup.
This can be confirmed, further down the line, with other experiments.


```{r}
data_to_plot <- myframes_complete %>% 
  ungroup() %>% 
  filter(condition %in% c("glucose")) %>% 
  filter(promoter %in% c("hi1","rrnB","rplN","med3")) %>% 
  group_by(cell) %>% 
  mutate(mean_concentration=mean(gfp_nb/length_um,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(cell,.keep_all=TRUE) %>% 
  group_by(condition,promoter,experimental_setup) %>% 
  mutate(mean_gr=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE),
         sd_gr=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(mean_mean_concentration=mean(mean_concentration,na.rm=TRUE),
         sd_mean_concentration=sd(mean_concentration,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,promoter,mean_mean_concentration,sd_mean_concentration,experimental_setup,mean_gr,sd_gr)
  #pivot_wider(values_from = c("mean_mean_concentration","sd_mean_concentration"),names_from = c("experimental_setup")) %>% 
  #mutate(ratio=mean_mean_concentration_3/mean_mean_concentration_1)

data_to_plot %>% 
  ggplot()+
  geom_point(aes(mean_gr,mean_mean_concentration,col=promoter,shape=experimental_setup))+
  geom_errorbar(aes(x=mean_gr,ymin=mean_mean_concentration-sd_mean_concentration,ymax=mean_mean_concentration+sd_mean_concentration,col=promoter))+
  scale_y_continuous(trans="log10")+
  ylab("Mean concentration (#GFP/um)")+
  xlab("Mean Growth rate (1/h)")
  #facet_wrap("promoter",scale="free")
```

```{r}
data_to_plot <- myframes_complete %>% 
  ungroup() %>% 
  filter(condition %in% c("glucose")) %>% 
  filter(promoter %in% c("hi1","rrnB","rplN","med3")) %>% 
  group_by(cell) %>% 
  dplyr::sample_n(1) %>% 
  mutate(mean_concentration=gfp_nb/length_um) %>% 
  ungroup() %>% 
  group_by(promoter,experimental_setup) %>% 
  dplyr::sample_n(285) %>% 
  ungroup() %>% 
  group_by(condition,promoter,experimental_setup) %>% 
  mutate(mean_gr=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE),
         sd_gr=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE),
         cv_gr=sd_gr/mean_gr) %>% 
  mutate(mean_mean_concentration=mean(mean_concentration,na.rm=TRUE),
         sd_mean_concentration=sd(mean_concentration,na.rm=TRUE),
         cv_mean_concentration=sd_mean_concentration/mean_mean_concentration) %>% 
  ungroup() %>% 
  distinct(condition,promoter,experimental_setup,cv_mean_concentration) %>% 
  pivot_wider(values_from = c("cv_mean_concentration"),names_from = c("experimental_setup"))
  #mutate(ratio=mean_mean_concentration_3/mean_mean_concentration_1)

data_to_plot %>% 
  rename("setup_3"="3") %>% 
  rename("setup_1"="1") %>% 
  ggplot()+
  geom_point(aes(setup_3,setup_1,col=promoter))+
  geom_abline(aes(slope=1,intercept=0),alpha=0.5)+
  ylab("CV concentration setup 1")+
  xlab("CV concentration setup 3")+
  coord_cartesian(xlim=c(0,0.75),ylim=c(0,0.75))
  #facet_wrap("promoter",scale="free")
```


```{r}
data_to_plot <- myframes_complete %>% 
  ungroup() %>% 
  filter(condition %in% c("glucose")) %>% 
  filter(promoter %in% c("hi1","rrnB","rplN","med3")) %>% 
  group_by(cell) %>% 
  mutate(mean_concentration=mean(gfp_nb/length_um,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(cell,.keep_all=TRUE) %>% 
  group_by(condition,promoter,experimental_setup) %>% 
  mutate(mean_gr=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE),
         sd_gr=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(mean_mean_concentration=mean(mean_concentration,na.rm=TRUE),
         sd_mean_concentration=sd(mean_concentration,na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(condition,promoter,mean_mean_concentration,sd_mean_concentration,experimental_setup,mean_gr,sd_gr)
  #pivot_wider(values_from = c("mean_mean_concentration","sd_mean_concentration"),names_from = c("experimental_setup")) %>% 
  #mutate(ratio=mean_mean_concentration_3/mean_mean_concentration_1)

data_to_plot %>% 
  ggplot()+
  geom_point(aes())+
```
  


Data acquired on Momo, must be downscaled by a factor 11697/13021=0.68
(to be confirmed and improved with other fluorescence data).

```{r}
conversion_factor <- 0.8983042
myframes_complete_corrected <- myframes_complete %>% 
  mutate(date=as.double(as.character(date))) %>% 
  mutate(gfp_nb=ifelse(date>20220701,gfp_nb*conversion_factor,gfp_nb))

myframes_complete_corrected %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha)
```

```{r}
myframes_complete_corrected %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha) %>% 
  ggplot()+
  geom_point(aes(m_alpha,m_c,col=interaction(date,condition)))+
  geom_errorbar(aes(x=m_alpha,ymin=m_c-sd_c,ymax=m_c+sd_c),width=0)+
  theme_cowplot()

myframes_complete_corrected %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha) %>% 
  ggplot()+
  geom_point(aes(m_alpha,m_c,col=interaction(date,condition)))+
  geom_errorbar(aes(x=m_alpha,ymin=m_c-sd_c,ymax=m_c+sd_c),width=0)+
  scale_x_continuous(trans="log10")+
  theme_cowplot()

myframes_complete_corrected %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha) %>% 
  ggplot()+
  geom_point(aes(m_alpha,m_c,col=interaction(date,condition)))+
  geom_errorbar(aes(x=m_alpha,ymin=m_c-sd_c,ymax=m_c+sd_c),width=0)+
  scale_y_continuous(trans="log10")+
  theme_cowplot()

myframes_complete_corrected %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha) %>% 
  ggplot()+
  geom_point(aes(m_alpha,m_c,col=interaction(date,condition)))+
  geom_errorbar(aes(x=m_alpha,ymin=m_c-sd_c,ymax=m_c+sd_c),width=0)+
  scale_y_continuous(trans="log10")+
  scale_x_continuous(trans="log10")+
  theme_cowplot()
```

```{r}
myframes_complete %>% 
  mutate(date=as.double(as.character(date))) %>% 
  filter(date>20220701) %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha) %>% 
  ggplot()+
  geom_point(aes(m_alpha,m_c,col=interaction(date,condition)))+
  geom_errorbar(aes(x=m_alpha,ymin=m_c-sd_c,ymax=m_c+sd_c),width=0)+
  theme_cowplot()

myframes_complete %>% 
  mutate(date=as.double(as.character(date))) %>% 
  filter(date>20220701) %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha) %>% 
  ggplot()+
  geom_point(aes(m_alpha,m_c,col=interaction(date,condition)))+
  geom_errorbar(aes(x=m_alpha,ymin=m_c-sd_c,ymax=m_c+sd_c),width=0)+
  scale_x_continuous(trans="log10")+
  theme_cowplot()

myframes_complete %>% 
  mutate(date=as.double(as.character(date))) %>% 
  filter(date>20220701) %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha) %>% 
  ggplot()+
  geom_point(aes(m_alpha,m_c,col=interaction(date,condition)))+
  geom_errorbar(aes(x=m_alpha,ymin=m_c-sd_c,ymax=m_c+sd_c),width=0)+
  scale_y_continuous(trans="log10")+
  theme_cowplot()

myframes_complete %>% 
  mutate(date=as.double(as.character(date))) %>% 
  filter(date>20220701) %>% 
  filter(promoter=="hi1") %>% 
  group_by(date,condition,promoter) %>% 
  mutate(c=gfp_nb/length_um_oriented_bbox) %>% 
  mutate(m_c=mean(c,na.rm=TRUE)) %>%
  mutate(sd_c=sd(c,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(date,condition,promoter) %>% 
  mutate(m_alpha=mean(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  mutate(sd_alpha=sd(alpha_oriented_bbox*3600/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(date,condition,promoter,m_c,sd_c,m_alpha,sd_alpha) %>% 
  ggplot()+
  geom_point(aes(m_alpha,m_c,col=interaction(date,condition)))+
  geom_errorbar(aes(x=m_alpha,ymin=m_c-sd_c,ymax=m_c+sd_c),width=0)+
  scale_y_continuous(trans="log10")+
  scale_x_continuous(trans="log10")+
  theme_cowplot()
```
# Write data for Bjoern

```{r}
myframes_towrite <- myframes_complete %>% 
  filter(promoter=="hi1") %>% 
  filter(date %in% c(20190515,20220824,20220921)) %>% 
  select(c("date","length_um_oriented_bbox","gfp_nb","cell","parent","time_sec","condition")) %>% 
  rename(length_um=length_um_oriented_bbox) %>% 
  group_by(cell) %>% 
  #mutate(not_complete=any_vars(is.na(.))) %>% 
  mutate(not_complete=(if_any(everything(), ~ is.na(.)))) %>% 
  mutate(missing=sum(not_complete)) %>% 
  filter(missing==0) %>% 
  ungroup() %>% 
  arrange(condition,cell,time_sec)
  #mutate(cell=paste(cell,".1.0",sep="")) %>% 
  #mutate(parent=paste(parent,".1.0",sep=""))
```

```{r}
readr::write_csv(myframes_towrite %>% filter(condition=="acetate"),"./raw_data_20221011/acetate_hi1.csv")
readr::write_csv(myframes_towrite %>% filter(condition=="glucose"),"./raw_data_20221011/glucose_hi1.csv")
readr::write_csv(myframes_towrite %>% filter(condition=="glucoseaa"),"./raw_data_20221011/glucoseaa_hi1.csv")
readr::write_csv(myframes_towrite %>% filter(condition=="glycerol"),"./raw_data_20221011/glycerol_hi1.csv")
```
