---
title: "growth_production_heatmap.Rmd"
author: "Dany Chauvin"
date: '2023-01-30'
output: html_document
---

We want to plot, a heat-map of actual growth-rate versus production (mean).
For each condition for hi1.

# Importing data

We assume here, denoised data were already saved in ./denoised_data

```{r message=FALSE,warning=FALSE}
source("../mother_machine_experiments_toolbox/load_functions_and_packages.R")
source("../mother_machine_experiments_toolbox/inference_simulations_useful_functions.R")
#load myframes uncomplete and complete cell cycles.
#source("../mother_machine_experiments_toolbox/load_denoised_data.R")
#load only full cell cycles
source("../mother_machine_experiments_toolbox/load_denoised_data_complete_cycles.R")
```

# Adding to myframes typical doubling times

```{r}
myframes <- myframes %>% 
  group_by(cell) %>% 
  arrange(time_sec) %>% 
  mutate(div_time=(last(time_sec)-first(time_sec))/3600) %>% 
  ungroup()

p <- 6 #number of doubling times to consider to get rid of the transient
#6 typical doubling times

conditions <- c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020")

doubling_times_df <- myframes %>% 
  filter(condition %in% conditions) %>% 
  group_by(condition,promoter,cell) %>% 
  sample_n(1) %>% 
  ungroup %>% 
  group_by(condition,promoter) %>% 
  mutate(#w=sum(1/abs(cov_ll)),
         #w_i=1/abs(cov_ll),
         #mean_l=sum(lambda*w_i)*1/w,
         mean_l=mean(lambda,.na.rm=TRUE),
         mean_doubling_time=1/(mean_l*60/log(2))) %>% 
  ungroup() %>% 
  distinct(condition,mean_doubling_time) %>% 
  mutate(time_interval=p*mean_doubling_time)

myframes <- myframes %>% 
  left_join(doubling_times_df,by=c("condition")) %>% 
  group_by(condition) %>% 
  mutate(time_h_rescaled=time_sec/3600-min(time_sec)/3600) %>% 
  #filter(time_h_rescaled>time_interval) %>% 
  ungroup() %>% 
  #filter(div_time<mean_doubling_time*4) %>% 
  mutate(concentration=gfp_nb/length_um)
```

# Plot scatter heat map on a single pdf file

```{r}
conditions <- c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020")
plot_heatscatter <- function(cond,prom){

 x <- myframes %>%
  filter(cell!="20220921.1.48.121") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$lambda
  
y <- myframes %>%
  filter(cell!="20220921.1.48.121") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$q
  
nb_cell_cycles <- nrow(myframes %>%
  filter(condition==cond,promoter==prom) %>% 
  distinct(cell))

nb_measurement <- nrow(myframes %>%
  filter(condition==cond,promoter==prom))

nb_gl <- nrow(myframes %>%
  filter(condition==cond,promoter==prom) %>% 
    distinct(gl_id))

df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top
#pdf(file=paste("./figures/",cond,".pdf",sep=""))
plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,
           xlab="Exponential growth-rate (/min)",ylab="Volumic production (GFP/min)",main=sprintf("%s, %s observations, %s cycles, %s gls",cond,nb_measurement,nb_cell_cycles,nb_gl))
#dev.off()}
}
```

```{r}
pdf(file=paste("./figures/all_2d_heatmap_scatter.pdf",sep=""),width=25,height=4)
par(mfrow=c(1,5))
plot_heatscatter("acetate005","hi1")
plot_heatscatter("acetate020","hi1")
plot_heatscatter("glycerol040","hi1")
plot_heatscatter("glucose020","hi1")
plot_heatscatter("glucoseaa020","hi1")
dev.off()
```

# Plotting correlation with lines (to discard)

This correlation are naive.

```{r}
plot_histogram_lambda <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  exp_density <- density(myframes %>% filter(condition==.cond) %>% .$lambda)
  exp <- myframes %>% filter(condition==.cond) %>% filter(!(cell %in% c("20190515.3.9.79","20220921.1.48.121"))) %>% .$lambda
  exp_density
  print(exp_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  if(plot){
    plot(x=h_exp$mids,y=h_exp$counts, type='l', col='black',
           xlab="Exponential growth-rate (/min)",ylab="Counts",main=sprintf("%s",.cond),log="y")}
  #ggsave(sprintf("./lambda_1D_%s.pdf",.cond),width=6,height=4)
}

plot_histogram_q <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  exp_density <- density(myframes %>% filter(condition==.cond) %>% .$q)
  exp <- myframes %>% filter(condition==.cond) %>% filter(!(cell %in% c("20190515.3.9.79","20220921.1.48.121"))) %>% .$q
  exp_density
  print(exp_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  if(plot){
    plot(x=h_exp$mids,y=h_exp$counts, type='l', col='black',
           xlab="Production (GFP/min)",ylab="Counts",main=sprintf("%s",.cond),log="y")}
  #ggsave(sprintf("./lambda_1D_%s.pdf",.cond),width=6,height=4)
}
```

```{r}
pdf(file=paste("./figures/all_1D_histogram.pdf",sep=""),width=25,height=8)
par(mfrow=c(2,5))
breakVec=seq(-0.0007,0.006,0.000025)
plot_histogram_lambda("acetate005",breakVec,TRUE)
breakVec=seq(-0.0013,0.01,0.000025)
plot_histogram_lambda("acetate020",breakVec,TRUE)
breakVec=seq(-0.0015,0.011,0.000025)
plot_histogram_lambda("glycerol040",breakVec,TRUE)
breakVec=seq(-0.005,0.022,0.0001)
plot_histogram_lambda("glucose020",breakVec,TRUE)
breakVec=seq(-0.0055,0.037,0.0001)
plot_histogram_lambda("glucoseaa020",breakVec,TRUE)
breakVec=seq(-14,91,0.6)
plot_histogram_q("acetate005",breakVec,TRUE)
breakVec=seq(-19,160,0.6)
plot_histogram_q("acetate020",breakVec,TRUE)
breakVec=seq(-110,350,1)
plot_histogram_q("glycerol040",breakVec,TRUE)
breakVec=seq(-130,600,1)
plot_histogram_q("glucose020",breakVec,TRUE)
breakVec=seq(-160,700,1)
plot_histogram_q("glucoseaa020",breakVec,TRUE)
dev.off()
```

# Converting histogram to proper dataframe for plotting (to discard)

```{r}
get_histogram_lambda <- function(.cond,breakVec=seq(4000,43000,500)){
  exp_density <- density(myframes %>% filter(condition==.cond) %>% .$lambda)
  exp <- myframes %>% filter(condition==.cond) %>% filter(!(cell %in% c("20190515.3.9.79","20220921.1.48.121"))) %>% .$lambda
  exp_density
  print(exp_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  df <- tibble(counts=h_exp$counts,mids=h_exp$mids,condition=.cond,variable="q")
  return(df)
  }

get_histogram_q <- function(.cond,breakVec=seq(4000,43000,500)){
  exp_density <- density(myframes %>% filter(condition==.cond) %>% .$q)
  exp <- myframes %>% filter(condition==.cond) %>% filter(!(cell %in% c("20190515.3.9.79","20220921.1.48.121"))) %>% .$q
  exp_density
  print(exp_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  df <- tibble(counts=h_exp$counts,mids=h_exp$mids,condition=.cond,variable="lambda")
  return(df)
}

data <- rbind(
get_histogram_lambda("acetate005",seq(-0.0007,0.006,0.000025)),
get_histogram_lambda("acetate020",seq(-0.0013,0.01,0.000025)),
get_histogram_lambda("glycerol040",seq(-0.0015,0.011,0.000025)),
get_histogram_lambda("glucose020",seq(-0.005,0.022,0.0001)),
get_histogram_lambda("glucoseaa020",seq(-0.0055,0.037,0.0001)),
get_histogram_q("acetate005",seq(-14,91,0.6)),
get_histogram_q("acetate020",seq(-19,160,0.6)),
get_histogram_q("glycerol040",seq(-110,350,1)),
get_histogram_q("glucose020",seq(-130,600,1)),
get_histogram_q("glucoseaa020",seq(-160,700,1)))

```

# Plotting production and growth rate distribution using ggplot

```{r}
myframes %>% 
  mutate(condition=factor(condition,levels=conditions)) %>% 
  filter(!(cell %in% c("20190515.3.9.79","20220921.1.48.121"))) %>% 
  ggplot(aes(x=lambda))+
  geom_freqpoly(aes(y=after_stat(density),col=condition),binwidth = 0.00005)+
  theme_cowplot()+
  ylab("Density")+
  xlab("Growth-rate (/min)")
ggsave("./figures/gr_all.pdf",width=10,height=5)

myframes %>% 
  mutate(condition=factor(condition,levels=conditions)) %>% 
  filter(!(cell %in% c("20190515.3.9.79","20220921.1.48.121"))) %>% 
  ggplot(aes(x=q))+
  geom_freqpoly(aes(y=after_stat(density),col=condition),binwidth=1)+
  theme_cowplot()+
  ylab("Density")+
  xlab("Production (#GFP/min)")
ggsave("./figures/q_all.pdf",width=10,height=5)
```
```{r}
gr <- myframes %>% 
  mutate(condition=factor(condition,levels=conditions)) %>% 
  filter(!(cell %in% c("20190515.3.9.79","20220921.1.48.121"))) %>% 
  ggplot(aes(x=lambda))+
  geom_freqpoly(aes(y=after_stat(density),col=condition),binwidth = 0.00005)+
  theme_cowplot()+
  scale_y_continuous(trans="log10")+
  ylab("Density")+
  xlab("Growth-rate (/min)")


q <- myframes %>% 
  mutate(condition=factor(condition,levels=conditions)) %>% 
  filter(!(cell %in% c("20190515.3.9.79","20220921.1.48.121"))) %>% 
  ggplot(aes(x=q))+
  geom_freqpoly(aes(y=after_stat(density),col=condition),binwidth=1)+
  theme_cowplot()+
  scale_y_continuous(trans="log10")+
  ylab("Density")+
  xlab("Production (#GFP/min)")

ptot <- plot_grid(gr,q,nrow=1)
ptot
ggsave("./figures/q_gr_all.pdf",width=15,height=5)
```

