---
title: "hi1_all_conditions_denoised_20221202.Rmd"
author: "Dany Chauvin"
date: '2022-12-02'
output: html_document
---

# Import packages and functions as well as data

```{r}
source("./mother_machine_experiments_toolbox/load_functions_and_packages.R")
myframes_final <- readr::read_csv("./denoised_data_hi1_all_conditions_20221202/hi1_allconditions_final.csv")

if(!exists("mycluster")){
mycluster <- min(30, parallel::detectCores()-1) %>%  # do not use more than 30 cores
  default_cluster() %>% cluster_library( # load currently loaded packages on each core
    names(sessionInfo()$otherPkgs))
  
cluster_copy(mycluster,c("fit_exp_elongation_predict","fit_exp_elongation_slope","fit_exp_elongation_sd_slope","fit_exp_elongation_intercept"))
}

#cluster_copy(mycluster,c("fit_exp_elongation_predict","fit_exp_elongation_slope","fit_exp_elongation_sd_slope","fit_exp_elongation_intercept","N0","random_selection","N"))

myframes_final <- myframes_final %>% 
  group_by(row_number()) %>% 
  partition(mycluster) %>% 
  #rowwise() %>% 
  mutate(lambda_m=ifelse(is.na(cov_ll)==FALSE,rnorm(1,mean=lambda,sd=sqrt(abs(cov_ll))),lambda),
  q_m=ifelse(is.na(cov_qq)==FALSE,rnorm(1,mean=q,sd=sqrt(abs(cov_qq))),q),
  gfp_nb_m=ifelse(is.na(cov_gg)==FALSE,rnorm(1,mean=gfp_nb,sd=sqrt(abs(cov_gg))),gfp_nb),
  length_um_m=ifelse(is.na(cov_xx)==FALSE,exp(rnorm(1,mean=log(length_um),sd=sqrt(abs(cov_xx)))),length_um)) %>% 
  mutate(c_m=gfp_nb_m/length_um_m) %>% 
  ungroup() %>% 
  collect() %>% 
  ungroup()
```


# Check denoising of the data, looking at predicted values

Randomly select 10 cells per condition, and check the goodness of the fit.

```{r}
selected_cells <- myframes_final %>% 
  filter(date=="20220824") %>% 
  distinct(cell,condition) %>% 
  group_by(condition) %>% 
  sample_n(10) %>% 
  ungroup()

toplot <- myframes_final %>% 
  semi_join(selected_cells,by=c("cell","condition"))

toplot %>% 
  ggplot()+
  geom_point(aes(time_sec,lambda))+
  geom_point(aes(time_sec,lambda_m),col="blue")+
  geom_line(aes(time_sec,lambda),col="red")+
  facet_wrap(~paste(condition,cell),scale="free")
```

```{r}
selected_cells <- myframes_final %>% 
  filter(date=="20220824") %>% 
  distinct(cell,condition) %>% 
  group_by(condition) %>% 
  sample_n(10) %>% 
  ungroup()

toplot <- myframes_final %>% 
  semi_join(selected_cells,by=c("cell","condition"))

toplot %>% 
  ggplot()+
  geom_point(aes(time_sec,q))+
  geom_point(aes(time_sec,q_m),col="blue")+
  geom_line(aes(time_sec,q),col="red")+
  facet_wrap(~paste(condition,cell),scale="free")
```

```{r}
selected_cells <- myframes_final %>% 
  filter(condition=="acetate020") %>% 
  distinct(cell,condition) %>% 
  group_by(condition) %>% 
  sample_n(10) %>% 
  ungroup()

toplot <- myframes_final %>% 
  semi_join(selected_cells,by=c("cell","condition"))

toplot %>% 
  ggplot()+
  geom_point(aes(time_sec,gfp_nb_raw))+
  geom_point(aes(time_sec,gfp_nb_m),col="blue")+
  geom_line(aes(time_sec,gfp_nb),col="red")+
  facet_wrap(~paste(condition,cell),scale="free")
```

```{r}
selected_cells <- myframes_final %>% 
  filter(condition=="acetate020") %>% 
  distinct(cell,condition) %>% 
  group_by(condition) %>% 
  sample_n(10) %>% 
  ungroup()

toplot <- myframes_final %>% 
  semi_join(selected_cells,by=c("cell","condition"))

toplot %>% 
  ggplot()+
  geom_point(aes(time_sec,length_um_raw))+
  geom_point(aes(time_sec,length_um_m),col="blue")+
  geom_line(aes(time_sec,length_um),col="red")+
  facet_wrap(~paste(condition,cell),scale="free")
```

# How many cells per condition per rank are there?

```{r}
myframes_final %>% 
  distinct(cell,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  summarise(n=n())

myframes_final$condition <- factor(myframes_final$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

myframes_final %>% 
  distinct(cell,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  summarise(n=n()) %>% 
  ggplot()+
  geom_col(aes(mean_cell_rank,n))+
  facet_grid(.~condition)+
  xlab("Mean cell rank")+
  ylab("# of cells")+
  theme_cowplot()
```

# Compute mean growth rate over cell cycles, stratified by mean_cell_rank

```{r}
myframes_final$mean_cell_rank <- factor(myframes_final$mean_cell_rank,levels = c(0:10))
myframes_final$condition <- factor(myframes_final$condition,levels = c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

myframes_final %>% 
  group_by(cell) %>% 
  mutate(lambda_cell=mean(lambda*60/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(mean_cell_rank,condition,.keep_all=TRUE) %>% 
  ggplot()+
  geom_point(aes(mean_cell_rank,mean_lambda_cell,col=condition))+
  geom_errorbar(aes(x=mean_cell_rank,ymin=mean_lambda_cell-sd_lambda_cell,ymax=mean_lambda_cell+sd_lambda_cell,col=condition))+
  theme_cowplot()+
  scale_y_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2,4))+
  xlab("Mean cell rank")+
  ylab("Mean Growth Rate")
```

```{r}
myframes_final$mean_cell_rank <- factor(myframes_final$mean_cell_rank,levels = c(0:10))
myframes_final$condition <- factor(myframes_final$condition,levels = c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

myframes_final %>% 
  group_by(cell) %>% 
  mutate(lambda_cell=mean(lambda*60/log(2),na.rm=TRUE)) %>% 
  ungroup() %>% 
  distinct(cell,.keep_all=TRUE) %>% 
  ggplot()+
  stat_ecdf(aes(lambda_cell,col=mean_cell_rank),size=0.25)+
  #geom_point(aes(mean_cell_rank,mean_lambda_cell,col=condition))+
  #geom_errorbar(aes(x=mean_cell_rank,ymin=mean_lambda_cell-sd_lambda_cell,ymax=mean_lambda_cell+sd_lambda_cell,col=condition))+
  theme_cowplot()+
  facet_grid(condition~.)+
  scale_x_continuous(trans='log',breaks=c(0.0625,0.125,0.25,0.5,1,2,4))+
  scale_y_continuous(breaks=c(0,0.5,1))+
  guides(col=guide_legend(title="Cell rank"))+
  theme(strip.text.y = element_text(size = 4),
        axis.text.y = element_text(size=5),
        axis.text.x = element_text(size=5),
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10),
        legend.title = element_text(size=5),
        legend.text =  element_text(size=5)
        )+
  xlab("Growth rate (h-1)")+
  ylab("CDF")

ggsave("./20221208_presentation/GR_all_conditions.pdf",width=3,height=3)
```

```{r}
myframes_final$condition <- factor(myframes_final$condition,levels = c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

myframes_final %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_gr=mean(alpha_oriented_bbox*3600/log(2))) %>% 
  mutate(sd_gr=sd(alpha_oriented_bbox*3600/log(2))) %>% 
  mutate(cv_gr=sd_gr/mean_gr) %>% 
  ungroup() %>% 
  distinct(condition,mean_cell_rank,mean_gr,sd_gr,cv_gr) %>% 
  group_by(condition) %>% 
  mutate(rank_0_gr=dplyr::first(mean_gr),
         gr_ratio=mean_gr/rank_0_gr) %>% 
  select(-rank_0_gr) %>% 
  ungroup() %>% 
  ggplot()+
  geom_col(aes(mean_cell_rank,mean_gr,fill=condition))+
  geom_errorbar(aes(x=mean_cell_rank,ymin=mean_gr-sd_gr,ymax=mean_gr+sd_gr,ymax=0))+
  facet_grid(.~condition)+
  theme_cowplot()+
  xlab("Cell rank")+
  ylab("Mean growth rate (h-1)")
```

# Sampling cells

Sample ten times and plot CV together with error bars. Also compare with overall CV, without stratifying by cell-rank.

```{r}
N <- 50
N0 <- 10

random_selection <- function(.d,.N,.N0){
  #.d: input dataframe
  #.N: Number of cells to pick per group
  #.N0 number of 'bags'
  
  .df <- .d %>% 
        group_by(cell) %>%  #already grouped by condition, promoter, type, simulationid
        sample_n(1) %>% 
        #mutate(lambda_cell=mean(lambda*60/log(2),na.rm=TRUE)) %>% 
        ungroup() %>% 
        #distinct(cell,.keep_all = TRUE) %>% 
        sample_n(.N) %>% 
        mutate(sampling=1)
  
  for(i in 2:.N0){
    .df_new <- .d %>% 
        group_by(cell) %>%  #already grouped by condition, promoter, type, simulationid
        sample_n(1) %>% 
        #mutate(lambda_cell=mean(lambda*60/log(2),na.rm=TRUE)) %>% 
        ungroup() %>% 
        #distinct(cell,.keep_all = TRUE) %>% 
        sample_n(.N) %>% 
        mutate(sampling=i)
    .df <- rbind(.df,.df_new)}
  
  return(.df)}

if(!exists("mycluster")){
mycluster <- min(30, parallel::detectCores()-1) %>%  # do not use more than 30 cores
  default_cluster() %>% cluster_library( # load currently loaded packages on each core
    names(sessionInfo()$otherPkgs))
  
cluster_copy(mycluster,c("fit_exp_elongation_predict","fit_exp_elongation_slope","fit_exp_elongation_sd_slope","fit_exp_elongation_intercept"))
}

cluster_copy(mycluster,c("fit_exp_elongation_predict","fit_exp_elongation_slope","fit_exp_elongation_sd_slope","fit_exp_elongation_intercept","N0","random_selection","N"))

selected_conditions <- myframes_final %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(promoter,mean_cell_rank,condition) %>% 
  filter(n()>50) %>% 
  ungroup() %>% 
  distinct(promoter,mean_cell_rank,condition)

myframes_sampled <- myframes_final %>% 
  semi_join(selected_conditions,by=c("promoter","mean_cell_rank","condition")) %>% 
  group_by(cell) %>% 
  partition(cluster=mycluster) %>%
  arrange(frame) %>% 
  mutate(alpha=fit_exp_elongation_slope(time_sec,length_um_m)) %>% 
  mutate(lambda_cell=mean(lambda_m*60/log(2),na.remove=TRUE)) %>% 
  mutate(q_cell=mean(q_m,na.remove=TRUE)) %>% 
  mutate(q_full_cellcycle=(last(gfp_nb_m)-first(gfp_nb_m))/(last(length_um_m)-first(length_um_m))*alpha) %>% 
  collect() %>% 
  ungroup() %>% 
  group_by(condition,promoter,mean_cell_rank) %>% 
  partition(cluster=mycluster) %>%
  do((function(.df){
    .new_df <- random_selection(.df,N,N0)
    return(.new_df)})
    (.)) %>% 
  collect() %>% 
  ungroup()
```
# Mean growth rate CV, stratfying and not stratifying by cell rank

```{r}
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))
```

```{r}
toplot <- myframes_sampled %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  

conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))


myframes_sampled %>%
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_cv_lambda_cell,col=condition_explicit,shape=mean_cell_rank))+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_cv_lambda_cell-sd_cv_lambda_cell,ymax=mean_cv_lambda_cell+sd_cv_lambda_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_cv_lambda_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_cv_lambda_cell,col=condition_explicit),alpha=0.2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_cv_lambda_cell-sd_cv_lambda_cell,ymax=mean_cv_lambda_cell+sd_cv_lambda_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_cv_lambda_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,0.5)+
  xlim(0,3)+
  scale_x_continuous(trans='log',breaks=c(0.0625,0.125,0.25,0.5,1,2))+
  xlab("Mean growth rate (h-1)")+
  ylab("Growth rate CV")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/cv_gr_mean_gr.pdf",width=6,height=4)
```

```{r}
toplot <- myframes_sampled %>% 
  mutate(lambda_cell=lambda*60/log(2)) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sqrt(mean(lambda_cell**2+cov_ll)-mean_lambda_cell**2)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  

conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))


myframes_sampled %>%
  mutate(lambda_cell=lambda*60/log(2)) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sqrt(mean(lambda_cell**2+cov_ll)-mean_lambda_cell**2)) %>%
  #mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_cv_lambda_cell,col=condition_explicit,shape=mean_cell_rank))+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_cv_lambda_cell-sd_cv_lambda_cell,ymax=mean_cv_lambda_cell+sd_cv_lambda_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_cv_lambda_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_cv_lambda_cell,col=condition_explicit),alpha=0.2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_cv_lambda_cell-sd_cv_lambda_cell,ymax=mean_cv_lambda_cell+sd_cv_lambda_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_cv_lambda_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,0.5)+
  xlim(0,3)+
  scale_x_continuous(trans='log',breaks=c(0.0625,0.125,0.25,0.5,1,2))+
  xlab("Mean growth rate (h-1)")+
  ylab("Growth rate CV")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/cv_gr_mean_gr_using_error.pdf",width=6,height=4)
```


# Mean growth rate CV, stratfying and not stratifying by cell rank, instantaneous values

```{r}
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))
```

```{r}
toplot <- myframes_sampled %>% 
  mutate(lambda_cell=lambda_m*60/log(2)) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  #mutate(mean_lambda_cell=lambda_m*60/log(2)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  

conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))


myframes_sampled %>%
  mutate(lambda_cell=lambda_m*60/log(2)) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  #mutate(mean_lambda_cell=lambda_m*60/log(2)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_cv_lambda_cell,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_cv_lambda_cell-sd_cv_lambda_cell,ymax=mean_cv_lambda_cell+sd_cv_lambda_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_cv_lambda_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_cv_lambda_cell,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_cv_lambda_cell-sd_cv_lambda_cell,ymax=mean_cv_lambda_cell+sd_cv_lambda_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_cv_lambda_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,0.5)+
  xlim(0,3)+
  scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  xlab("Mean growth rate (h-1)")+
  ylab("Growth rate CV")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/gr_cv_vs_mean_gr.pdf",width=8,height=4)
```



# Mean production versus mean growth rate

```{r}
toplot <- myframes_sampled %>% 
  mutate(q_cell=q_m) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
myframes_sampled %>%
  mutate(q_cell=q_m) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_mean_q_cell,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_mean_q_cell-sd_mean_q_cell,ymax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_mean_q_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_mean_q_cell,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_mean_q_cell-sd_mean_q_cell,ymax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_mean_q_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,250)+
  xlim(0,2.5)+
  #scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  xlab("Mean Growth Rate (h-1)")+
  ylab("Mean volumic production (#GFP/min/um)")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/mean_q_cv_vs_mean_gr.pdf",width=8,height=4)

```

```{r}
toplot <- myframes_sampled %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
myframes_sampled %>%
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_mean_q_cell,col=condition_explicit,shape=mean_cell_rank))+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_mean_q_cell-sd_mean_q_cell,ymax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_mean_q_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_mean_q_cell,col=condition_explicit),alpha=0.2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_mean_q_cell-sd_mean_q_cell,ymax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_mean_q_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  #ylim(0,0.5)+
  #xlim(0,3)+
  scale_y_continuous(trans='log',breaks=c(5,10,20,40,80,160,320,640))+
  scale_x_continuous(trans='log',breaks=c(0.0625,0.125,0.25,0.5,1,2))+
  xlab("Mean Growth Rate (h-1)")+
  ylab("Mean volumic production (#GFP/min/um)")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))
```


```{r}
toplot <- myframes_sampled %>% 
  mutate(q_cell=q) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(s=compute_slope_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell)) %>% 
  mutate(sd=compute_sdslope_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell)) %>% 
  mutate(b=compute_intercept_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>%


  
myframes_sampled %>%
  mutate(q_cell=q) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_mean_q_cell,col=condition_explicit,shape=mean_cell_rank))+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_mean_q_cell-sd_mean_q_cell,ymax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_mean_q_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_mean_q_cell,col=condition_explicit),alpha=0.2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_mean_q_cell-sd_mean_q_cell,ymax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  geom_line(data=toplot,aes(mean_mean_lambda_cell,mean_mean_lambda_cell*s+b),col="red",linetype="dashed",alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_mean_q_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,250)+
  xlim(0,2.5)+
  #scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  xlab("Mean Growth Rate (h-1)")+
  ylab("Mean volumic production (#GFP/min/um)")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/meanq_vs_mean_gr.pdf",width=6,height=4)
```



```{r}
toplot <- myframes_sampled %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
toplot %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  mutate(s=compute_slope_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell)) %>% 
  mutate(sd=compute_sdslope_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell)) %>% 
  mutate(b=compute_intercept_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell)) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_mean_q_cell,col=condition_explicit))+
  geom_line(aes(mean_mean_lambda_cell,mean_mean_lambda_cell*s+b),col="red")+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_mean_q_cell-sd_mean_q_cell,ymax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_mean_q_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  #geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_mean_q_cell,col=condition_explicit),alpha=0.2)+
  #geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_mean_q_cell-sd_mean_q_cell,ymax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  #geom_errorbar(data=toplot,aes(y=mean_mean_q_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  #ylim(0,0.5)+
  xlim(0,2.5)+
  #scale_y_continuous(trans='log',breaks=c(5,10,20,40,80,160,320,640))+
  #scale_x_continuous(trans='log',breaks=c(0.0625,0.125,0.25,0.5,1,2))+
  xlab("Mean Growth Rate (h-1)")+
  ylab("Mean volumic production (#GFP/min/um)")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))
```
```{r}
toplot %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  mutate(s=compute_slope_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell)) %>% 
  mutate(sd=compute_sdslope_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell)) %>% 
  mutate(b=compute_intercept_errxy_robust(mean_mean_lambda_cell,mean_mean_q_cell)) %>% 
  distinct(s,b,sd)
```


# Mean concentration versus mean growth rate

```{r}
toplot <- myframes_sampled %>% 
  mutate(c_cell=c_m) %>% 
  ungroup() %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
myframes_sampled %>%
  mutate(c_cell=c_m) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_mean_c_cell,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_mean_c_cell-sd_mean_c_cell,ymax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_mean_c_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_mean_c_cell,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_mean_c_cell-sd_mean_c_cell,ymax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_mean_c_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,25000)+
  xlim(0,2.5)+
  #scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  xlab("Mean Growth Rate (h-1)")+
  ylab("Mean Concentration (#GFP/um)")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/mean_c_cv_vs_mean_gr.pdf",width=8,height=4)

```

```{r}
toplot <- myframes_sampled %>% 
  mutate(c_cell=gfp_nb/length_um) %>% 
  ungroup() %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
myframes_sampled %>%
  mutate(c_cell=gfp_nb/length_um) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_mean_c_cell,col=condition_explicit,shape=mean_cell_rank))+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_mean_c_cell-sd_mean_c_cell,ymax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_mean_c_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_mean_c_cell,col=condition_explicit),alpha=0.2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_mean_c_cell-sd_mean_c_cell,ymax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_mean_c_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  scale_y_continuous(trans='log',breaks=c(8000,12000,18000,27000))+
  scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  #ylim(0,0.5)+
  #xlim(2500,40000)+
  xlab("Mean Growth Rate (h-1)")+
  ylab("Mean Concentration (#GFP/um)")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))
```
```{r}
toplot <- myframes_sampled %>% 
  mutate(c_cell=gfp_nb/length_um) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
toplot %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  mutate(s=compute_slope_errxy_robust(log(mean_mean_lambda_cell),log(mean_mean_c_cell))) %>% 
  mutate(sd=compute_sdslope_errxy_robust(log(mean_mean_lambda_cell),log(mean_mean_c_cell))) %>% 
  mutate(b=compute_intercept_errxy_robust(log(mean_mean_lambda_cell),log(mean_mean_c_cell))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_mean_c_cell,col=condition_explicit))+
  geom_line(aes(mean_mean_lambda_cell,exp(log(mean_mean_lambda_cell)*s+b)),col="red")+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_mean_c_cell-sd_mean_c_cell,ymax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_mean_c_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  #geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_mean_c_cell,col=condition_explicit),alpha=0.2)+
  #geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_mean_c_cell-sd_mean_c_cell,ymax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  #geom_errorbar(data=toplot,aes(y=mean_mean_c_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  scale_y_continuous(trans='log',breaks=c(8000,12000,18000,27000))+
  scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  #ylim(0,0.5)+
  #xlim(2500,40000)+
  xlab("Mean Growth Rate (h-1)")+
  ylab("Mean Concentration (#GFP/um)")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))
```
```{r}
toplot %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  mutate(s=compute_slope_errxy_robust(log(mean_mean_lambda_cell),log(mean_mean_c_cell))) %>% 
  mutate(sd=compute_sdslope_errxy_robust(log(mean_mean_lambda_cell),log(mean_mean_c_cell))) %>% 
  mutate(b=compute_intercept_errxy_robust(log(mean_mean_lambda_cell),log(mean_mean_c_cell))) %>% 
  distinct(s,b,sd)
```


```{r}
toplot <- myframes_sampled %>% 
  mutate(c_cell=gfp_nb/length_um) %>% 
  ungroup() %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
myframes_sampled %>%
  mutate(c_cell=gfp_nb/length_um) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_lambda_cell,mean_mean_c_cell,col=condition_explicit,shape=mean_cell_rank))+
  geom_errorbar(aes(x=mean_mean_lambda_cell,ymin=mean_mean_c_cell-sd_mean_c_cell,ymax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_mean_c_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_lambda_cell,mean_mean_c_cell,col=condition_explicit),alpha=0.2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_lambda_cell,ymin=mean_mean_c_cell-sd_mean_c_cell,ymax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_mean_c_cell,xmin=mean_mean_lambda_cell-sd_mean_lambda_cell,xmax=mean_mean_lambda_cell+sd_mean_lambda_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  #scale_y_continuous(trans='log',breaks=c(8000,12000,18000,27000))+
  #scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  ylim(5000,30000)+
  xlim(0,2.5)+
  xlab("Mean Growth Rate (h-1)")+
  ylab("Mean Concentration (#GFP/um)")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))
```


# Variance and CV of production together with mean production

```{r}
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))
```

```{r}
toplot <- myframes_sampled %>% 
  mutate(q_cell=q) %>% 
  #mutate(q_cell=q_m) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sqrt(mean(q**2+cov_qq)-mean_q_cell**2)) %>%
  #mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))

myframes_sampled %>%
  #mutate(q_cell=q_m) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sqrt(mean(q**2+cov_qq)-mean_q_cell**2)) %>%
  #mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_q_cell,mean_sd_q_cell**2,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_q_cell,mean_sd_q_cell**2,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  #ylim(0,0.5)+
  #xlim(0,3)+
  scale_y_continuous(trans='log10',breaks=c(10,100,1000,10000),limits=c(10,20000))+
  annotation_logticks(sides="l")+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean production (#GFP/min/um)")+
  ylab("Production variance")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/var_q_vs_gr.pdf",width=7,height=4)

```

```{r}
toplot <- myframes_sampled %>% 
  mutate(q_cell=q) %>% 
  #mutate(q_cell=q_m) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sqrt(mean(q**2+cov_qq)-mean_q_cell**2)) %>%
  #mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(s=compute_slope_errxy_robust(mean_mean_q_cell,mean_sd_q_cell**2)) %>% 
  mutate(sd=compute_sdslope_errxy_robust(mean_mean_q_cell,mean_sd_q_cell**2)) %>% 
  mutate(b=compute_intercept_errxy_robust(mean_mean_q_cell,mean_sd_q_cell**2))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))

myframes_sampled %>%
  #mutate(q_cell=q_m) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sqrt(mean(q**2+cov_qq)-mean_q_cell**2)) %>%
  #mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_q_cell,mean_sd_q_cell**2,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_q_cell,mean_sd_q_cell**2,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2,col=condition_explicit),alpha=0.2)+
  geom_line(data=toplot,aes(mean_mean_q_cell,mean_mean_q_cell*s+b,col=condition_explicit),alpha=0.2,col="red",linetype="dashed")+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  #ylim(0,0.5)+
  #xlim(0,3)+
  #scale_y_continuous(trans='log10',breaks=c(10,100,1000,10000),limits=c(10,20000))+
  #annotation_logticks(sides="l")+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean production (#GFP/min/um)")+
  ylab("Production variance")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/var_q_vs_gr_lin.pdf",width=7,height=4)

```



```{r}
N <- 100
N0 <- 10

random_selection <- function(.d,.N,.N0){
  #.d: input dataframe
  #.N: Number of cells to pick per group
  #.N0 number of 'bags'
  
  .df <- .d %>% 
        group_by(cell) %>%  #already grouped by condition, promoter, type, simulationid
        sample_n(1) %>% 
        #mutate(lambda_cell=mean(lambda*60/log(2),na.rm=TRUE)) %>% 
        ungroup() %>% 
        #distinct(cell,.keep_all = TRUE) %>% 
        #mutate(re) %>% 
        sample_n(.N,replace=TRUE) %>% 
        mutate(sampling=1)
  
  for(i in 2:.N0){
    .df_new <- .d %>% 
        group_by(cell) %>%  #already grouped by condition, promoter, type, simulationid
        sample_n(1) %>% 
        #mutate(lambda_cell=mean(lambda*60/log(2),na.rm=TRUE)) %>% 
        ungroup() %>% 
        #distinct(cell,.keep_all = TRUE) %>% 
        sample_n(.N,replace=TRUE) %>% 
        mutate(sampling=i)
    .df <- rbind(.df,.df_new)}
  
  return(.df)}

if(!exists("mycluster")){
mycluster <- min(30, parallel::detectCores()-1) %>%  # do not use more than 30 cores
  default_cluster() %>% cluster_library( # load currently loaded packages on each core
    names(sessionInfo()$otherPkgs))
  
cluster_copy(mycluster,c("fit_exp_elongation_predict","fit_exp_elongation_slope","fit_exp_elongation_sd_slope","fit_exp_elongation_intercept"))
}

cluster_copy(mycluster,c("fit_exp_elongation_predict","fit_exp_elongation_slope","fit_exp_elongation_sd_slope","fit_exp_elongation_intercept","N0","random_selection","N"))

selected_conditions <- myframes_final %>% 
  distinct(cell,.keep_all = TRUE) %>% 
  group_by(promoter,mean_cell_rank,condition) %>% 
  filter(n()>50) %>% 
  ungroup() %>% 
  distinct(promoter,mean_cell_rank,condition)

myframes_sampled <- myframes_final %>% 
  semi_join(selected_conditions,by=c("promoter","mean_cell_rank","condition")) %>% 
  group_by(cell) %>% 
  partition(cluster=mycluster) %>%
  arrange(frame) %>% 
  mutate(alpha=fit_exp_elongation_slope(time_sec,length_um_m)) %>% 
  mutate(lambda_cell=mean(lambda_m*60/log(2),na.remove=TRUE)) %>% 
  mutate(q_cell=mean(q_m,na.remove=TRUE)) %>% 
  mutate(q_full_cellcycle=(last(gfp_nb_m)-first(gfp_nb_m))/(last(length_um_m)-first(length_um_m))*alpha) %>% 
  collect() %>% 
  ungroup() %>% 
  group_by(condition,promoter,mean_cell_rank) %>% 
  partition(cluster=mycluster) %>%
  do((function(.df){
    .new_df <- random_selection(.df,N,N0)
    return(.new_df)})
    (.)) %>% 
  collect() %>% 
  ungroup()
```

```{r}
toplot <- myframes_sampled %>% 
  mutate(q_cell=q) %>% 
  #mutate(q_cell=q_m) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sqrt(mean(q**2+cov_qq)-mean_q_cell**2)) %>%
  #mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))

myframes_sampled %>%
  #mutate(q_cell=q_m) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sqrt(mean(q**2+cov_qq)-mean_q_cell**2)) %>%
  #mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_q_cell,mean_cv_q_cell,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_q_cell,ymin=mean_cv_q_cell-sd_cv_q_cell,ymax=mean_cv_q_cell+sd_cv_q_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_cv_q_cell,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_q_cell,mean_cv_q_cell,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_q_cell,ymin=mean_cv_q_cell-sd_cv_q_cell,ymax=mean_cv_q_cell+sd_cv_q_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_cv_q_cell,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,1)+
  #xlim(0,3)+
  #scale_y_continuous(trans='log10',breaks=c(10,100,1000,10000),limits=c(10,20000))+
  #annotation_logticks(sides="l")+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean production (#GFP/min/um)")+
  ylab("Production CV")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/cv_q_vs_mean_q.pdf",width=7,height=4)

```

```{r}
toplot <- myframes_sampled %>% 
  mutate(q_cell=q_m) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  

conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))


myframes_sampled %>%
  mutate(q_cell=q_m) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_q_cell,mean_cv_q_cell,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_q_cell,ymin=mean_cv_q_cell-sd_cv_q_cell,ymax=mean_cv_q_cell+sd_cv_q_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_cv_q_cell,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_q_cell,mean_cv_q_cell,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_q_cell,ymin=mean_cv_q_cell-sd_cv_q_cell,ymax=mean_cv_q_cell+sd_cv_q_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_cv_q_cell,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,0.6)+
  #xlim(0,3)+
  #scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  xlab("Mean Production (#GFP/min/um)")+
  ylab("Production CV")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/cv_q_vs_gr.pdf",width=7,height=4)

```

# CV of concentration

```{r}
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))
```

```{r}
toplot <- myframes_sampled %>% 
  mutate(c_cell=gfp_nb/length_um) %>% 
  mutate(sigma2_c_cell=(1/length_um*sqrt(cov_gg)-gfp_nb/(length_um**2)*sqrt(cov_ll))**2) %>%
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sqrt(mean(c_cell**2+sigma2_c_cell)-mean_c_cell**2)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_c_cell=mean(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_c_cell=sd(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))

myframes_sampled %>%
  mutate(c_cell=gfp_nb/length_um) %>% 
  mutate(sigma2_c_cell=(1/length_um*sqrt(cov_gg)-gfp_nb/(length_um**2)*sqrt(cov_ll))**2) %>%
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  #mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sqrt(mean(c_cell**2+sigma2_c_cell)-mean_c_cell**2)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_c_cell=mean(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_c_cell=sd(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_c_cell,mean_sd_c_cell**2,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_c_cell,ymin=(mean_sd_c_cell-sd_sd_c_cell)**2,ymax=(mean_sd_c_cell+sd_sd_c_cell)**2,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_c_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_sd_c_cell**2,xmin=mean_mean_c_cell-sd_mean_c_cell,xmax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_c_cell,mean_sd_c_cell**2,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_c_cell,ymin=(mean_sd_c_cell-sd_sd_c_cell)**2,ymax=(mean_sd_c_cell+sd_sd_c_cell)**2,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_sd_c_cell**2,xmin=mean_mean_c_cell-sd_mean_c_cell,xmax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  #ylim(0,0.5)+
  #xlim(0,3)+
  #scale_y_continuous(trans='log',breaks=c(1,10,100,1000))+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean concentration (#GFP/min/um)")+
  ylab("Concentration variance")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/var_c_vs_mean_c.pdf",width=7,height=4)

```


```{r}
toplot <- myframes_sampled %>% 
  mutate(c_cell=gfp_nb/length_um) %>% 
  mutate(sigma2_c_cell=(1/length_um*sqrt(cov_gg)-gfp_nb/(length_um**2)*sqrt(cov_ll))**2) %>%
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sqrt(mean(c_cell**2+sigma2_c_cell)-mean_c_cell**2)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_c_cell=mean(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_c_cell=sd(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(s=compute_slope_errxy_robust(mean_mean_c_cell,log(mean_sd_c_cell**2))) %>% 
  mutate(sd=compute_sdslope_errxy_robust(mean_mean_c_cell,log(mean_sd_c_cell**2))) %>%
  mutate(b=compute_intercept_errxy_robust(mean_mean_c_cell,log(mean_sd_c_cell**2)))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 

print(unique(toplot$s))
print(unique(toplot$b))
print(unique(toplot$sd))
  
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))

myframes_sampled %>%
  mutate(c_cell=gfp_nb/length_um) %>% 
  mutate(sigma2_c_cell=(1/length_um*sqrt(cov_gg)-gfp_nb/(length_um**2)*sqrt(cov_ll))**2) %>%
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  #mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sqrt(mean(c_cell**2+sigma2_c_cell)-mean_c_cell**2)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_c_cell=mean(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_c_cell=sd(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_c_cell,mean_sd_c_cell**2,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_c_cell,ymin=(mean_sd_c_cell-sd_sd_c_cell)**2,ymax=(mean_sd_c_cell+sd_sd_c_cell)**2,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_c_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_sd_c_cell**2,xmin=mean_mean_c_cell-sd_mean_c_cell,xmax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_c_cell,mean_sd_c_cell**2,col=condition_explicit),alpha=0.2,size=2)+
  geom_line(data=toplot,aes(mean_mean_c_cell,exp(mean_mean_c_cell*s+b)),alpha=0.2,col="red",linetype="dashed")+
  geom_errorbar(data=toplot,aes(x=mean_mean_c_cell,ymin=(mean_sd_c_cell-sd_sd_c_cell)**2,ymax=(mean_sd_c_cell+sd_sd_c_cell)**2,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_sd_c_cell**2,xmin=mean_mean_c_cell-sd_mean_c_cell,xmax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  #ylim(0,0.5)+
  #xlim(0,3)+
  scale_y_continuous(trans='log10',breaks=c(1e5,1e6,1e7,1e8),limits=c(1e6,1e8))+
  annotation_logticks(side="l")+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean concentration (#GFP/min/um)")+
  ylab("Concentration variance")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/var_c_vs_mean_c_log.pdf",width=7,height=4)

```

```{r}
toplot <- myframes_sampled %>% 
  mutate(c_cell=gfp_nb/length_um) %>% 
  mutate(sigma2_c_cell=(1/length_um*sqrt(cov_gg)-gfp_nb/(length_um**2)*sqrt(cov_ll))**2) %>%
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sqrt(mean(c_cell**2+sigma2_c_cell)-mean_c_cell**2)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_c_cell=mean(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_c_cell=sd(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))

myframes_sampled %>%
  mutate(c_cell=gfp_nb/length_um) %>% 
  mutate(sigma2_c_cell=(1/length_um*sqrt(cov_gg)-gfp_nb/(length_um**2)*sqrt(cov_ll))**2) %>%
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  #mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sqrt(mean(c_cell**2+sigma2_c_cell)-mean_c_cell**2)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_c_cell=mean(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_c_cell=sd(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_c_cell,mean_cv_c_cell,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_c_cell,ymin=mean_cv_c_cell-sd_cv_c_cell,ymax=mean_cv_c_cell+sd_cv_c_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_c_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_cv_c_cell,xmin=mean_mean_c_cell-sd_mean_c_cell,xmax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_c_cell,mean_cv_c_cell,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_c_cell,ymin=mean_cv_c_cell-sd_cv_c_cell,ymax=mean_cv_c_cell+sd_cv_c_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_cv_c_cell,xmin=mean_mean_c_cell-sd_mean_c_cell,xmax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,1)+
  #xlim(0,3)+
  #scale_y_continuous(trans='log',breaks=c(1,10,100,1000))+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean concentration (#GFP/um)")+
  ylab("Concentration CV")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/cv_c_vs_mean_c.pdf",width=7,height=4)

```




```{r}
toplot <- myframes_sampled %>% 
  mutate(c_cell=c_m) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_c_cell=mean(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_c_cell=sd(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))

myframes_sampled %>%
  mutate(c_cell=c_m) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_c_cell=mean(c_cell,na.rm=TRUE)) %>%
  mutate(sd_c_cell=sd(c_cell,na.rm=TRUE)) %>%
  mutate(cv_c_cell=sd_c_cell/mean_c_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_c_cell=mean(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_c_cell=mean(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_c_cell=sd(sd_c_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_c_cell=sd(mean_c_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_c_cell=mean(cv_c_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_c_cell=sd(cv_c_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  
  geom_point(aes(mean_mean_c_cell,mean_cv_c_cell,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_c_cell,ymin=mean_cv_c_cell-sd_cv_c_cell,ymax=mean_cv_c_cell+sd_cv_c_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_c_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_cv_c_cell,xmin=mean_mean_c_cell-sd_mean_c_cell,xmax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_c_cell,mean_cv_c_cell,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_c_cell,ymin=(mean_cv_c_cell-sd_cv_c_cell),ymax=(mean_cv_c_cell+sd_cv_c_cell),col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_cv_c_cell,xmin=mean_mean_c_cell-sd_mean_c_cell,xmax=mean_mean_c_cell+sd_mean_c_cell,col=condition_explicit),alpha=0.2)+
  
  theme_cowplot()+
  ylim(0,0.5)+
  #xlim(0,3)+
  #scale_y_continuous(trans='log',breaks=c(1,10,100,1000))+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean concentration (#GFP/min/um)")+
  ylab("CV concentration")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/cv_c_vs_mean_c.pdf",width=7,height=4)

```













```{r}
toplot <- myframes_sampled %>% 
  mutate(q_cell=q_m) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  

conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))


myframes_sampled %>%
  mutate(q_cell=q_m) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_q_cell,mean_cv_q_cell,col=condition_explicit,shape=mean_cell_rank),size=2)+
  geom_errorbar(aes(x=mean_mean_q_cell,ymin=mean_cv_q_cell-sd_cv_q_cell,ymax=mean_cv_q_cell+sd_cv_q_cell,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_cv_q_cell,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_q_cell,mean_cv_q_cell,col=condition_explicit),alpha=0.2,size=2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_q_cell,ymin=mean_cv_q_cell-sd_cv_q_cell,ymax=mean_cv_q_cell+sd_cv_q_cell,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_cv_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_cv_q_cell,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  ylim(0,0.6)+
  #xlim(0,3)+
  #scale_x_continuous(trans='log',breaks=c(0.125,0.25,0.5,1,2))+
  xlab("Mean Production (#GFP/min/um)")+
  ylab("Production CV")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ggsave("./20221208_presentation/cv_q_vs_gr.pdf",width=7,height=4)

```




# Production OU parameters

```{r}
myparameters %>% 
  filter(name %in% c("mean_q","var_q","gamma_q")) %>% 
  select(name,final,carbon_source,carbon_source_concentration) %>% 
  pivot_wider(names_from = name,values_from = final) %>% 
  mutate(condition=paste(carbon_source,carbon_source_concentration,sep="")) %>% 
  mutate(variance_q=var_q/(2*gamma_q)) %>% 
  ggplot()+
  geom_point(aes(mean_q,variance_q,col=condition))

myparameters %>% 
  filter(name %in% c("mean_q","var_q","gamma_q")) %>% 
  select(name,final,carbon_source,carbon_source_concentration) %>% 
  pivot_wider(names_from = name,values_from = final) %>% 
  mutate(condition=paste(carbon_source,carbon_source_concentration,sep="")) %>% 
  mutate(variance_q=var_q/(2*gamma_q)) %>% 
  mutate(cv_q=sqrt(variance_q)/mean_q) %>% 
  ggplot()+
  geom_point(aes(mean_q,cv_q,col=condition))

```

# Production: full cell cycle variables

```{r}
myframes_sampled$mean_cell_rank <- factor(myframes_sampled$mean_cell_rank,levels = c(0:10))
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))

toplot <- myframes_sampled %>% 
  mutate(q_cell=q_full_cellcycle*60) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  


myframes_sampled %>%
  mutate(q_cell=q_full_cellcycle*60) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))) %>% 
  ggplot()+
  geom_point(aes(mean_mean_q_cell,mean_sd_q_cell**2,col=condition_explicit,shape=mean_cell_rank))+
  geom_errorbar(aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2,col=condition_explicit))+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_q_cell,col=mean_cell_rank))+
  geom_errorbar(aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit))+
  
  geom_point(data=toplot,aes(mean_mean_q_cell,mean_sd_q_cell**2,col=condition_explicit),alpha=0.2)+
  geom_errorbar(data=toplot,aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2,col=condition_explicit),alpha=0.2)+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot,aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell,col=condition_explicit),alpha=0.2)+
  theme_cowplot()+
  #ylim(0,0.5)+
  #xlim(0,3)+
  #scale_y_continuous(trans='log',breaks=c(1,10,100,1000))+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean production (#GFP/min/um)")+
  ylab("Production variance")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))
```

# Comparing full cell cycle observables and mean value over the cell cycle

```{r}
conditions_df <- tibble(condition=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"),condition_explicit=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa"))


toplot_mean_norank <- myframes_sampled %>% 
  #mutate(q_cell=q) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  

toplot_mean <- myframes_sampled %>% 
  #mutate(q_cell=q) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa")))
  
toplot_full_norank <- myframes_sampled %>% 
  mutate(q_cell=q_full_cellcycle*60) %>% 
  group_by(condition,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,.keep_all=TRUE) %>% 
  left_join(conditions_df,by=c("condition"))
  #mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  

toplot_full <- myframes_sampled %>% 
  mutate(q_cell=q_full_cellcycle*60) %>% 
  group_by(condition,mean_cell_rank,sampling) %>% 
  mutate(mean_lambda_cell=mean(lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_lambda_cell=sd(lambda_cell,na.rm=TRUE)) %>%
  mutate(cv_lambda_cell=sd_lambda_cell/mean_lambda_cell) %>%
  mutate(mean_q_cell=mean(q_cell,na.rm=TRUE)) %>%
  mutate(sd_q_cell=sd(q_cell,na.rm=TRUE)) %>%
  mutate(cv_q_cell=sd_q_cell/mean_q_cell) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,sampling,.keep_all=TRUE) %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(mean_mean_lambda_cell=mean(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_lambda_cell=sd(mean_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_lambda_cell=mean(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_lambda_cell=sd(cv_lambda_cell,na.rm=TRUE)) %>%
  mutate(mean_mean_q_cell=mean(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_sd_q_cell=mean(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_sd_q_cell=sd(sd_q_cell,na.rm=TRUE)) %>%
  mutate(sd_mean_q_cell=sd(mean_q_cell,na.rm=TRUE)) %>%
  mutate(mean_cv_q_cell=mean(cv_q_cell,na.rm=TRUE)) %>%
  mutate(sd_cv_q_cell=sd(cv_q_cell,na.rm=TRUE)) %>%
  ungroup() %>% 
  distinct(condition,mean_cell_rank,.keep_all=TRUE) %>% 
  mutate(mean_cell_rank_integer=as.integer(mean_cell_rank)) %>% 
  left_join(conditions_df,by=c("condition")) %>% 
  mutate(condition_explicit=factor(condition_explicit,levels=c("acetate 0.05%","acetate 0.2%","glycerol 0.4%","glucose 0.2%","glucose 0.2% + aa")))
  
ptot <- ggplot()+
  geom_point(data=toplot_full,aes(mean_mean_q_cell,mean_sd_q_cell**2,shape=mean_cell_rank),col="blue")+
  geom_errorbar(data=toplot_full,aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2),col="blue")+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_q_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot_full,aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell),col="blue")+
  
  geom_point(data=toplot_full_norank,aes(mean_mean_q_cell,mean_sd_q_cell**2),alpha=0.2,col="blue")+
  geom_errorbar(data=toplot_full_norank,aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2),alpha=0.2,col="blue")+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot_full_norank,aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell),alpha=0.2,col="blue")+
  
  geom_point(data=toplot_mean,aes(mean_mean_q_cell,mean_sd_q_cell**2,shape=mean_cell_rank),col="red")+
  geom_errorbar(data=toplot_mean,aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2),col="red")+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_q_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot_mean,aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell),col="red")+
  
  geom_point(data=toplot_mean_norank,aes(mean_mean_q_cell,mean_sd_q_cell**2),alpha=0.2,col="red")+
  geom_errorbar(data=toplot_mean_norank,aes(x=mean_mean_q_cell,ymin=(mean_sd_q_cell-sd_sd_q_cell)**2,ymax=(mean_sd_q_cell+sd_sd_q_cell)**2),alpha=0.2,col="red")+
  #geom_point(aes(mean_cell_rank_integer,mean_sd_lambda_cell,col=mean_cell_rank))+
  geom_errorbar(data=toplot_mean_norank,aes(y=mean_sd_q_cell**2,xmin=mean_mean_q_cell-sd_mean_q_cell,xmax=mean_mean_q_cell+sd_mean_q_cell),alpha=0.2,col="red")+
  
  theme_cowplot()+
  #ylim(0,0.5)+
  #xlim(0,3)+
  #scale_y_continuous(trans='log',breaks=c(1,10,100,1000))+
  #scale_x_continuous(trans='log',breaks=c(1,10,100,1000))+
  xlab("Mean production (#GFP/min/um)")+
  ylab("Production variance")+
  guides(col=guide_legend(title="Conditions"))+
  guides(shape=guide_legend(title="Cell rank"))

ptot
```

**Red**: mean value over the cell cycle, over 50 cells
**Blue**: full cell cycle observable
**Question to Bjoern**: could it be that the variance of the production is vastly underestimated in acetate 0.05%?

# Looking at the production variance, using all data points at my disposal

```{r}
myframes_final$mean_cell_rank <- factor(myframes_final$mean_cell_rank,levels = c(0:10))

myframes_final %>% 
  group_by(condition) %>% 
  mutate(variance_production=var(q,na.rm=FALSE)) %>% 
  mutate(mean_production=mean(q,na.rm=TRUE)) %>% 
  ungroup %>% 
  ggplot()+
  geom_point(aes(mean_production,variance_production,col=condition))+
  theme_cowplot()


myframes_final %>% 
  group_by(condition) %>% 
  mutate(variance_production=var(q,na.rm=FALSE)) %>% 
  mutate(mean_production=mean(q,na.rm=TRUE)) %>% 
  ungroup %>% 
  ggplot()+
  geom_point(aes(log(mean_production),log(variance_production),col=condition))+
  theme_cowplot()

myframes_final %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(variance_production=var(q,na.rm=FALSE)) %>% 
  mutate(mean_production=mean(q,na.rm=TRUE)) %>% 
  ungroup %>% 
  ggplot()+
  geom_point(aes(mean_production,variance_production,col=condition,shape=mean_cell_rank))+
  theme_cowplot()


myframes_final %>% 
  group_by(condition,mean_cell_rank) %>% 
  mutate(variance_production=var(q,na.rm=FALSE)) %>% 
  mutate(mean_production=mean(q,na.rm=TRUE)) %>% 
  ungroup %>% 
  ggplot()+
  geom_point(aes(log(mean_production),log(variance_production),col=condition,shape=mean_cell_rank))+
  theme_cowplot()
```












