---
title: "growth_production_heatmap.Rmd"
author: "Dany Chauvin"
date: '2023-01-30'
output: html_document
---

We want to plot, a heat-map of actual growth-rate versus production (mean).
For each condition for hi1.

# Importing data
We assume here, denoised data were already saved in ./denoised_data

```{r message=FALSE,warning=FALSE}
source("../mother_machine_experiments_toolbox/load_functions_and_packages.R")
source("../mother_machine_experiments_toolbox/inference_simulations_useful_functions.R")
#load myframes uncomplete and complete cell cycles.
source("../mother_machine_experiments_toolbox/load_denoised_data.R")
#load only full cell cycles
#source("../mother_machine_experiments_toolbox/load_denoised_data_complete_cell_cycles.R")
```

# Studying weird cells in the glycerol distribution

```{r}
plot_histogram <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  
  exp_density <- density(myframes %>% filter(condition==.cond) %>% mutate(ll=length_um) %>%  .$ll)
  #sim_density <- density(myframes %>% filter(condition==.cond) %>% mutate(ll=log(gfp_nb)) %>%  .$ll)
  exp <- myframes %>% filter(condition==.cond) %>% mutate(ll=length_um) %>% .$ll
  #sim <- myframes %>% filter(condition==.cond,datatype=="allnoisesources") %>% mutate(ll=log(gfp_nb)) %>% .$ll
  exp_density
  #sim_density
  print(exp_density)
  #print(sim_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  #h_sim <- hist(sim, breaks = breakVec,plot=FALSE)
  if(plot){
  print(
  ggplot()+
    geom_col(aes(x=h_exp$mids,y=h_exp$counts),fill="blue",alpha=0.5)+
    #geom_col(aes(x=h_sim$mids,y=h_sim$counts),fill="red",alpha=0.5))+
      scale_y_continuous(trans = "log10")+
      #scale_x_continuous(trans = "log10")+
      ylab("Counts")+
      xlab("Cell-size"))}
}

breakVec=seq(0.8,8,0.01)
plot_histogram("glycerol040",breakVec,TRUE)
```

```{r}
plot_histogram <- function(.cond,breakVec=seq(4000,43000,500),plot=FALSE){
  
  exp_density <- density(myframes %>% filter(condition==.cond) %>% mutate(ll=gfp_nb) %>%  .$ll)
  #sim_density <- density(myframes %>% filter(condition==.cond) %>% mutate(ll=log(gfp_nb)) %>%  .$ll)
  exp <- myframes %>% filter(condition==.cond) %>% mutate(ll=gfp_nb) %>% .$ll
  #sim <- myframes %>% filter(condition==.cond,datatype=="allnoisesources") %>% mutate(ll=log(gfp_nb)) %>% .$ll
  exp_density
  #sim_density
  print(exp_density)
  #print(sim_density)
  h_exp <- hist(exp, breaks = breakVec,plot=FALSE)
  #h_sim <- hist(sim, breaks = breakVec,plot=FALSE)
  if(plot){
  print(
  ggplot()+
    geom_col(aes(x=h_exp$mids,y=h_exp$counts),fill="blue",alpha=0.5)+
    geom_vline(aes(xintercept=10000),col="red")+
    #geom_col(aes(x=h_sim$mids,y=h_sim$counts),fill="red",alpha=0.5))+
      scale_y_continuous(trans = "log10")+
      #scale_x_continuous(trans = "log10")+
      ylab("Counts")+
      xlab("Cell-size"))}
}

breakVec=seq(-1300,250000,300)
plot_histogram("glycerol040",breakVec,TRUE)
```
```{r}
bad_cells_points <- myframes %>% 
  filter(condition=="glycerol040") %>% 
  filter(gfp_nb<10000) %>% 
  distinct(cell,time_sec)

bad_cells <- bad_cells_points %>% 
  distinct(cell)

myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,length_um,group="cell"))+
  facet_wrap(~cell)
```

The root cell is already lysed at the beginning of the experiment, and becomes gently smaller and smaller. I can discard it.

# acetate005

```{r}
conditions <- factor(myframes$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom){

 x <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$lambda
  
  y <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top

  plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,xlab="Lambda (/min)",ylab="Q (GFP/min)")
  abline(h=c(-15,15),v=c(-0.0005,0.0005))
  }
```

```{r}
plot_heatscatter("acetate005","hi1")
plot_heatscatter("acetate020","hi1")
plot_heatscatter("glycerol040","hi1")
plot_heatscatter("glucose020","hi1")
plot_heatscatter("glucoseaa020","hi1")
```

Actually, the question is: are the vast majority of these cells, casher or not?

```{r}
conditions <- factor(myframes$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom,qmin,qmax,grmin,grmax){

 x <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$lambda
  
  y <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top

  plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,xlab="Lambda (/min)",ylab="Q (GFP/min)")
  abline(h=c(qmin,qmax),v=c(grmin,grmax))
  }

plot_heatscatter("acetate005","hi1",-50,5,-0.001,0.0005)
```
```{r}
bad_cells_point <- myframes %>% 
  filter(condition=="acetate005") %>% 
  filter(between(q,-50,5),between(lambda,-0.001,0005)) %>% 
  distinct(cell,time_sec,frame,cell_rank)

bad_cells <- bad_cells_point %>% 
  distinct(cell)

bad_cells_full <- myframes %>% 
  semi_join(bad_cells,by=c("cell"))

myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,log(length_um_raw),group="cell"),col="green")+
  geom_point(aes(time_sec/3600,log(length_um),group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,log(length_um),group="cell"),col="red")+
  facet_wrap(~cell)

myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,gfp_nb_raw,group="cell"),col="green")+
  geom_point(aes(time_sec/3600,gfp_nb,group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,gfp_nb,group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_gfp_acetate005.pdf",width=30,height=30,limitsize = FALSE)
```


```{r}
bad_cells_full %>% 
  arrange(cell,frame) %>% 
  select(cell,frame,cell_rank)
```

**Problematic cells**:
- 20221121.2.28.2: badly segmented, to discard (root)
- 20221121.2.8.2: it does not grow, but normal (higher cell rank)
- 20221121.2.18.2: it does not grow, but normal (root)
- 20221121.1.21.9: it does not grow, but normal (root)
- 20221121.0.20.1: badly segmented, to discard (root)
- 20221121.0.28.7: badly segmented

Except 2.28.2 which is badly segmented in one frame (but still seems to grow), there is nothing really wrong with these cells, from the length point of view.
Not what's happening, from Q point of view

```{r}
bad_cells_point <- myframes %>% 
  filter(condition=="acetate005") %>% 
  filter(between(q,-50,-25)) %>% 
  distinct(cell,time_sec,frame,cell_rank)

bad_cells <- bad_cells_point %>% 
  distinct(cell)

bad_cells_full <- myframes %>% 
  semi_join(bad_cells,by=c("cell"))

myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(frame,gfp_nb_raw,group="cell"),col="green")+
  geom_point(aes(frame,gfp_nb,group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(frame,gfp_nb,group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_q_acetate005.pdf",width=30,height=30,limitsize = FALSE)
```

Actually, when it comes to this, I should only look at the raw data...


# acetate020

Actually, the question is: are the vast majority of these cells, casher or not?

```{r}
conditions <- factor(myframes$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom,qmin,qmax,grmin,grmax){

 x <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$lambda
  
  y <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top

  plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,xlab="Lambda (/min)",ylab="Q (GFP/min)")
  abline(h=c(qmin,qmax),v=c(grmin,grmax))
  }

plot_heatscatter("acetate020","hi1",-100,12,-0.002,0.0007)
```

```{r}
bad_cells_point <- myframes %>% 
  filter(condition=="acetate020") %>% 
  filter(between(q,-100,12),between(lambda,-0.002,0007)) %>% 
  distinct(cell,time_sec,frame,cell_rank)

bad_cells <- bad_cells_point %>% 
  distinct(cell)

bad_cells_full <- myframes %>% 
  semi_join(bad_cells,by=c("cell"))

myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,log(length_um_raw),group="cell"),col="green")+
  geom_point(aes(time_sec/3600,log(length_um),group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,log(length_um),group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_log_length_acetate020.pdf",width=50,height=50,limitsize = FALSE)


myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,gfp_nb_raw,group="cell"),col="green")+
  geom_point(aes(time_sec/3600,gfp_nb,group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,gfp_nb,group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_gfp_acetate020.pdf",width=50,height=50,limitsize = FALSE)
```


```{r}
bad_cells_full %>% 
  arrange(cell,frame) %>% 
  select(cell,frame,cell_rank)
```

**Problematic cells**:
- None, just checking what does "20220824.5.48.65"

```{r}
myframes %>% 
  filter(cell=="20220824.5.48.65") %>% 
  select(cell_rank,frame) %>% 
  arrange(frame)
```

```{r}
myframes %>% 
  filter(cell=="20220824.5.48.82") %>% 
  select(cell_rank,frame) %>% 
  arrange(frame)
```
Ok

```{r}
myframes %>% 
  filter(cell=="20220824.5.50.82") %>% 
  select(cell_rank,frame) %>% 
  arrange(frame)
```
Ok

# glycerol040

Actually, the question is: are the vast majority of these cells, casher or not?

```{r}
conditions <- factor(myframes$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom,qmin,qmax,grmin,grmax){

 x <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$lambda
  
  y <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top

  plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,xlab="Lambda (/min)",ylab="Q (GFP/min)")
  abline(h=c(qmin,qmax),v=c(grmin,grmax))
  }

plot_heatscatter("glycerol040","hi1",-120,16,-0.0035,0.0008)
```

```{r}
bad_cells_point <- myframes %>% 
  filter(condition=="glycerol040") %>% 
  filter(cell!="20190515.3.9.79") %>% 
  filter(between(q,-100,16),between(lambda,-0.0035,0.0008)) %>% 
  distinct(cell,time_sec,frame,cell_rank)

bad_cells <- bad_cells_point %>% 
  distinct(cell)

bad_cells_full <- myframes %>% 
  semi_join(bad_cells,by=c("cell"))

myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,log(length_um_raw),group="cell"),col="green")+
  geom_point(aes(time_sec/3600,log(length_um),group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,log(length_um),group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_log_length_glycerol040.pdf",width=50,height=50,limitsize = FALSE)


myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,gfp_nb_raw,group="cell"),col="green")+
  geom_point(aes(time_sec/3600,gfp_nb,group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,gfp_nb,group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_gfp_glycerol040.pdf",width=50,height=50,limitsize = FALSE)
```

Checking cells:
- Cells that go down in gfp over time

```{r}
cell_to_check=c("20190515.0.12.266","20190515.1.2.256","20190515.1.2.256","20190515.1.9.283","20190515.4.8.265","20190515.5.5.255","20190515.5.4.255","20190515.5.3.270","20190515.0.12.251")

bad_cells <- myframes %>% 
  filter(cell %in% cell_to_check) %>% 
  #semi_join(cell_to_check,by=c("cell")) %>% 
  select(cell,frame,cell_rank) %>% View()
```

- 20190515.5.6.255: cell is going through "plasmolysis" (rank 0, from frame 762), to be discarded.
- 20190515.5.4.255: cell certainly start some kind of plasmolysis. But we only see the beginning, so hard to discard it.
- 20190515.4.8.265: cell is going through "plasmolysis" (rank 0, from frame 762), to be discarded.
- 20190515.0.12.251: this is ok, but about too.
- Look at the production traces: filter based on how fast these cells do decay/or for how many times points in a row. I can simply measure the mean production during the cell cycle. If this is significantly small, I discard the cells. Look at these distributions. Applying to all conditions.
- Same for mean growth rate.
- See if this a better way to get rid of them.

# glucose020

Actually, the question is: are the vast majority of these cells, casher or not?

```{r}
conditions <- factor(myframes$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom,qmin,qmax,grmin,grmax){

 x <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$lambda
  
  y <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top

  plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,xlab="Lambda (/min)",ylab="Q (GFP/min)")
  abline(h=c(qmin,qmax),v=c(grmin,grmax))
  }

plot_heatscatter("glucose020","hi1",-150,16,-0.01,0.0008)
```

```{r}
bad_cells_point <- myframes %>% 
  filter(condition=="glucose020") %>% 
  #filter(cell!="20190515.3.9.79") %>% 
  filter(between(q,-150,16),between(lambda,-0.01,0.0008)) %>% 
  distinct(cell,time_sec,frame,cell_rank)

bad_cells <- bad_cells_point %>% 
  distinct(cell)

bad_cells_full <- myframes %>% 
  semi_join(bad_cells,by=c("cell"))

myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,log(length_um_raw),group="cell"),col="green")+
  geom_point(aes(time_sec/3600,log(length_um),group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,log(length_um),group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_log_length_glucose020.pdf",width=50,height=50,limitsize = FALSE)


myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,gfp_nb_raw,group="cell"),col="green")+
  geom_point(aes(time_sec/3600,gfp_nb,group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,gfp_nb,group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_gfp_glucose020.pdf",width=50,height=50,limitsize = FALSE)
```

Checking cells.

# glucoseaa020

Actually, the question is: are the vast majority of these cells, casher or not?

```{r}
conditions <- factor(myframes$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom,qmin,qmax,grmin,grmax){

 x <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$lambda
  
  y <- myframes %>%
  filter(cell!="20190515.3.9.79") %>% 
  filter(condition==cond,promoter==prom) %>% 
  .$q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top

  plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,xlab="Lambda (/min)",ylab="Q (GFP/min)")
  abline(h=c(qmin,qmax),v=c(grmin,grmax))
  }

plot_heatscatter("glucoseaa020","hi1",-230,30,-0.02,0.006)
```

```{r}
bad_cells_point <- myframes %>% 
  filter(condition=="glucoseaa020") %>% 
  #filter(cell!="20190515.3.9.79") %>% 
  filter(between(q,-230,30),between(lambda,-0.02,0.006)) %>% 
  distinct(cell,time_sec,frame,cell_rank)

bad_cells <- bad_cells_point %>% 
  distinct(cell)

bad_cells_full <- myframes %>% 
  semi_join(bad_cells,by=c("cell"))

myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,log(length_um_raw),group="cell"),col="green")+
  geom_point(aes(time_sec/3600,log(length_um),group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,log(length_um),group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_log_length_glucoseaa020.pdf",width=50,height=50,limitsize = FALSE)


myframes %>% 
  semi_join(bad_cells,by=c("cell")) %>% 
  ggplot()+
  geom_point(aes(time_sec/3600,gfp_nb_raw,group="cell"),col="green")+
  geom_point(aes(time_sec/3600,gfp_nb,group="cell"),alpha=0.5)+
  geom_point(data=myframes %>% semi_join(bad_cells_point,by=c("cell","time_sec")),aes(time_sec/3600,gfp_nb,group="cell"),col="red")+
  facet_wrap(~cell)

ggsave("./bad_cells_gfp_glucoseaa020.pdf",width=50,height=50,limitsize = FALSE)
```

Discarding
- 20220821.1.48.121
- 20220921.1.48.127

# Looking at mean distributions, can we easily discard shitty cells?

```{r}
conditions <- factor(myframes$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom){

 x <- myframes %>%
  filter(condition==cond,promoter==prom) %>% 
  group_by(cell) %>% 
  mutate(m_lambda=mean(lambda,na.rm=TRUE)) %>% 
  ungroup() %>%
  distinct(cell,.keep_all = TRUE) %>% 
  .$m_lambda
  
  y <- myframes %>%
  filter(condition==cond,promoter==prom) %>% 
  group_by(cell) %>% 
  mutate(m_q=mean(q,na.rm=TRUE)) %>% 
  ungroup() %>%
  distinct(cell,.keep_all = TRUE) %>%
  .$m_q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top
print(plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,
           xlab="Mean Lambda (/min)",ylab="Mean Q (GFP/min)"))}
```

```{r}
plot_heatscatter("acetate005","hi1")
plot_heatscatter("acetate020","hi1")
plot_heatscatter("glycerol040","hi1")
plot_heatscatter("glucose020","hi1")
plot_heatscatter("glucoseaa020","hi1")
```

# Now, filtering out the cells by their mean, see what are distributions looking like.

```{r}
myframes_filtered <- myframes %>% 
  group_by(cell) %>% 
  mutate(m_lambda=mean(lambda,na.rm=TRUE)) %>% 
  mutate(m_q=mean(q,na.rm=TRUE)) %>% 
  filter(m_lambda>0) %>%
  filter(m_q>0) %>% 
  ungroup()
```

```{r}
conditions <- factor(myframes_filtered$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom){

 x <- myframes_filtered %>%
  filter(condition==cond,promoter==prom) %>% 
  group_by(cell) %>% 
  mutate(m_lambda=mean(lambda,na.rm=TRUE)) %>% 
  ungroup() %>%
  distinct(cell,.keep_all = TRUE) %>% 
  .$m_lambda
  
  y <- myframes_filtered %>%
  filter(condition==cond,promoter==prom) %>% 
  group_by(cell) %>% 
  mutate(m_q=mean(q,na.rm=TRUE)) %>% 
  ungroup() %>%
  distinct(cell,.keep_all = TRUE) %>%
  .$m_q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top
print(plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,
           xlab="Mean Lambda (/min)",ylab="Mean Q (GFP/min)"))}
```

```{r}
plot_heatscatter("acetate005","hi1")
plot_heatscatter("acetate020","hi1")
plot_heatscatter("glycerol040","hi1")
plot_heatscatter("glucose020","hi1")
plot_heatscatter("glucoseaa020","hi1")
```

# Now, filtering out cells not displaying a full cell cycle (division)

Does it look the same?

```{r}
myframes_filtered <- myframes %>% 
  filter(end_type=="div")
```

## Mean plot

```{r}
conditions <- factor(myframes_filtered$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom){

 x <- myframes_filtered %>%
  filter(condition==cond,promoter==prom) %>% 
  group_by(cell) %>% 
  mutate(m_lambda=mean(lambda,na.rm=TRUE)) %>% 
  ungroup() %>%
  distinct(cell,.keep_all = TRUE) %>% 
  .$m_lambda
  
  y <- myframes_filtered %>%
  filter(condition==cond,promoter==prom) %>% 
  group_by(cell) %>% 
  mutate(m_q=mean(q,na.rm=TRUE)) %>% 
  ungroup() %>%
  distinct(cell,.keep_all = TRUE) %>%
  .$m_q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top
print(plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,
           xlab="Mean Lambda (/min)",ylab="Mean Q (GFP/min)"))}
```

```{r}
plot_heatscatter("acetate005","hi1")
plot_heatscatter("acetate020","hi1")
plot_heatscatter("glycerol040","hi1")
plot_heatscatter("glucose020","hi1")
plot_heatscatter("glucoseaa020","hi1")
```
## Instantaneous plot

```{r}
conditions <- factor(myframes_filtered$condition,levels=c("acetate005","acetate020","glycerol040","glucose020","glucoseaa020"))

plot_heatscatter <- function(cond,prom){

 x <- myframes_filtered %>%
  filter(condition==cond,promoter==prom) %>% 
  .$lambda
  
  y <- myframes_filtered %>%
  filter(condition==cond,promoter==prom) %>% 
  .$q
  
df <- data.frame(x,y)

## Use densCols() output to get density at each point
x <- densCols(x,y, colramp=colorRampPalette(c("black", "white")))
df$dens <- col2rgb(x)[1,] + 1L

## Map densities to colors
cols <-  colorRampPalette(c("#000099", "#00FEFF", "#45FE4F", 
                            "#FCFF00", "#FF9400", "#FF3100"))(256)
df$col <- cols[df$dens]

## Plot it, reordering rows so that densest points are plotted on top
print(plot(y~x, data=df[order(df$dens),], pch=20, col=col, cex=2,
           xlab="Mean Lambda (/min)",ylab="Mean Q (GFP/min)"))}
```

```{r}
plot_heatscatter("acetate005","hi1")
plot_heatscatter("acetate020","hi1")
plot_heatscatter("glycerol040","hi1")
plot_heatscatter("glucose020","hi1")
plot_heatscatter("glucoseaa020","hi1")
```
